\begin{frame}{Packet F1 Question 1}
In a poem in this genre,  \tsquare{xred} a wealthy merchant sacrifices his only surviving seventh son in order to cure a sick stranger. A  \tcircle{xred} poem in this genre tells of Heraclius, who is executed when he refuses to abandon Christianity after his capture. The main character of a poem in this genre is unable to walk until he stands up using an iron rod that he fashions into a bow. The Swahili “utendi” are poems in this genre, such as The Story of Tambuka. The founding of the Mali Empire is told in a poem in this genre titled for Sundiata. For 10 points, name this genre of long, narrative poetry that  \hsquare{xgreen} details heroic deeds. \hdiamond{xred}  \htriangle{xred} 

\textbf{Answer}: Epic\ poetry\\
\tsquare{xred} Battle of Monmouth
\tcircle{xred} Noh
\hdiamond{xred} Epic poetry
\htriangle{xred} Satire
\end{frame}

\begin{frame}{Packet F1 Question 2}
Along with K.W. Wagner, this man names a polarization in which a build up of charge occurs at low frequencies in dielectric spectroscopy. Leo Szilard responded to a construct named for this man by arguing  \tcircle{xred} that measuring molecular speed would require energy, and therefore would increase the total entropy of a system consisting of two chambers connected by a trapdoor.  \tsquare{xred} This man’s “addition” to Ampere’s Law is part of his  \htriangle{xgreen} four namesake laws that govern electromagnetism. For 10 points,  \hcircle{xgreen} what scientist names a “demon” that violates the Second Law of Thermodynamics? \hdiamond{xred} 

\textbf{Answer}: James\ Clerk\ Maxwell\\
\tcircle{xred} Albert Einstein
\tsquare{xred} Maxwell's demon
\hdiamond{xred} Josiah Willard Gibbs
\end{frame}

\begin{frame}{Packet F1 Question 3}
A maximum bound for the number of elements in a set that has this property is given by the “replacement theorem.” The elements of a matroid possess  \hdiamond{xgreen} a generalized version of this property. Necessarily, the set of objects that are inputted and outputted in the Gram-Schmidt process have this property. A basis is a spanning set whose elements have this property. A set of vectors that  \tsquare{xgreen} includes the zero vector cannot have, for 10 points, what property of a vector set in which no one vector can be written as a linear combination  \tcircle{xgreen} of the others? \htriangle{xred} 

\textbf{Answer}: Linear\ independence\\
\htriangle{xred} Linear independence
\end{frame}

\begin{frame}{Packet F1 Question 4}
The fourth chapter of T.J. Clark’s The Painting of Modern Life argues that this painting represents the  \tcircle{xred} bisection between the proletariat and the bourgeoisie. On the upper right of this painting, a pair of green boots on a trapeze bar are visible  \hcircle{xgreen} above a circular light on a pink wall. On the bottom right  \tsquare{xgreen} of this painting, bottles of Bass Pale Ale appear on a marble counter next to a bowl of oranges.  \ttriangle{xgreen} The maid Suzon looks at the viewer, and also appears to hold a conversation with a patron in a mirror in, for 10 points, what Edouard Manet  \tdiamond{xgreen} painting of a Paris nightclub?

\textbf{Answer}: A\ Bar\ at\ the\ Folies-Bergère\\
\tcircle{xred} Olympia, London
\end{frame}

\begin{frame}{Packet F1 Question 5}
A model constitution was published on March 19th during this war in a city that was in the middle of enduring a two and a half year long siege. That siege in this war was initiated by forces under Jean-de-Dieu Soult. During this war, Andre Messena’s  \tcircle{xred} futile assaults on fortifications along the Lines of Torres Vedras failed  \hcircle{xgreen}  \tsquare{xgreen} to capture a national capital. Joseph I abdicated his throne at the end of this war after troops under the Duke of Wellington won decisive  \tdiamond{xgreen} clashes at Salamanca and Vittoria. For 10 points, name this phase of the Napoleonic Wars fought in  \ttriangle{xgreen} Spain.

\textbf{Answer}: Peninsular\ War\\
\tcircle{xred} War of 1812
\end{frame}

\begin{frame}{Packet F1 Question 6}
A play set in this country is about the troubled engagement between Billy Dimple and Maria von Rough. William Dunlap wrote a history of the theater in this country,  \tcircle{xred} which is the setting of Royall Tyler’s play The Contrast. Fans of two Shakespearean actors in this country turned violent in the Astor Place Riot. In the early 19th Century, some of the most popular plays in this country were minstrel shows, which often included white actors wearing blackface. For 10 points, name this country where Uncle Tom’s Cabin was frequently adapted for the stage. \hdiamond{xred}  \hsquare{xred}  \htriangle{xred} 

\textbf{Answer}: United\ States\\
\tcircle{xred} Royall Tyler
\hdiamond{xred} China
\hsquare{xred} Drama
\htriangle{xred} India
\end{frame}

\begin{frame}{Packet F1 Question 7}
In a novel with this title, the lead singer of the Terrible Children commits suicide in his basement, leaving his daughter Calliope Bird Morath unable to speak for several years; that book is the debut novel of Andrew Foster Altschul. The speaker of a poem with this title states, “The peanut-crunching  \hdiamond{xgreen} crowd / Shoves in to see / Them unwrap me hand and foot” and lists “A cake of soap, / A wedding ring, / A gold filling” as objects sought by the Nazi “Herr Doktor.”  \ttriangle{xred} “I rise with my red hair / And I eat men like air” closes, for 10 points, what Sylvia Plath poem? \hcircle{xred}  \hsquare{xred} 

\textbf{Answer}: Lady\ Lazarus\\
\ttriangle{xred} The New Life (novel)
\hcircle{xred} Daddy (poem)
\hsquare{xred} Ariel (poetry collection)
\end{frame}

\begin{frame}{Packet F1 Question 8}
Oliver Goldsmith attacked  \tsquare{xred} the lack of faults in stock characters used in “sentimental” plays in this genre.  \tcircle{xred} The critic Irving Wardle coined the term of a style within this genre, whose name is a pun that makes use of the word “menace.” Harry Horner feigns impotence in a play in this genre, William Wycherley’s The Country Wife. Plays in this genre “of humours” were written by Ben Jonson, which were similar to plays in this genre “of manners.” For 10 points, name this genre whose “Restoration” form amused during the reign of Charles II. \hdiamond{xred}  \htriangle{xred} 

\textbf{Answer}: Comedy\\
\tsquare{xred} The Vicar of Wakefield
\tcircle{xred} She Stoops to Conquer
\hdiamond{xred} Morality play
\htriangle{xred} Oratorio
\end{frame}

\begin{frame}{Packet F1 Question 9}
The play Moliere, or The  \tsquare{xred} Cabal of Hypocrites was shut down after  \tcircle{xred} only seven performances in this city. Edward Gordon Craig designed a series of movable screens for a performance of Hamlet in this city. A man who worked in this city advocated experiencing a role rather than representing it in his manual An Actor Prepares. A theater based in this city took a seagull as its symbol after a successful performance of Anton Chekhov’s The Seagull in 1898. For 10 points, name this city where Konstantin Stanislavski founded an “art theatre,” and which is a cultural rival of Saint Petersburg. \hdiamond{xred}  \htriangle{xred} 

\textbf{Answer}: Moscow\\
\tsquare{xred} The Misanthrope
\tcircle{xred} Mikhail Bulgakov
\hdiamond{xred} Rome
\htriangle{xred} New York City
\end{frame}

\begin{frame}{Packet F1 Question 10}
An author who was part  \tsquare{xred} of this literary movement wrote the lines, “Traveler, there is no path. / The path is made by walking.” In a novel from this movement, an artist dies of heart trouble shortly after his throat is clasped by a jealous doctor and that artist had earlier created a painting based on Byron’s Cain for his marriage to Helena. This movement included Antonio Machado and the author of Abel  \hdiamond{xgreen} Sanchez. Miguel de  \hsquare{xgreen} Unamuno belonged to, for 10 points, what literary movement named for the year  \hcircle{xgreen} in which Spain lost the Spanish-American war? \htriangle{xred} 

\textbf{Answer}: Generation\ of\ '98\\
\tsquare{xred} Transitive relation
\htriangle{xred} Generation of '98
\end{frame}

\begin{frame}{Packet F1 Question 11}
An author from this country wrote about how his father styled himself a “poliatrist,” or healer of the city, in his book Oblivion: A Memoir. A collection set in this birthplace of Hector Abad includes “Artificial Roses,” “Balthazar’s Marvelous Afternoon,” and a story in which an officer waiting for a pension check does not sell his dead son’s prized cockfighting  \tsquare{xred} rooster. In a novella from this country, two brothers stab  \hdiamond{xgreen} Santiago Nasar to death. For 10 points, name this birthplace of the author of No One Writes to the Colonel and Chronicle of a Death Foretold, Gabriel Garcia Marquez. \hcircle{xred}  \htriangle{xred} 

\textbf{Answer}: Colombia\\
\tsquare{xred} No One Writes to the Colonel
\hcircle{xred} Argentina
\htriangle{xred} China
\end{frame}

\begin{frame}{Packet F1 Question 12}
The 914 photocopier was developed by a company that was founded in this state, and which today is known as Xerox. In a trial held in this state, Ward Hunt directed the jury to issue a guilty verdict, which he accompanied with a sentence of a one hundred dollar fine. Frederick Douglass founded his newspaper The North Star in this state. Susan B. Anthony was arrested for voting in this state in 1872. George Eastman established his Kodak photography company in this state’s city of Rochester. For 10 points, name this state where the Seneca Falls Convention was held. \hdiamond{xred}  \hcircle{xred}  \hsquare{xred}  \htriangle{xred} 

\textbf{Answer}: New\ York\ (state)\\
\hdiamond{xred} Winamac
\hcircle{xred} Texas
\hsquare{xred} Susan B. Anthony
\htriangle{xred} Pennsylvania
\end{frame}

\begin{frame}{Packet F1 Question 13}
The sitting president described ongoing events in this city by saying “There is only an American problem.” “Turnaround Tuesday” was held in this city, which is where the minister James Reeb was beaten to death. “Spider” Martin is known for photographing an unconscious Amelia Boynton in this city during  \tcircle{xgreen} a series of events  \tdiamond{xgreen} nicknamed Bloody Sunday. A group of white  \tsquare{xgreen} deputies attacked African-Americans in this city as they attempted to cross the Edmund Pettus Bridge. For 10 points, name this starting point of three 1965 civil rights marches to Montgomery. \htriangle{xred} 

\textbf{Answer}: Selma,\ Alabama\\
\htriangle{xred} New York City
\end{frame}

\begin{frame}{Packet F1 Question 14}
Late in his reign, this man repulsed an Arab raid in the Battle of Akroinon. This ruler married his daughter Anna to his ally Artabasdos, who  \tcircle{xgreen} nevertheless tried to seize the throne upon this man’s death. He came to power when he repulsed the Second Arab Siege of Constantinople, thus ending the Twenty Years’ Anarchy. The Patriarch of Constantinople  \tsquare{xgreen} Germanus I resigned  \tdiamond{xgreen} rather than  \ttriangle{xgreen} enforce this man’s decree that forbade the veneration of images. The First Iconoclasm was instituted by, for 10 points, what Byzantine emperor who founded the Isaurian Dynasty?

\textbf{Answer}: Leo\ III\ the\ Isaurian\\
\end{frame}

\begin{frame}{Packet F1 Question 15}
A Norman king of Sicily  \tsquare{xred} used this campaign as a distraction to send seventy galleys to take Kerkyra. A commander in this campaign divided his forces into a unit that was repulsed at the Second Battle of Dorylaeum and a unit under Otto of Freising that was routed near Laodicea. Eugene  \tcircle{xgreen} III announced the  \hsquare{xgreen} bull Quantum praedecessores to call for this campaign after the fall of Edessa. Bernard of Clairvaux  \ttriangle{xgreen} preached in support of this campaign,  \tdiamond{xgreen} in which European forces were led by Conrad III and Louis VII. For 10 points, name this religious campaign that ended in a disastrous siege of Damascus.

\textbf{Answer}: Second\ Crusade\\
\tsquare{xred} William the Conqueror
\end{frame}

\begin{frame}{Packet F1 Question 16}
A politician from this party negotiated the  \tsquare{xred} sale of the Leuna oil refinery to the French conglomerate Elf Aquitaine. This party accepted secret contributions from arms dealers and lobbyists- partly in exchange for allowing Thyssen to export tanks to Saudi Arabia- as part of a namesake “donations scandal” that unseated its leadership in 2000. This party facilitated  \hsquare{xgreen} a post-World War Two “economic miracle” under chancellor Konrad Adenauer. Helmut  \tdiamond{xgreen} Kohl was succeeded by Angela Merkel as the leader of,  \htriangle{xgreen} for 10 points, what center-right Germany political party that often aligns with the Christian Social Union? \hcircle{xred} 

\textbf{Answer}: Christian\ Democratic\ Union\ of\ Germany\\
\tsquare{xred} Jeremy Corbyn
\hcircle{xred} Socialist Party (France)
\end{frame}

\begin{frame}{Packet F1 Question 17}
On holidays this location  \tsquare{xred} is home to a group of portraits known as ``the history of shaving.'' Its notoriety instigated a statement of ``Attitudes and Demands'' that shuttered the World  \hsquare{xgreen} Economic Herald. Leaders called for a hunger strike at this location near a massive bulletin board nicknamed “The Triangle.” A papier-mache statue of a woman grasping a torch that was constructed at this location is known as the Goddess of Democracy. A lone person stands in front of a column of armored vehicles in this location in the photograph  \hdiamond{xgreen} “Tank Man.” Deng Xiaoping ordered  \tcircle{xgreen}  \ttriangle{xred} troops to fire on student protestors in, for 10 points, what Beijing location, the site of 1989 demonstrations?

\textbf{Answer}: Tiananmen\ Square\\
\tsquare{xred} New Year
\ttriangle{xred} Kunlun Mountains
\end{frame}

\begin{frame}{Packet F1 Question 18}
Blood clots in these organs  \tcircle{xred}  \tsquare{xred} can be detected using a V-Q scan. The presence of fibrous tissues in these organs can produce  \hsquare{xgreen} a pattern on a CT scan termed “honeycombing.” In men, the most common cause of death from cancer occurs  \ttriangle{xred} in these organs, one variety of which is the asbestos-caused mesothelioma. Long-term exposure to heavy pollution can cause a disease of  \hdiamond{xgreen} these organs alternately called COPD or emphysema. Tobacco smoking can seriously damage, for 10 points, what organs that are impacted by pulmonary fibrosis?

\textbf{Answer}: Lung\\
\tcircle{xred} Platelet
\tsquare{xred} Platelet
\ttriangle{xred} Testicle
\end{frame}

\begin{frame}{Packet F1 Question 19}
Translocations of MLL,  \tsquare{xred}  \ttriangle{xred} which regulates these genes in humans,  \hdiamond{xgreen}  \tcircle{xgreen}  \htriangle{xgreen} often cause aggressive, fatal leukemias in children. Many of these proteins prefer to bind DNA that contains the sequence TAAT. In many organisms,  \hsquare{xgreen} these genes are expressed in the same order as they appear on the chromosome. They are regulated by gap and pair-rule genes in Drosophila, who possess eight of these genes. Antennae and limbs grow in their proper places because of, for 10 points, what genes that control the anterior-posterior axis of a developing animal, which are a subset of `homeobox' genes?

\textbf{Answer}: Hox\ gene\\
\tsquare{xred} Chromosomal inversion
\ttriangle{xred} Chromosomal inversion
\end{frame}

\begin{frame}{Packet F1 Question 20}
An application of this law suggests that hydrogen fuel pipelines would often develop problematic, microscopic leaks. Though today often replaced with centrifuges, an application of this law was the basis for the separation of uranium 235 from uranium 238 during the Manhattan Project. Unlike Fick’s Laws,  \tsquare{xred}  \htriangle{xgreen} this law can govern a process that occurs through a hole  \tcircle{xred} whose diameter is smaller than the mean free path of some given particles. For 10 points, name this law which states that the rate of effusion for two gases is  \hsquare{xgreen} inversely proportional to the square root  \tdiamond{xgreen} of their molar masses.

\textbf{Answer}: Graham's\ law\\
\tsquare{xred} Plutonium
\tcircle{xred} Second law of thermodynamics
\end{frame}

\begin{frame}{Packet F1 Question 21}
The thesis of Hendrika Johanna van Leeuwen  \tsquare{xred} rediscovered a proof  \tcircle{xred} that this cannot exist under classical physics. It occurs at positive values of the integral function J sub A B, and is correlated with the strength of A, the exchange stiffness constant, in a Hamiltonian model developed by Heisenberg. A lattice of +1 and -1 spins models this phenomenon in a paradigm whose two-dimensional version was solved by Lars Onsager,  \hcircle{xgreen}  \ttriangle{xred} the Ising Model. Alnico alloys display high levels of this property, as they are composed of aluminum, nickel, cobalt,  \tdiamond{xgreen}  \hsquare{xgreen} or iron. For 10 points, name this property which disappears  \htriangle{xgreen} at temperatures above the Curie Point in permanent magnets.

\textbf{Answer}: Ferromagnetism\\
\tsquare{xred} Theo van Gogh (film director)
\tcircle{xred} Niels Bohr
\ttriangle{xred} Ising model
\end{frame}

\begin{frame}{Packet F1 Question 22}
The oldest fossil of the  \ttriangle{xred} eutherian clade of  \tsquare{xred} mammals is a Chinese shrew that has been  \tcircle{xred} dated to this period. The Aurornis genus lived during this period. The Sundance Sea existed as an  \hcircle{xgreen}  \hsquare{xgreen} extension of the Arctic Ocean during this period, and sediments  \htriangle{xgreen} along its shores gradually created the fossil-rich Morrison Formation. The Archaeopteryx genus, which is sometimes considered the first bird, lived during this period, in which Allosaurus sometimes preyed upon Stegosaurus.  \tdiamond{xgreen} For 10 points, name this period that followed the Carboniferous and preceded the Triassic.

\textbf{Answer}: Jurassic\\
\ttriangle{xred} Taung Child
\tsquare{xred} Amniote
\tcircle{xred} Placenta
\end{frame}

\begin{frame}{Packet F1 Question 23}
The coalescent named by  \tsquare{xred}  \ttriangle{xred} this letter is an  \hdiamond{xgreen} instance of lambda coalescents and a generalization of Kingman's.  The substrate in a process partly named for this letter is carried to its destination by a carnitine shuttle. A protein family partly  \tcircle{xred} named for this letter provides hardness  \htriangle{xgreen} to the scales, shells, and skin of reptiles. The most common type of carotene in  \hcircle{xgreen}  \hsquare{xgreen} plants is named for this letter. A “sheet” named for this letter is a regular secondary structure in proteins. Fatty acids are broken down by an oxidation named after, for 10 points, what Greek letter that can refer to the second carbon to attach to a molecule, after the alpha carbon?

\textbf{Answer}: Beta\\
\tsquare{xred} Crow Creek massacre
\ttriangle{xred} Crow Creek massacre
\tcircle{xred} Gamma
\end{frame}

\begin{frame}{Packet F1 Question 24}
A piece that highlights this instrument has a second movement larghetto in D major, which is followed by a minuet whose second trio is based on a landler peasant dance. A piece intended for this instrument includes no cadenzas, instead opting for three short eingangs that allow improvisation while the accompaniment holds a dominant chord. Mozart wrote a trio in E flat for instrument, as well as a concerto and a quintet for this instrument  \htriangle{xgreen} in A major for Anton Stadler. For 10 points,  \tcircle{xgreen}  \tsquare{xgreen} name this woodwind instrument that today usually plays  \tdiamond{xgreen} in B flat.

\textbf{Answer}: Clarinet\\
\end{frame}

\begin{frame}{Packet F1 Question 25}
A musical genre developed in this country, the semi-opera, is sometimes performed today as an opera or  \tcircle{xred} a ballet. A dancer from this country adapted the music of Cesar Franck into his ballet Symphonic Variations. Enrico Cecchetti founded a ballet school in this country in 1918. Ninette de Valois essentially founded the leading ballet company in this country. After  \tsquare{xred} leaving Russia, Anna Pavlova lived the rest of her life in this country. Frederick Ashton choreographed many productions in this country. For 10 points, name this country where ballets are staged in Covent Garden. \hdiamond{xred}  \htriangle{xred} 

\textbf{Answer}: Great\ Britain\\
\tcircle{xred} Henry Purcell
\tsquare{xred} Bolshoi Ballet
\hdiamond{xred} Russia
\htriangle{xred} France
\end{frame}

\begin{frame}{Packet F1 Question 26}
A martyrs’ monument commissioned  \tsquare{xred} by this empire consists of a  \htriangle{xgreen} column with a broken white marble top and a large, bronze laurel branch. The Fossati Brothers were employed as architects primarily by this  \hdiamond{xgreen} empire. This empire constructed Kulliye  \tcircle{xred} centers that contained houses of worship and facilities to provide food for the poor. A religious building constructed by this empire in the early 1600s is named for its many blue tiles. The architect Sinan was employed by, for 10 points, what empire that converted the Hagia Sophia into a mosque after the conquest of Constantinople?

\textbf{Answer}: Ottoman\ Empire\\
\tsquare{xred} Washington Monument
\tcircle{xred} Inca Empire
\end{frame}

\begin{frame}{Packet F1 Question 27}
Henry argues that the Jayamala is an increasingly common part of this event because of videography. Sometimes, this event includes a symbolic brushing away of defects by using a blade of darbha grass to wipe a woman’s eyebrows. A woman in this event places her foot on a block of granite while a man reads prayers for strength. A participant in this event ties an “auspicious thread,” or mangalsutra, around a woman’s neck. The two main participants in this event take seven steps while making promises around a holy fire that symbolizes Agni.  \tdiamond{xgreen}  \tcircle{xgreen} That Saptapadi ritual  \tsquare{xgreen}  \ttriangle{xgreen} occurs during, for 10 points, what event in which the bride may wear a sari?

\textbf{Answer}: Hindu\ wedding\\
\end{frame}

\begin{frame}{Packet F1 Question 28}
The blood of one of these animals killed a man who lusted after Iole, the princess of Oechalia. One of these animals named Eurytion caused a conflict when he abducted the bride Hippodamia. In one story,  \tcircle{xgreen} these creatures are born when Ixion copulates  \tsquare{xgreen} with the cloud Nephele. After consuming wine at the wedding of Pirithous,  \tdiamond{xgreen} these animals fought a namesake war with the Lapiths. One of these animals served as the tutor of Achilles and many other mythological heroes. Nessus and Chiron are, for 10 points, which animals that have a human’s upper body and a horse’s lower body? \htriangle{xred} 

\textbf{Answer}: Centaur\\
\htriangle{xred} Horse
\end{frame}

\begin{frame}{Packet F1 Question 29}
In Serbian tradition, these objects were sometimes  \tsquare{xred} buried with corpses to prevent a spirit from wandering out of its grave. After a god partly named for these objects  \htriangle{xgreen} turns into the sun, his rival knocks him from the sky using a stone club. One of these objects “of Eight Ta” is joined by a sword and a jewel in the Imperial Regalia of Japan. Tezcatlipoca’s right foot was depicted as one of these objects, which were usually made from obsidian in Mesoamerica. A  \tdiamond{xgreen} “magic” one of these  \tcircle{xgreen} objects is asked “who is the fairest one of all” in the story of Snow White. For 10 points, name these reflective surfaces.

\textbf{Answer}: Mirror\\
\tsquare{xred} Marina Abramović
\end{frame}

\begin{frame}{Packet F1 Question 30}
In section 42 of Being  \tsquare{xred} and Time, Martin Heidegger  \ttriangle{xred} builds upon this earlier thinker’s idea that nature perfects the good of god, but care perfects the good of a human being. This man wrote that “I cannot now influence so strong a grief by polite and mild measures: it must be broken down by force” in a “consolation” written to a friend who lost her son, Marcia. This author, whose tract On Mercy originated the genre of “mirror of the princes,” wrote the Moral Epistles to his friend Lucilius. For 10 points,  \tdiamond{xgreen} name this Stoic philosopher who served  \hcircle{xgreen} as Nero’s tutor.

\textbf{Answer}: Seneca\ the\ Younger\\
\tsquare{xred} Tisha B'Av
\ttriangle{xred} Martin Heidegger
\end{frame}

\begin{frame}{Packet F1 Question 31}
The title of a book by a Cambridge historian uses it to explain the interaction between evidence and realism. Its existence is presented as a paradox in ``The Internal Basis of Meaning'' by a Wayne State philosopher. Saul Kripke used a statement defining this substance as an example  \htriangle{xgreen} of a theoretical identity  \tsquare{xred} statement. In a thought experiment that supports semantic externalism, Hilary  \tcircle{xred} Putnam imagined a “twin earth” that  \ttriangle{xred} was identical to earth in every way except that this substance is replaced with  \hcircle{xgreen} “XYZ.” Heraclitus said that one cannot step into the same area containing this substance twice. For 10 points, name this substance that, along with air, earth,  \tdiamond{xgreen} and fire, was one of the classical elements.

\textbf{Answer}: Water\\
\tsquare{xred} Naming and Necessity
\tcircle{xred} Hilary Putnam
\ttriangle{xred} Hilary Putnam
\end{frame}

\begin{frame}{Packet F1 Question 32}
In 2018, this state rejected  \tsquare{xred} Proposition 1, which would have increased the homestead exemption from fifty thousand to seventy-five thousand dollars. A former governor of this state who won its senate seat in 2018 is nicknamed “Red Tide” for cutting water management funds prior to an algal bloom. This state re-enfranchised 1.5 million ex-felons in 2018. Also in 2018, Rick Scott defeated  \hdiamond{xgreen}  \htriangle{xgreen} the Democrat  \hsquare{xgreen} incumbent Bill Nelson to win a senate seat in this state, where Ron DeSantis was  \tcircle{xred} elected governor. For 10 points, name this state whose government meets in Tallahassee.

\textbf{Answer}: Florida\\
\tsquare{xred} Space telescope
\tcircle{xred} Arizona
\end{frame}

\begin{frame}{Packet F1 Question 33}
A major center for the production of these objects in Japan is the Shima Peninsula in Mie Prefecture. In 2017, it was reported that a population of ivory-billed woodpeckers may still be alive near a river of this name, which flows past Jackson, Mississippi. The Bocca Tigris strait is in the delta of a different river of this name, whose shores  \ttriangle{xred} contain the city of Guangzhou. The Hickam Air Force Base joined with a naval base partly named for these objects, where tourists can visit the memorial to the USS Arizona. For  \hcircle{xgreen} 10 points, give these objects that name a Hawaii “harbor.” \hdiamond{xred}  \hsquare{xred} 

\textbf{Answer}: Pearl\\
\ttriangle{xred} List of rivers of Colorado
\hdiamond{xred} Ceratitis capitata
\hsquare{xred} Oahu
\end{frame}

\begin{frame}{Packet F1 Question 34}
Joel  \tcircle{xred} Robuchon’s restaurant in this city is his only dining establishment  \tsquare{xred} in North America to receive three Michelin stars. Julian Serrano is the executive chef of a restaurant in this city whose walls contain reproductions of Picasso’s paintings. Giada de Laurentiis opened her first, flagship restaurant in this city. Mario Batali’s three restaurants in this city, including Carnevino Steakhouse, closed in this city in 2018 after he was accused of sexually inappropriate behavior. For 10 points, name this Nevada city where  \tdiamond{xgreen} many restaurants are found in casinos along the Strip. \htriangle{xred} 

\textbf{Answer}: Las\ Vegas\\
\tcircle{xred} Symmetric matrix
\tsquare{xred} T.G.I. Friday's
\htriangle{xred} New York City
\end{frame}

\begin{frame}{Packet F1 Question 35}
The main character of this movie becomes upset with a woman when she puts on Bach’s sinfonia on a radio. A character in this movie recognizes a woman’s identity when he notices she is wearing Carlotta Valdes’s necklace. This film pioneered a technique in which a camera zooms in on  \tcircle{xgreen} a subject while being pulled away from the subject, called the Dolly Zoom. In this  \hdiamond{xgreen} film, a detective follows a woman into a bell tower at a  \tsquare{xgreen} California mission, but his fear of heights prevents him from  \ttriangle{xgreen} following her to the top. For 10 points, name this movie directed by Alfred Hitchcock.

\textbf{Answer}: Vertigo\\
\end{frame}

\begin{frame}{Packet F1 Question 36}
The narrator of this novel chastises two of his friends as “careless people” who “smashed up things and creatures and then... let other people clean up the mess they had made.” A woman in the final chapter of this novel recalls a time when the narrator told her that “a bad driver was only safe until she met another bad driver.” In its last chapter, this novel’s narrator learns that one of his friends told a man holding a revolver the identity of a man driving a yellow car before he reflects upon the meaning of a “green light” on a dock  \hdiamond{xgreen}  \tcircle{xgreen} in East Egg. For 10 points, name this novel  \ttriangle{xred} narrated by Nick Carraway. \hsquare{xred} 

\textbf{Answer}: The\ Great\ Gatsby\\
\ttriangle{xred} My Life in the Bush of Ghosts (novel)
\hsquare{xred} The Great Gatsby
\end{frame}

\begin{frame}{Packet F1 Question 37}
Rivkah Harris argued that this man ushered in a period of ``secularization'', and Breckwoldt studied falling grain prices which earned him the nickname “bani matim,” or builder of the land. This man subjugated the Assyrian ruler Ishme-Dagan I and conquered the rival states of Larsa,  \tcircle{xgreen} Eshnunna, and Elam.  \tsquare{xgreen}  \ttriangle{xgreen} In 1901, Gustave Jequier unearthed a stele bearing a decree promulgated by this ruler in Susa. This ruler declared that a man who breaks the bone of a freeman should pay him a gold mina, which is less severe than his statement “an eye for an eye.” For 10 points, give this Babylonian ruler who developed  \tdiamond{xgreen} a namesake law code. 

\textbf{Answer}: Hammurabi\\
\end{frame}

\begin{frame}{Packet F1 Question 38}
An art museum in this  \tsquare{xred} city consists of two buildings with limestone paneling connected by an above-ground glass box. That museum, completed in 2012 by Tod Williams and Billie Tsien, houses the collection of the Barnes Foundation. In a painting set in this city, the Girard Avenue Bridge appears in the distance behind a man in a long, racing rowboat. Max Schmitt in a Single Scull depicts  \hdiamond{xgreen} a waterway in this city, which today houses the paintings The Agnew Clinic and The Gross Clinic.  \tcircle{xred} For 10 points, name this primary workplace of Thomas Eakins. \htriangle{xred} 

\textbf{Answer}: Philadelphia\\
\tsquare{xred} Solomon R. Guggenheim Museum
\tcircle{xred} Thomas Eakins
\htriangle{xred} New York City
\end{frame}

\begin{frame}{Packet F1 Question 39}
In 2017, the USS John McCain collided with a merchant ship near this body of water. This body of water is at its narrowest point at Phillip’s Channel. The exclave of Cape Rachado is in this body of water, and is part of a state that is located to the northwest of Johor. This waterway connects the Andaman  \tsquare{xred} Sea to the South China Sea. Plans to construct the Kra Canal, which would relieve heavily congested shipping traffic through this body of water, are yet to be implemented by Thailand. For 10 points, identify this straight on which Singapore can be found. \hdiamond{xred}  \hcircle{xred}  \htriangle{xred} 

\textbf{Answer}: Strait\ of\ Malacca\\
\tsquare{xred} English Channel
\hdiamond{xred} North Sea
\hcircle{xred} English Channel
\htriangle{xred} Indian Ocean
\end{frame}

\begin{frame}{Packet F1 Question 40}
People engage in this process because of profit, but ignore the relation of misery it causes, according to a 1957 book which holds that people who engage in this process experience self-hatred via a “Nero Complex.” A new society is founded in the “settler” variety of this process, which names the magnum opus of Albert Memmi. The period of time after this process occurs names a discipline  \tsquare{xgreen} of study partly founded by Franz Fanon and Edward Said. For 10 points, name this process by which an imperial power  \tdiamond{xgreen} extends military  \tcircle{xred} and economic dominance over other polities. \htriangle{xred} 

\textbf{Answer}: Colonization\\
\tcircle{xred} Convection
\htriangle{xred} Coagulation
\end{frame}

\begin{frame}{Packet F1 Question 41}
Thomas Cousineau’s An Unwritten Novel is about a book from this country in which an accountant for a textile company compiles anecdotes into a autobiography devoid of facts. An author from this country wrote a novel in which a woman who eats raw rabbits is found living in the home of the girl with dark glasses. The Book of Disquiet is from  \tcircle{xgreen} this country, as is a novel in which the Doctor’s Wife is the only character not affected by a sudden debilitating illness. For 10 points, name this birthplace of Fernando Pessoa and  \tdiamond{xgreen}  \tsquare{xgreen} the author of Blindness, José Saramago. \htriangle{xred} 

\textbf{Answer}: Portugal\\
\htriangle{xred} Japan
\end{frame}

