\begin{frame}{Packet F3 Question 1}
In 2018, the FDA approved  \ttriangle{xred} Merck’s drugs Delstrigo  \tsquare{xred} and Pifeltro to treat this disease, noting that they caused a surprising positive side effect of lowering cholesterol. It is often treated using a cocktail of protease and integrase inhibitors. Burroughs-Wellcome marketed the first drug used to treat this disease, which is alternately called ZDV or AZT. Maraviroc, a drug used to treat  \tcircle{xgreen} this disease, targets the CCR5 receptor on helper T-cells.  \tsquare{xyellow} Reverse transcriptase inhibitors and antiretrovirals are commonly used to treat, for 10 points, what sexually transmitted disease? \tdiamond{gray}  \ttriangle{gray} 

\textbf{Answer}: HIV\\
\ttriangle{xred} Space telescope
\tsquare{xred} Proton-pump inhibitor
\tdiamond{gray} Homeopathy
\ttriangle{gray} Space telescope
\end{frame}

\begin{frame}{Packet F3 Question 2}
The final step of one reaction of this type converts raney nickel  \tcircle{xred}  \tsquare{xyellow} into two nickel  \tdiamond{xyellow} disulfides and is named for a Merck chemist, Mozingo. Another  \ttriangle{xyellow} of these reactions creates a cyclohexadiene from an aromatic ring, and is commonly performed in liquid ammonia. Usually, a hydrazone is formed and nitrogen gas  \tsquare{xred} is emitted in two intermediate steps of one of these reactions named for Wolff and Kishner. Hydrogenations are a type of, for 10 points, what reactions in which a compound gains electrons, and which are commonly contrasted with oxidations? \tcircle{gray} 

\textbf{Answer}: Reductions\\
\tcircle{xred} Nickel
\tsquare{xred} Hydrogenation
\tcircle{gray} Nickel
\end{frame}

\begin{frame}{Packet F3 Question 3}
A discovery involving its parity was awarded  \tsquare{xyellow} the first Wolf Prize in Physics, and was identified in an experiment in which Wú Jiànxióng cooled a cobalt isotope using adiabatic demagnetization. This interaction can be classified  \tcircle{xgreen} using Wolfenstein parameters as part of an analysis using CKM matrices. Cronin  \tsquare{xred} and Fitch showed that it violates CP symmetry by analyzing neutral kaons that  \tdiamond{xred} decayed into antiparticles. The electromagnetic force was  \ttriangle{xgreen} unified with, for 10 points, what fundamental force that causes beta decay? \tdiamond{xgreen} 

\textbf{Answer}: Weak\ interaction\\
\tsquare{xred} Wu experiment
\tdiamond{xred} CP violation
\end{frame}

\begin{frame}{Packet F3 Question 4}
This leader provided funding for and once  \tsquare{xred} named a massive mosque in Kampala, Uganda, whose construction  \tcircle{xred} had been discontinued in 1976. This man and his followers instigated the One September Revolution by enacting Operation Jerusalem. The king Idris was overthrown  \tsquare{xyellow} by this man, who styled himself a “brotherly leader” and outlined his political philosophy in The Green Book. This man  \ttriangle{xgreen} was killed near Sirte  \tdiamond{xgreen} during a 2011 revolution in which he was deposed as part of the Arab Spring.  \tcircle{xyellow} For 10 points, name this longtime dictator of Libya.

\textbf{Answer}: Muammar\ Gaddafi\\
\tsquare{xred} National Geographic Society
\tcircle{xred} Idi Amin
\end{frame}

\begin{frame}{Packet F3 Question 5}
This philosopher originated the line of reasoning that it is rational to ask what the place of an object is, but it is not rational to ask what the place of a place is. Book VI of Aristotle’s Physics is largely about this thinker, and discusses his analysis of three groups of people in three rows running past each other in a stadium. This thinker shares his name with a later philosopher from Citium who founded the Stoic philosophical school. An arrow that is frozen in time was discussed by, for 10 points, what Greek philosopher who outlined  \ttriangle{xred} many paradoxes? \tdiamond{xgreen}  \tcircle{gray}  \tsquare{xgreen}  \ttriangle{gray} 

\textbf{Answer}: Zeno\ of\ Elea\\
\ttriangle{xred} Aristotle
\tcircle{gray} John Dewey
\ttriangle{gray} Aristotle
\end{frame}

\begin{frame}{Packet F3 Question 6}
Selmer Bringsjord articulated strategies to judge if this were passed, including asking  \ttriangle{xred} participants to  \tcircle{xred} write a short story. Levesque, Davis, and Morgenstern propose an alternative: resolving referential ambiguities called the Winograd Schema Challenge. Mark Halpern’s “The Trouble with” ~this~ criticized the Loebner prize. Searle’s Chinese  \ttriangle{xyellow} Room argues that it, along with all strong AI, did not imply consciousness. Name this thought experiment derived from “the imitation game” that  \tdiamond{xyellow}  \tsquare{xgreen} asks a judge to determine whether a conversational partner  \tcircle{xyellow} is human or computer named for a British computer scientist and that, for ten points, is said to determine when a computer is intelligent.

\textbf{Answer}: Turing\ test\\
\ttriangle{xred} Maharashtra
\tcircle{xred} Game theory
\end{frame}

\begin{frame}{Packet F3 Question 7}
He was the head of a military band at Richmond  \tsquare{xred} for the Earl of Darlington and later the organist at the Octagon Chapel in Bath. In unpublished notes taken in May 1776, he claimed to see forests on the moon. His name is attached to an off-axis telescope that tilts  \tdiamond{xyellow} the primary mirror to prevent observer obstruction. His first paper was on the variable star Mira Ceti, and on March 13, 1781 he recorded  \tsquare{xyellow} a comet that was moving at 2.25 seconds per hour. After failing to find a tail,  \tcircle{xyellow} the object was called Georgium Sidus. Assisted by his sister Caroline, for ten points  \ttriangle{xgreen} name this German-British discoverer of Uranus.

\textbf{Answer}: William\ Herschel\\
\tsquare{xred} Alan Grayson
\end{frame}

\begin{frame}{Packet F3 Question 8}
A discipline founded by this man originated so-called “time-and-motion” studies. This man argued for the creation of separate “planning offices” that popularized the modern conceptualization of bulletin boards. A colleague and ideological associate of this man, Henry Gantt, developed a chart for plotting  \tsquare{xred} the time frames for the completion of sequential tasks. He argued for the adoption of universal shovel sizes and developed a tungsten-cutting technique while working at Bethlehem Steel. For 10 points,  \tdiamond{xyellow}  \ttriangle{xred} name this founder of scientific management. \tcircle{gray}  \tsquare{xgreen}  \ttriangle{xgreen} 

\textbf{Answer}: Frederick\ Winslow\ Taylor\\
\tsquare{xred} Scientific management
\ttriangle{xred} Scientific management
\tcircle{gray} Claude Lévi-Strauss
\end{frame}

\begin{frame}{Packet F3 Question 9}
A lower-bound temperature  \tcircle{xred}  \tsquare{xred} named for this phenomenon is equal to Plank’s constant times the spectral linewidth  \tcircle{xyellow} over two times Boltzmann’s constant, and can be exceeded using an optical molasses. Collisions lessen the effect of this phenomenon on spectral lines in the Dicke effect, thus narrowing the impact of this phenomenon’s namesake “broadening.” It names a commonly used form of laser cooling. Ives and Stilwell measured  \tsquare{xyellow} the “transverse”  \tdiamond{xgreen} form of, for 10 points, what change in frequency of a wave  \ttriangle{xyellow} caused by the relative motion of an observer and a source?

\textbf{Answer}: Doppler\ effect\\
\tcircle{xred} Egg
\tsquare{xred} Egg
\end{frame}

\begin{frame}{Packet F3 Question 10}
This artist probably depicted himself with blond hair and a yellow cloak on the far right of a painting that shows Mary and the infant Jesus inside some Roman ruins. Twelve angels represent the privileges of Mary in a painting by this artist, in which angels in white, red, and green robes are placed on a rooftop. This artist included many members of the Medici family in his Adoration of the Magi and  \tdiamond{xgreen} painted The Mystic Nativity. He showed  \tcircle{xgreen}  \tsquare{xgreen} the Graces standing to the left of Venus in a painting set in an orange grove. For  \ttriangle{xgreen} 10 points, name this Italian Renaissance artist of Primavera.

\textbf{Answer}: Sandro\ Botticelli\\
\end{frame}

\begin{frame}{Packet F3 Question 11}
An essay titled for this concept expands upon Wilhelm von Humboldt’s assertion that a “variety of situations” is necessary for human development. An essay partly titled for this concept claims that Stoics and Buddhists seek self-mastery through  \tdiamond{xyellow}  \tcircle{xgreen} self-denial in its discussion of the “Retreat to the Inner Citadel.” A 1958 Oxford lecture analyzed the “positive” and “negative” varieties of this concept. It titles an 1859 essay the formalized the “harm principle.”  \tsquare{xgreen}  \ttriangle{xgreen} An Isaiah Berlin essay is titled “Two Concepts of,” for 10 points, what subject of a John Stuart Mill essay?

\textbf{Answer}: Liberty\\
\end{frame}

\begin{frame}{Packet F3 Question 12}
This composer’s writings refer to his closeted homosexuality using  \tsquare{xred} the letter “z” and the phrase “xxx.” In a symphony by this composer, the andante second movement contains a horn solo shortly after the key shifts from B minor to D major. This composer, who was patronized for thirteen years by Nadezhda von Meck, included a bassoon solo marked  \tcircle{xgreen} with six “p”s and a 5/4 “limping waltz” in his final symphony,  \ttriangle{xyellow} which premiered just over a week before  \tdiamond{xgreen} his death. For 10 points, what Russian composer’s sixth symphony in B minor is nicknamed “Pathetique”? \tsquare{gray} 

\textbf{Answer}: Pyotr\ Ilyich\ Tchaikovsky\\
\tsquare{xred} Fun Home
\tsquare{gray} Fun Home
\end{frame}

\begin{frame}{Packet F3 Question 13}
The loss of pericytes can lead to weakness and damage to these structures, which can in turn lead to retinopathy and blindness. Inhibiting the new development of these structures--for instance, by targeting VEGF--is central to a class of cancer-fighting drugs called angiogenesis inhibitors. In these structures, buildup of  \tsquare{xred} plaques can lead to atherosclerosis and, in the long term, stroke. These structures release nitric oxide to relax smooth  \tsquare{xyellow} muscles cells and induce vasodilation. For ten points, name  \tcircle{xgreen} these structures responsible for shuttling endocrine hormones and erythrocytes around the body. They include capillaries, arteries, and veins. \tdiamond{gray}  \ttriangle{gray} 

\textbf{Answer}: Blood\ vessel\\
\tsquare{xred} Macular degeneration
\tdiamond{gray} Vein
\ttriangle{gray} Leaf
\end{frame}

\begin{frame}{Packet F3 Question 14}
An island in this river contains a Holocaust memorial in which 200,000 lights can be viewed in an underground chamber, the Memorial to the Martyrs of the Deportation. Richard the Lionheart ordered the construction of the Gaillard fortification on the banks of this river. This river’s  \tcircle{xred} mascaret tidal bore  \tdiamond{xgreen}  \tsquare{xgreen} was eliminated through continual dredging starting in the  \tcircle{xyellow} 1860s. The Oise River is a tributary of this river, which is naturally navigable by seagoing vessels as far as Rouen after they pass by the port of Le Havre. For 10 points, what river is crossed by the Pont Neuf in Paris? \ttriangle{gray} 

\textbf{Answer}: Seine\\
\tcircle{xred} Nile
\ttriangle{gray} Ohio River
\end{frame}

\begin{frame}{Packet F3 Question 15}
The MyZeil shopping center in this city designed Massimiliano Fuksas resembles a Klein bottle.  In 1909, the world's first airline, DELAG, was founded in this city, and this city was the origin of the Hindenburg.  The headquarters for IG Farben, the Poelzig Building, was the site of the Headquarters of the Allied European Forces and is now the main lecture hall of Goethe University.  The ten tallest buildings in Germany are located in this city, including the tallest, Commerzbank Tower.  For 10 points, name this Hessian city, the commercial center of Germany on the Main River. \tdiamond{gray}  \tcircle{gray}  \tsquare{gray}  \ttriangle{gray} 

\textbf{Answer}: Frankfurt\\
\tdiamond{gray} Dubai
\tcircle{gray} New York City
\tsquare{gray} Shanghai
\ttriangle{gray} New York City
\end{frame}

\begin{frame}{Packet F3 Question 16}
A technique named for these organisms has been used to develop monoclonal antibody drugs such as adalimumab. The presence  \tsquare{xred} of these organisms did not cause mutations in the Luria-Delbruck Experiment. George  \tcircle{xgreen} Smith shared the 2018 Nobel in chemistry for developing a “display” technique named for these organisms, which were tagged with radioactive sulfur and phosphorus  \tdiamond{xgreen} to show that DNA  \tsquare{xyellow} carried genetic material in the Hershey-Chase Experiment.  \ttriangle{xgreen} T2 and lambda are varieties of, for 10 points, what type of viruses that target bacteria?

\textbf{Answer}: Bacteriophage\\
\tsquare{xred} Rheumatoid arthritis
\end{frame}

\begin{frame}{Packet F3 Question 17}
His aliases include: Pastor  \tsquare{xred} Hansford of Free Will Baptist in Coushatta, Louisianna; Viktor with a K St. Claire, a South African who just inherited money from his uncle; Charlie Hustle, a mailboy in the HHM mailroom; and Gene Takavic, a Cinnabon manager in Omaha. His best known alias came from selling burner phones in Albuquerque, New Mexico and was more fitting for a lawyer than his birthname, James McGill. For ten points, name this titular CRIMINAL lawyer from an AMC series who originated on Breaking Bad. \tdiamond{gray}  \tcircle{gray}  \tsquare{gray}  \ttriangle{gray} 

\textbf{Answer}: Better\ Call\ Saul\\
\tsquare{xred} Julius and Ethel Rosenberg
\tdiamond{gray} Saul Goodman
\tcircle{gray} French language
\tsquare{gray} Julius and Ethel Rosenberg
\ttriangle{gray} Ansel Adams
\end{frame}

\begin{frame}{Packet F3 Question 18}
Zebulon Vance staunchly opposed a conscription order issued by this man. This man took up residence at the Brierfield Plantation after marrying Sarah Knox Taylor, the daughter of future  \tdiamond{xyellow} president Zachary. As Secretary of War, he oversaw the construction of the Washington Aqueduct and argued in support of the Gadsen purchase during the presidency of Franklin Pierce. He assumed his  \tcircle{xgreen} highest office after defeating Robert Toombs at a constitutional  \tsquare{xgreen} convention in Montgomery, Alabama in 1861. For 10 points,  \ttriangle{xgreen} name this first and only president of the Confederate States of America.

\textbf{Answer}: Jefferson\ Davis\\
\end{frame}

\begin{frame}{Packet F3 Question 19}
This novel includes an aside in which the voice of Socrates declares that knowledge and beauty both lead into an abyss. When confronted with a desperate thirst, this novel's main character buys some overripe strawberries from a street vendor; earlier, he feels the  \tcircle{xgreen} urge to travel after seeing a red-headed  \tsquare{xgreen} stranger in a Munich cemetery. In this novel, a jester assures a writer that sirocco is the only plague to fear despite police disinfecting an Italian city for cholera. Gustav  \ttriangle{xgreen} von Aschenbach becomes  \tdiamond{xgreen} obsessed with the Polish boy Tadzio in, for 10 points, what Thomas Mann novel?

\textbf{Answer}: Death\ in\ Venice\\
\end{frame}

\begin{frame}{Packet F3 Question 20}
In a novel by this author, a detective wraps his arm to survive a dog attack, thus obtaining a bullet identical to one used to kill the policeman Schmied. This author wrote a play in which yellow shoes symbolize how the town of Gullen turns against Anton Schill, who was once spurned by the rich woman Claire Zachanassian.  \tdiamond{xgreen}  \tsquare{xgreen} This author of The Judge and his Hangman wrote a play in which a scientist is hounded by spies who  \tcircle{xgreen} call themselves Einstein and Newton. For 10 points, name this Swiss author of The  \ttriangle{xyellow} Visit and The Physicists.

\textbf{Answer}: Friedrich\ Dürrenmatt\\
\end{frame}

\begin{frame}{Packet F3 Question 21}
The main character of a story by this author opens Crime and Punishment to a random page, but finds it to be a copy of The Brother Karamazov, and equates himself  \ttriangle{xred} with Monsieur Bovary. This author wrote a story in which the priest Naigu undergoes a boiling treatment to decrease the size of his nose. This  \tsquare{xgreen} author of ``Cogwheels'' wrote about two  \tdiamond{xgreen}  \tcircle{xgreen} people who steal to survive near the southern gate of Kyoto in a story that features inconsistent accounts from a woodcutter, a priest, a widow, and the ghost of a samurai. For 10 points, name this Japanese  \ttriangle{xyellow} author ``Rashomon.''

\textbf{Answer}: Ryūnosuke\ Akutagawa\\
\ttriangle{xred} Fyodor Dostoevsky
\end{frame}

\begin{frame}{Packet F3 Question 22}
In the last chapters of book set in this country, the narrator’s lover is killed in a Gipsy Moth plane that took off from the town of Voi. In another novel set in this country, the main character’s brothers kill Jacobo, a landowner supported by Mr. Howlands during a rebellion. Weep Not, Child is set in this country, as is a novel in which Mugo betrays one of his countrymen to the  \tdiamond{xyellow} British army. Denys Finch Hatton is a central  \tcircle{xgreen} character of a memoir set in this country by a Danish writer. For 10 points, name this setting of Karen Blixen’s Out of Africa and Ngũgĩ wa Thiong’o’s A  \tsquare{xgreen} Grain of Wheat. \ttriangle{gray} 

\textbf{Answer}: Kenya\\
\ttriangle{gray} India
\end{frame}

\begin{frame}{Packet F3 Question 23}
In G.K. Chesterton’s “The  \tsquare{xred} Invisible Man,`` Isidore Smythe’s ''Silent Service" provides these figures, one of which murders Moxon after losing a game of chess in a story by Ambrose Bierce. At the end of a play partly named for these figures, the  \tdiamond{xyellow} engineer Alquist realizes that two of them named Primus and Helena have fallen in love. Robbie, Speedy, and Cutie are examples of these figures from an author who created three laws governing their morality. A 1921 play that premiered in Prague coined the name of, for 10 points, what humanoids that feature in works by Karel Capek and Isaac  \ttriangle{xred} Asimov? \tcircle{gray}  \tsquare{gray}  \ttriangle{gray} 

\textbf{Answer}: Robot\\
\tsquare{xred} The Man Who Was Thursday
\ttriangle{xred} R.U.R.
\tcircle{gray} R.U.R.
\tsquare{gray} The Man Who Was Thursday
\ttriangle{gray} R.U.R.
\end{frame}

\begin{frame}{Packet F3 Question 24}
Ritchie Watson commended this play's historical accuracy for getting the price for a dozen eggs right- ten cents- to defend against Elizabeth Hardwick’s contention that it was a sentimental history. At the end of this play, a man wonders why a wheelchair is at the top of a staircase, and Alexandra announces that she is leaving her mother. Leo is pressured into stealing a set of valuable railroad bonds in this drama. In this play, which takes its title from the Song of Solomon, Regina Hubbard schemes  \tdiamond{xgreen}  \tcircle{xgreen} to obtain a majority share in a cotton mill. For 10 points,  \tsquare{xgreen}  \ttriangle{xgreen} name this play by Lillian Hellman.

\textbf{Answer}: The\ Little\ Foxes\\
\end{frame}

\begin{frame}{Packet F3 Question 25}
In Our Town, a character  \ttriangle{xred} with this given name explains Grover’s Corners’ place in the universe. In The Crucible, a character  \tcircle{xred} with this first name contends that the girls’ actions are part of their “silly seasons” and is the wife of Francis Nurse. A novel with this name, which conducts hidden messages to Rommel in The English Patient, is titled for a character who is killed in a boating accident at Manderley. For 10 points, give this name of a Daphne du Maurier  \tdiamond{xyellow}  \tsquare{xgreen} gothic novel which is also the first name of Miss Sharp, the protagonist of William Thackeray's Vanity Fair. \tcircle{gray}  \ttriangle{gray} 

\textbf{Answer}: Rebecca\\
\ttriangle{xred} Thornton Wilder
\tcircle{xred} Richard
\tcircle{gray} Richard
\ttriangle{gray} Thornton Wilder
\end{frame}

\begin{frame}{Packet F3 Question 26}
This author's poem once claimed that its first line referred to “All our scientific, democratic, fact-accumulating heterogeneous civilization.`` Initial drafts of this poem included a “winged beast” like that in its author's play On Baile's Strand. This poem lables ''A shape with lion body and the head  \tdiamond{xyellow} of a man`` as ''a vast image out of Spiritus  \ttriangle{xgreen} Mundi.`` This poem begins by describing  \tcircle{xgreen} ''Turning and turning in the widening gyre.`` For 10 points,  \tsquare{xgreen} name this W.B. Yeats poem that asks “what rough beast... Slouches towards Bethlehem to be born,'' one of numerous references to the apocalypse.

\textbf{Answer}: The\ Second\ Coming\ (poem)\\
\end{frame}

\begin{frame}{Packet F3 Question 27}
After this empire's final  \tsquare{xred} ruler was assassinated on a parade ground, its lands were invaded by Demetrius I, the Invincible.  \tcircle{xgreen} Strabo relates how Deimachus served for many years as an ambassador to this empire. A governing manual produced under this empire has a name that loosely translates as ``The Science of Politics.'' This empire's second ruler, Bindusara, appointed his son as viceroy of Ujjayini; that son conquered Kalinga before converting to Buddhism and promulgated  \tdiamond{xgreen}  \tsquare{xyellow} many edicts on stone pillars.  \ttriangle{xyellow} For 10 points name this Indian Empire led by Chandragupta and Ashoka.

\textbf{Answer}: Maurya\ Empire\\
\tsquare{xred} Arabs
\end{frame}

\begin{frame}{Packet F3 Question 28}
A congressman from this state added a set  \tcircle{xred} of namesake amendments to the Hepburn Act to facilite its passage through the senate. This state’s first republican governor, Ralph P. Lowe, practiced law with the man who became grant’s Secretary of War, William Belknap. Richard Bland co-names an act that restored bimetallism with a senator from this state, William Allison. A politician from this state served as Secretary of Agriculture for most of the Great Depression. Henry Wallace hailed from, for 10 points, what midwestern state where the cities of Davenport and Des Moines were founded? \tdiamond{gray}  \tcircle{gray}  \tsquare{xgreen}  \ttriangle{gray} 

\textbf{Answer}: Iowa\\
\tcircle{xred} California
\tdiamond{gray} California
\tcircle{gray} California
\ttriangle{gray} South Carolina
\end{frame}

\begin{frame}{Packet F3 Question 29}
An army that took its name from this geographical feature had a British doctor, James Paroissien, as its Surgeon General, and recent scholarship by Peter Blanchard revealed its use of slaves. That army crossed this geographical feature according  \ttriangle{xred} to Thomas Maitland’s  \tcircle{xred} plans at Uspallata and Los Patos. Spanish forces under Rafael Maroto were defeated in the foothills of these mountains by an army led by José de San Martín and Bernardo O'Higgins.  \tsquare{xred} For 10 points, name this mountain range of South America that played a role  \ttriangle{xyellow} in the independence of Chile. \tdiamond{gray}  \tcircle{gray}  \tsquare{gray} 

\textbf{Answer}: Andes\\
\ttriangle{xred} Angel Falls
\tcircle{xred} Mountain
\tsquare{xred} Battle of Chacabuco
\tdiamond{gray} Battle of Chacabuco
\tcircle{gray} Mountain
\tsquare{gray} Battle of Chacabuco
\end{frame}

\begin{frame}{Packet F3 Question 30}
A painting by this artist  \tsquare{xred} presents a tree as a cupboard with two doors, behind which are a white sphere and a miniature lighted house. A series of three paintings by this man shows a daytime sky with cumulus clouds above a dark house illuminated by a lamppost. This artist of Blood Will Tell and The Empire of Lights depicted a clock set to 12:43  \tcircle{xgreen} as a locomotive speeds out of a fireplace and a man in  \tsquare{xyellow} a bowler hat with an  \ttriangle{xgreen} apple in front of his face. For 10 points, name this Belgian surrealist painter  \tdiamond{xgreen} of the Son of Man and Time Transfixed.

\textbf{Answer}: René\ Magritte\\
\tsquare{xred} Argon
\end{frame}

\begin{frame}{Packet F3 Question 31}
Suetonius describes two gigantic boats commissioned by this ruler that were recovered from Lake Nemi and then destroyed by American and German crossfire in 1944. He levied a tax on prostitutes equal to the amount they charged for an embrace. This emperor ordered the construction of a massive pontoon bridge  \tsquare{xgreen} across the Bay of Baiae and then rode  \tcircle{xgreen}  \ttriangle{xgreen} across it on his deified horse, Incitatus. The centurion Cassius Chaerea assassinated this man in  \tdiamond{xgreen} 41 CE. For 10 points, name this Roman emperor who reigned between Tiberius and Claudius and who took the nickname “little boot."

\textbf{Answer}: Caligula\\
\end{frame}

\begin{frame}{Packet F3 Question 32}
This author praises ``A  \tsquare{xred} Cloud of Pinafores'' because it remains alive even after you set it on your bookshelf in ``The Modern Essay.'' The narrator  \ttriangle{xyellow} of an essay by this  \tdiamond{xyellow} writer lifts a pencil to help a certain  \tcircle{xred} insect but lays the pencil down again when that narrator realizes that the insect is dying. The most famous essay by this author includes an author surrogate who is prohibited from entering an Oxbridge library unless chaperoned by a fellow of the college. That essay later focuses on the prospects of Judith Shakespeare, overshadowed by her  \tcircle{xyellow} male brother. For 10 points, name this author of ``The Death of the Moth'' and ``A Room of One's Own.'' \tsquare{gray} 

\textbf{Answer}: Virginia\ Woolf\\
\tsquare{xred} On the Sublime
\tcircle{xred} Oscar Wilde
\tsquare{gray} On the Sublime
\end{frame}

\begin{frame}{Packet F3 Question 33}
A significant milestone in this artistic medium was Pierina Legnani's 1893 completion of thirty-two feats described by a term that translates as ``whipped.'' Those fouettés were later inserted into a work in this medium that was completed in 1877 to a poor reception in Moscow. The modern, abstract type of this medium is sometimes  \tcircle{xred} held to have originated with the piece Jewels. Darren Aronovsky directed a 2010 film that revolves around this medium starring Natalie Portman and Mila Kunis. George Balanchine co-founded the New York City company of, for 10 points, what performance art exemplified by ``Swan Lake''? \tdiamond{gray}  \tcircle{gray}  \tsquare{xgreen}  \ttriangle{gray} 

\textbf{Answer}: Ballet\\
\tcircle{xred} Photography
\tdiamond{gray} Tapestry
\tcircle{gray} Photography
\ttriangle{gray} Photography
\end{frame}

\begin{frame}{Packet F3 Question 34}
This thinker described a gap between virtual social identity and actual social identity, in a theory of  \ttriangle{xred} how some people become deeply discredited by society. This thinker identified orphanages, sanitariums, and prisons as exampeles of five types of institutions where members are expected to ``resocialize,'' termed total institutions. This man  \tcircle{xgreen} developed a theory of stigma and described ``back region'' conduct that is necessary for, but inconsistent with, ``front region'' performance. For 10 points, name this sociologist who  \ttriangle{xyellow} pioneered the dramaturgical approach in  \tdiamond{xgreen}  \tsquare{xgreen} The Presentation of Self in Everyday Life.

\textbf{Answer}: Erving\ Goffman\\
\ttriangle{xred} Stigma (wrestler)
\end{frame}

\begin{frame}{Packet F3 Question 35}
A museum in this country contains the Colonna Venus, which is the best preserved ancient replica of a Praxitiles statue. A sculpture located in this country consists of a stained glass dove above a bronze throne. A bonze canopy in this country is supported by marble plinths that depict an allegory of childbirth. A sculpture housed in this country that was unearthed in 1506 depicts Laocoon and his sons being eaten by serpents during the Trojan War. Gian Bernini's Baldachino is in,  \tcircle{xred} for 10 points, what very small country that contains Saint Peter's tomb? \tdiamond{gray}  \tcircle{gray}  \tsquare{gray}  \ttriangle{gray} 

\textbf{Answer}: Vatican\ City\\
\tcircle{xred} Laocoön and His Sons
\tdiamond{gray} Spain
\tcircle{gray} Laocoön and His Sons
\tsquare{gray} Italy
\ttriangle{gray} Peru
\end{frame}

\begin{frame}{Packet F3 Question 36}
This man wrote a three-part treatise on his failures titled Social Reconstruction, Psychological Reconstruction, and Material  \tcircle{xred} Reconstruction. Tōten Miyazaki gave this man the pseudonym Nakayama Shō in Japan.  \tcircle{xyellow} He signed a manifesto with Adolph Joffe stating that the Soviet model was not suitable for his  \tsquare{xgreen} country, and he formed the “First United Front” with the communists against the Beiyang government. Nationalism, democracy,  \ttriangle{xgreen} and the livelihood constitutute this man's Three Principles of the People.  \tdiamond{xgreen} For 10 points, name this mentor of Chiang Kai-shek and first leader of the Republic of China

\textbf{Answer}: Sun\ Yat-sen\\
\tcircle{xred} Rutherford B. Hayes
\end{frame}

\begin{frame}{Packet F3 Question 37}
Franco Modigliani argued that this construct was only applicable for values below a level he termed NAIRU. Additional research surrounding the two central parameters  \tcircle{xred} of this construct was called for in the Phelps Volume. Milton Friedman attacked this construct for  \ttriangle{xred} its lack of relevance in the long term,  \tsquare{xgreen} in which it becomes a vertical line at  \tdiamond{xyellow}  \tcircle{xyellow} one of its chief parameter's ``natural rate.'' Stagflation directly contradicts the relationship predicted by, for 10 points, what economic ``curve'' that shows an inverse relationship  \ttriangle{xyellow} between inflation and unemployment?

\textbf{Answer}: Phillips\ curve\\
\tcircle{xred} Unemployment
\ttriangle{xred} Geoid
\end{frame}

\begin{frame}{Packet F3 Question 38}
A controversial Donald  \tsquare{xred} Trump tweet about this  \tcircle{xred} disease stated, in all caps, that ``THE UNITED STATES HAS ENOUGH PROBLEMS!'' STRIVE is an trial for a vaccine of this disease, whose most significant epidemic occurred between the years of 2013 and 2016. The presence of Mai-Mai militias has hindered international efforts to stop an outbeak of this disease, which began in Beni in 2018 and threatens the province of North Kivu in  \tsquare{xyellow} the Democratic Republic of the Congo. For 10 points, name this African virus with incredibly high mortality rates. \tdiamond{gray}  \tcircle{gray}  \ttriangle{gray} 

\textbf{Answer}: Ebola\ virus\\
\tsquare{xred} The Shadow of a Gunman
\tcircle{xred} Kellyanne Conway
\tdiamond{gray} Yellow fever
\tcircle{gray} Kellyanne Conway
\ttriangle{gray} Tuberculosis
\end{frame}

\begin{frame}{Packet F3 Question 39}
The German name for these events comes from the title of a Stefan Zweig novel that combines the German  \tcircle{xred} word for runner with an Indonesian term- Amokläufer. A set of fingerprints implicated the filipino woman Marilou Danley in one of these events in 2017. In Florida, one of these events was carried out at the Pulse gay nightclub in 2016, and another occurred at Marjory Stoneman Douglan High School in Parkland in 2018. For 10 points, name these events, such as when Stephen Paddock opened fire on a crowd at a country concert. \tdiamond{gray}  \tcircle{gray}  \tsquare{gray}  \ttriangle{gray} 

\textbf{Answer}: Mass\ shooting\\
\tcircle{xred} LETTERS
\tdiamond{gray} Fires
\tcircle{gray} LETTERS
\tsquare{gray} Genocide
\ttriangle{gray} Witch-hunt
\end{frame}

\begin{frame}{Packet F3 Question 40}
This country's First Armoured Division held Hill 262 during the Battle of the Falaise Pocket. A force of troops from this country, Anders' Army, marched through Iran to Palestine in mid-1942. Infantry from this country's II Corps led the frontal assault during the Battle of Monte Cassino, eventually raising their country's flag over the ruined abbey. After a false flag operation in the Gleiwitz Incident, Nazi Germany ordered the invasion of this country in the  \tcircle{xyellow} September Campaign, triggering the onset of World War Two. For 10 points, name this country whose city of Danzig was seized by the Germans. \tdiamond{gray}  \tsquare{gray}  \ttriangle{gray} 

\textbf{Answer}: Poland\\
\tdiamond{gray} Italy
\tsquare{gray} Belgium
\ttriangle{gray} France
\end{frame}

\begin{frame}{Packet F3 Question 41}
This man's first wife was Elisaveta, the daughter of Yaroslav the Wise of Kiev. This king once served  \tdiamond{xyellow} as a mercenary in the Byzantine Varangian guards, in one apocryphal story kidnapping Pricess Maria. This one-time co-monarch alongside his nephew, Magnus the Good,  \tcircle{xgreen}  \ttriangle{xgreen} gained the throne of Denmark after fighting  \tsquare{xgreen} Sweyn Estridsson until 1064. This man seized York following his defeat of Morcar, the Earl of Northumbira, at the Battle of Fulford, just five days before his final defeat. For 10 points, name this Norweigan king who was defeated by Harold Godwinson at  \tdiamond{xred} the Battle of Stamford Bridge.

\textbf{Answer}: Harald\ Hardrada\\
\tdiamond{xred} William the Conqueror
\end{frame}

