\begin{frame}{Packet P1 Question 1}
A team based in this city won a game where a ruled incompletion by Quentin Morgan lead to fans throwing bottles on the field. A quarterback for a team in this city miraculously won a game when Mike Thomas caught his Hail Mary off a deflection; that 2009 pro bowler is David Garrard. A cornerback of a team from this city hilariously called Buffalo Bills quarterback Josh Allen “trash” in a GQ interview and plays alongside A.J. Bouye. For 10 points, name this city home to a team starring Jalen Ramsey and quarterbacked by Blake Bortles, that plays home games in Florida. \hdiamond{xred}  \hcircle{xred}  \hsquare{xred}  \htriangle{xred} 

\textbf{Answer}: Jacksonville,\ Florida\\
\hdiamond{xred} Atlanta
\hcircle{xred} Los Angeles
\hsquare{xred} New York Jets
\htriangle{xred} New York City
\end{frame}

\begin{frame}{Packet P1 Question 2}
Scott Tremaine proposed  \tcircle{xred} that an eccentric disk created this entity's nuclei in 1995 - that model was discussed in a paper by CY Peng that also described the 2 nuclei of this entity. Walter Baade used observation of this body to classify stars into 2 populations.  \hcircle{xgreen} The Hooker telescope found the first Cepheid variables here,  \hdiamond{xgreen}  \tsquare{xred} following up on hypotheses about this object discussed in the Curtis Shapley debate. The Triangulum Galaxy is thought to be bound to this other galaxy. Also known  \hsquare{xgreen} as M31, it is the  \ttriangle{xgreen} largest galaxy in the Milky Way. For  \tdiamond{xred} ten points, name this galaxy, predicted to collide with the Milky Way in a few billion years.

\textbf{Answer}: Andromeda\ Galaxy\\
\tcircle{xred} Kuiper belt
\tsquare{xred} Allan Sandage
\tdiamond{xred} Andromeda (constellation)
\end{frame}

\begin{frame}{Packet P1 Question 3}
Examples of these species with C2 symmetry can increase enantioselectivity,  \tcircle{xred} as in their Josiphos variety. Two of these species combine in migratory insertion, an important step in carbonylation reactions. These species are classified as either L, X, or Z based on how many electrons they donate. Carbon monoxide functions as this type of group in a metal carbonyl. ``Agents'' that can cure heavy metal poisoning in chelation therapy are polydentate examples of these  \tsquare{xred}  \ttriangle{xred} species, such as EDTA. For 10 points, name these species that bind to a central metal atom in coordination complexes. \hdiamond{xred} 

\textbf{Answer}: Ligand\\
\tcircle{xred} Homo erectus
\tsquare{xred} Chelation
\ttriangle{xred} Ion
\hdiamond{xred} Ligand
\end{frame}

\begin{frame}{Packet P1 Question 4}
It's not the pituitary gland, but this organ  \tdiamond{xred}  \tsquare{xred} is tested with the insulin tolerance test. The binding of CRF to the pituitary gland releases a hormone that stimulates this organ. Heightened activity of this organ leads to a high ARR, as overproduction of one hormone from this organ dangerously  \tcircle{xred} depresses renin levels. This last organ in the HPA axis produces too much aldosterone in Conn's Syndrome. This organ's zona fasciculata  \hsquare{xgreen} is overactive in Cushing’s disease,  \hcircle{xgreen} overproducing the anti-stress hormone cortisol. For 10 points, name these glands that also produce the catecholamine hormone epinephrine. \htriangle{xred} 

\textbf{Answer}: Adrenal\ gland\\
\tdiamond{xred} Pituitary gland
\tsquare{xred} Follicle-stimulating hormone
\tcircle{xred} Pituitary gland
\htriangle{xred} Liver
\end{frame}

\begin{frame}{Packet P1 Question 5}
A paper titled this algorithm ``through Time'' by Paul Werbos lays the theoretical groundwork for recurrent models that repeat parameters.  In pytorch, setting requires\_grad to False means that this is not applied to a parameter.  This can fail because of either ``vanishing'' or ``exploding'' gradients in particularly large neural networks, as it uses the chain rule to calculate the gradient of the loss at each layer, which  \hdiamond{xgreen}  \tsquare{xgreen} in turn is used to compute how much and in what direction layer weights should be  \ttriangle{xgreen} tuned. For 10 points, name this algorithm  \tcircle{xgreen} that is the basis for most forms of neural network training named for the direction that error moves through a model.

\textbf{Answer}: Backpropagation\\
\end{frame}

\begin{frame}{Packet P1 Question 6}
A paper by Lutchyn, Sau and Das Sarma details how observing one of these events in a nanowire would prove the existence of Majorana fermions. Widom scaling leads to the dependence of critical exponents  \hdiamond{xgreen} that characterize these events. The dissociation of vortex-antivortex pairs occurs during one of these events named for Kosterlitz and Thouless.  \tcircle{xgreen}  \tsquare{xgreen} YBCO undergoes one of these events at an abnormally high temperature. In contrast, elemental mercury undergoes one at about 234 Kelvin, far lower than most metals. When materials are brought past these events' points without undergoing these events, the material can enter metastates such as supercooled or superheated. For 10 points, name these events such as freezing, which are transitions between different states of matter. \htriangle{xred} 

\textbf{Answer}: Phase\ transition\\
\htriangle{xred} Witch-hunt
\end{frame}

\begin{frame}{Packet P1 Question 7}
A paper by Lutchyn, Sau and Das Sarma details how observing one of these events in a nanowire would prove the existence of Majorana fermions. Properties of these events are described in Halperin-Lubensky-Ma theory. Widom scaling leads to the dependence of critical exponents that characterize these events. The dissociation of vortex-antivortex pairs occurs during one of these events named for Kosterlitz and Thouless. YBCO  \tcircle{xgreen}  \tsquare{xgreen} undergoes one of these events at an abnormally high temperature. For 10 points, name these transitions between different states of matter, such as freezing. \hdiamond{xred}  \htriangle{xred} 

\textbf{Answer}: Phase\ transition\\
\hdiamond{xred} Phase transition
\htriangle{xred} Witch-hunt
\end{frame}

\begin{frame}{Packet P1 Question 8}
The Epsilon system released in JDK 11 performs this task. In Java, objects not affected by this process are stored in metaspace,  \tcircle{xgreen} while other objects are stored in the Eden space until this action occurs, after which they are divided generationally. The tricolor abstraction visualizes algorithms for this  \tsquare{xred} task. This task can be performed with the mark and sweep  \hsquare{xgreen} algorithm, which sometimes requires a stop-the-world pause. This task occurs when unreachable objects on the heap are found, and failure to perform it can cause memory leaks. For 10 points, name this task that frees unneeded  \tdiamond{xgreen}  \ttriangle{xred} memory.

\textbf{Answer}: Garbage\ collection\ (computer\ science)\\
\tsquare{xred} Sperm
\ttriangle{xred} String searching algorithm
\end{frame}

\begin{frame}{Packet P1 Question 9}
Tensor-vector-scalar' gravity is an extension to an alternative answer to the puzzles posed by this substance, known as MOND theory. String theory predicts a class of particles that do not interact via gauge boson forces, known as `hidden sector' particles, another candidate for this substance. This substance derives its name from its apparent lack of interaction with light, and its existence is inferred from its gravitational effects, leading scientists to hypothesize the existence of a new class of particles known as WIMPs. For 10 points,  \tsquare{xgreen} identify this substance  \htriangle{xgreen} believed to greatly outnumber its baryonic counterpart  \tcircle{xgreen} in the universe, an as-yet-unobserved form of matter. \hdiamond{xred} 

\textbf{Answer}: Dark\ matter\\
\hdiamond{xred} Neutron
\end{frame}

\begin{frame}{Packet P1 Question 10}
This virus is a member of the Flaviviridae family and is most  \tsquare{xred} closely related to the  \tcircle{xred} Spondweni virus. It was first isolated in a rhesus macaque in Uganda in 1947.  \hdiamond{xgreen}  \hsquare{xgreen} In both humans and monkeys it is transmitted primarily by Aedes aegypti, though it can also be spread through sex, blood transfusions, and mother-to-child transmission. The latter can lead to chorioretinal scarring and microcephaly. An outbreak of this disease in 2015-2016 raised concerns about athletes competing in the Olympics. For 10 points, identify this mosquito-borne virus  \ttriangle{xgreen} that caused a sharp drop in tourism to Brazil and the Caribbean.

\textbf{Answer}: Zika\ virus\\
\tsquare{xred} Poxviridae
\tcircle{xred} Hepatitis C virus
\end{frame}

\begin{frame}{Packet P1 Question 11}
Richard Feynman hypothesized that an element with atomic number 138 could not exist because it would require this particle to violate the laws of physics. Huckel's Rule relies on counting  \tcircle{xred} the number of these particles. Linus Pauling proposed a property measuring the tendency of an atom to attract these  \tsquare{xred} particles; that property  \hcircle{xgreen} is termed (*) ``electronegativity.'' The charge of these  \htriangle{xgreen} particles was first measured by suspending oil drops in an  \hdiamond{xgreen} electric field. For ten points, name these particles that Niels Bohr modeled as traveling in circular orbits around the  \hsquare{xgreen} nucleus of an atom.

\textbf{Answer}: Electron\\
\tcircle{xred} Magnetic monopole
\tsquare{xred} Electronegativity
\end{frame}

\begin{frame}{Packet P1 Question 12}
Edward Gibbon relies on  \tcircle{xred}  \tsquare{xred} Hydatius’s chronicle to identify the location of this battle, which is troubling as the chronicle technically begins the year after it occurred. The cavalry of this battle’s winning side returned from foraging to rebuff an assault on their wagon circle led by Bacurius. Gratian  \hcircle{xgreen}  \hsquare{xgreen} infuriated his legionnaires by dressing up in a Scythian outfit after this battle. Ammianus Marcellinus's history of Rome concludes with the empire's loss of this battle to an army commanded by Fritigern. For 10 points, name this battle at which Valens was killed by the Goths in  \tdiamond{xgreen} 378 AD. \htriangle{xred} 

\textbf{Answer}: Battle\ of\ Adrianople\\
\tcircle{xred} The History of the Decline and Fall of the Roman Empire
\tsquare{xred} The History of the Decline and Fall of the Roman Empire
\htriangle{xred} Battle of Marathon
\end{frame}

\begin{frame}{Packet P1 Question 13}
One of this author's characters claims “America … stretches so far everywhere you look. And there's lots of insects there.`` One of this author's characters recalls punching a woman who asks for help with a mangle during a sexually tense encounter over a glass of water. Later, characters in that play by this man ask if Joey went the ''whole hog" with Ruth, who becomes a prostitute despite being Teddy's  \tcircle{xgreen} wife. In another play by this author,  \tsquare{xred} a character repeatedly pulls a toilet chain, though no toilet flushes. For 10 points, name this author of The Homecoming who created the hit-men  \tdiamond{xgreen} Ben and Gus in  \hsquare{xgreen}  \ttriangle{xgreen} The Dumbwaiter.

\textbf{Answer}: Harold\ Pinter\\
\tsquare{xred} The Homecoming
\end{frame}

\begin{frame}{Packet P1 Question 14}
This character is likely named after a type of fur used in nobles' robes and a French term for a horse. This man ``eyed a khaki suit with loathing'' in a stanza that expresses his preference for ``iron clothing.''  \hdiamond{xgreen} This man, who dreamed of ``Thebes and Camelot,'' loved  \tcircle{xred} the Medici despite  \ttriangle{xred} never having seen one of them. This man ``coughed, and called  \htriangle{xgreen} it fate, / And kept  \hcircle{xgreen} on drinking'' at the end of a poem that calls him a ``child of scorn'' who was ``born too late.'' For 10 points, name this character who ``loved the days of old'' in an Edwin Arlington Robinson poem. \hsquare{xred} 

\textbf{Answer}: Miniver\ Cheevy\\
\tcircle{xred} Edwin Arlington Robinson
\ttriangle{xred} Edwin Arlington Robinson
\hsquare{xred} Weird Al Yankovic
\end{frame}

\begin{frame}{Packet P1 Question 15}
One of this author’s character becomes white-haired after sitting in a Ferris Wheel and watching a copy of herself have sex. In that novel, the protagonist’s friend has a lesbian crush on her employer and disappears suddenly off an island near Greece. In another novel by this author, a character who receives a letter about “duck people” sits at the bottom of a well after being trapped there by his neighbor May Kasahara; that character hires Creta Kano to help  \hdiamond{xgreen}  \tsquare{xred} find his cat. For 10 points, name this author of Sputnik Sweetheart who created  \tdiamond{xred} Toru Okada in The  \tcircle{xgreen}  \htriangle{xgreen} Wind-Up Bird Chronicle.

\textbf{Answer}: Haruki\ Murakami\\
\tsquare{xred} The Wind-Up Bird Chronicle
\tdiamond{xred} Ryū Murakami
\end{frame}

\begin{frame}{Packet P1 Question 16}
In a story set during this war, a draper and  \tsquare{xred} a watchmaker are executed by enemy soldiers for refusing to reveal the password of their country's  \tcircle{xgreen} defense lines. A woman uses a hay-loft to burn down a house with enemy soldiers in it after her son dies during this war. This war, the backdrop of ``Two Friends'' and “Mother Savage,” sets a work in which a woman who shares a basket of food with her wagonmates is made to sleep with an enemy officer for passage to Le Havre. For 10 points, name this setting of Guy de Maupassant's ``Ball of Fat,'' a war  \tdiamond{xgreen} France lost against its eastern neighbor in 1870. \htriangle{xred} 

\textbf{Answer}: Franco-Prussian\ War\\
\tsquare{xred} Mad Men
\htriangle{xred} World War II
\end{frame}

\begin{frame}{Packet P1 Question 17}
This artist depicted a woman with red and grey arms stretching paw-like limbs across a table in Stenographic Figure, which was shown in Peggy Guggenheim's gallery Art of This Century. This artist supposedly  \tcircle{xred} painted his twenty foot long by eight foot high Mural in one day, and he used a turkey baster to apply black paint to a canvas in a painting characteristically called Number 7, 1951. This husband of Lee Krasner often  \tsquare{xgreen} painted by laying  \hcircle{xgreen} out canvases on his studio floor. Lavender Mist is by, for 10  \tdiamond{xgreen}  \ttriangle{xgreen} points, what abstract expressionist painter nicknamed ``Jack the Dripper''?

\textbf{Answer}: Jackson\ Pollock\\
\tcircle{xred} Max Ernst
\end{frame}

\begin{frame}{Packet P1 Question 18}
One member of this school of thought developed a three stage criterion for it, which he illustrated by  \tcircle{xred} using the example of a rope in a dark room. Legendarily, the founder of one branch of this non-Confucian school left his friend to die while he was trapped in a hole. Circularity and regress are among this school’s “five modes” named for Agrippa, and it included Carneades. Pyrrhonism, a movement within this school of thought, included an author who wrote Against the Mathematicians, Sextus Empiricus.  \hcircle{xgreen} For 10 points name  \tsquare{xgreen} this school that  \tdiamond{xgreen} questions the certainty of much of knowledge. \htriangle{xred} 

\textbf{Answer}: Skepticism\\
\tcircle{xred} Behaviorism
\htriangle{xred} Behaviorism
\end{frame}

\begin{frame}{Packet P1 Question 19}
A book by this man discusses the absurdity of animal sacrifice while describing the Intichiuma ceremony. This man argued that the difference between Protestants and Catholics was the amount of ``free inquiry'' demanded of their members. A book by this sociologist differentiates between totemistic objects  \tcircle{xgreen} that have special significance and mundane objects which do not, or the sacred and the profane. He  \tsquare{xgreen} discussed egoistic, altruistic, fatalistic,  \tdiamond{xgreen}  \htriangle{xgreen} and anomic forms  \ttriangle{xred} of the title phenomenon in one text. For 10 points, name this sociologist who wrote The Elementary Forms of Religious Life and Suicide.

\textbf{Answer}: Émile\ Durkheim\\
\ttriangle{xred} Suicide (book)
\end{frame}

\begin{frame}{Packet P1 Question 20}
After being trapped in  \tsquare{xred} a cave with a demon, one of these animals assumes his brother betrayed him to take  \hsquare{xgreen} control of Kishkindha. One of these  \tcircle{xgreen} animals carries an entire mountain and stops the sun from rising to find a medicinal herb. After escaping  \hdiamond{xgreen} from a trigram meant to turn him into an elixir, one of these animals becomes trapped by pillars revealed to be the Buddha's fingers. Indra breaks the chin of a devotee of Rama who takes this form, which is also taken by a ``king'' who appears in Journey to the West. For 10 points, name these animals including Sun Wukong and Hanuman. \htriangle{xred} 

\textbf{Answer}: Monkey\\
\tsquare{xred} Shangri-La
\htriangle{xred} Horse
\end{frame}

\begin{frame}{Packet P1 Question 21}
This culture produced an image of a walking man with sandals in its Monument 13, or the ``Ambassador Relief.'' A sculpture from this culture shows a man with a twisting torso and a possibly fake mustache called “The Wrestler”. Much of this culture’s artwork was preserved in the bogs of El Manati. This culture used jade in the Kunz Axe, which  \tsquare{xgreen} features its common  \tcircle{xgreen} were-jaguar motif. This civilization produced many of its works in cities such as San Lorenzo and La Venta. For 10 points, name this Mesoamerican culture that produced  \tdiamond{xgreen} many sculptures of gigantic heads. \htriangle{xred} 

\textbf{Answer}: Olmec\\
\htriangle{xred} Mississippian culture
\end{frame}

\begin{frame}{Packet P1 Question 22}
A fiat order given to  \tcircle{xred}  \tsquare{xred} a person with this profession was deemed illegal in the DC circuit case of Sherrill v. Knight. A recording of one man with this profession at a community barbeque featured his glasses being broken. Donald Trump yelled ``I don't know what I said'' while shaking his arms to mock Serge Kovaleski, who has this job. After the November 2018 elections, Trump said ``that's enough'' to a member of this profession at the White House as an intern tried to seize his microphone. For 10 points, name this job held by Jim Acosta, who works for what Donald Trump terms the ``Fake News Media.'' \hdiamond{xred}  \htriangle{xred} 

\textbf{Answer}: Journalist\\
\tcircle{xred} Money
\tsquare{xred} Money
\hdiamond{xred} Lists of actors
\htriangle{xred} ELIZA
\end{frame}

\begin{frame}{Packet P1 Question 23}
Thomas Carlyle influenced  \tsquare{xred} this thinker to develop a theory on the impact of ``Great Men, Great Thoughts, and the Environment''  \tcircle{xred} on history. This American posited that emotions arise from  \hcircle{xgreen} the mind's appraisal of physical changes in response to environmental stimuli in a theory that he  \hdiamond{xgreen} co-names with Carl Lange. He posited the theory of ``radical empiricism'' in The Meaning  \hsquare{xgreen} of Truth and titled a book for a philosophical school that he developed with C.S. Pierce and John Dewey. For 10 points, name this ``father of American psychology'' and co-founder  \ttriangle{xgreen} of pragmatism.

\textbf{Answer}: William\ James\\
\tsquare{xred} Sartor Resartus
\tcircle{xred} John Stuart Mill
\end{frame}

\begin{frame}{Packet P1 Question 24}
This thinker argued that  \tsquare{xred} capital punishment  \tdiamond{xred} was only acceptable in very pious socieities- as they believed in atonement in the afterlife- in his essay ``Reflections  \hdiamond{xgreen} on the Guillotine.'' An essay by this thinker argues that Ivan  \tcircle{xred} Karamazov's statement that ``Everything is permitted'' is not a happy observation but rather a bitter  \hcircle{xgreen} truth. That essay by this man begins by saying that ``There is but one truly serious philosophical problem, and that is suicide,'' and it concludes that ``One must imagine'' the title  \ttriangle{xred} figure ``happy.'' For ten points, name this existentialist author of ``The Myth of Sisyphus.''

\textbf{Answer}: Albert\ Camus\\
\tsquare{xred} Rosa Luxemburg
\tdiamond{xred} Michel Foucault
\tcircle{xred} Sigmund Freud
\ttriangle{xred} The Myth of Sisyphus
\end{frame}

\begin{frame}{Packet P1 Question 25}
Richard Lourie echoed a Flaubert insult by saying of a version of this work, ``It is flat, your translation.'' Two years after discussing it in Le Ton beau de Marot, Douglas Hofstadter  \tsquare{xred} published a translation of this work. Walter Arndt's translation of this work won the 1962 Bollingen Prize. Vladimir Nabokov published a notoriously literal translation of this work, despite calling it ``mathematically impossible'' to maintain its masculine and feminine rhymes across  \hdiamond{xgreen}  \tcircle{xgreen}  \hsquare{xgreen} fourteen-line stanzas. Vikram Seth's The Golden Gate pays homage to, for 10 points, what verse novel  \ttriangle{xgreen} by Alexander Pushkin?

\textbf{Answer}: Eugene\ Onegin\\
\tsquare{xred} Douglas Hofstadter
\end{frame}

\begin{frame}{Packet P1 Question 26}
In a story set in this country, an academic crawls to a tavern to order wine after his legs are broken as punishment for stealing food. After losing a fight at a gambling table, the title character of a story set in this country slaps himself in the face twice, claiming a ``spiritual victory'' because it was he who gave the slap. A collection from this country, A Call to Arms, contains ``The True Story of Ah Q.'' An autobiographical  \tdiamond{xgreen}  \htriangle{xgreen} novel from this country tells  \tcircle{xgreen} of ``I,'' who is misdiagnosed with terminal lung cancer, in Soul Mountain. For 10  \tsquare{xgreen} points, name this birthplace of Lu Xun and Gao Xingjian.

\textbf{Answer}: China\\
\end{frame}

\begin{frame}{Packet P1 Question 27}
This writer developed the ``status'' and ``contract'' models of writing in an essay that labels William Gaddis as ``Mr. Difficult.'' In a novel by this man, a character flees a kitchen when he sees a plate of liver and onions, and later his father hallucinates about talking feces. He discussed the research  \tsquare{xred} of Shirley Bryce Heath on reading demographics in a work alternately titled ``Why Bother?'' or ``The Harpers  \hsquare{xgreen} Essay,'' and he wrote a novel in which Alfred Lambert suffers  \tdiamond{xgreen}  \tcircle{xgreen} from Parkinson's. For 10 points, named this contemporary  \ttriangle{xgreen} author of The Corrections.

\textbf{Answer}: Jonathan\ Franzen\\
\tsquare{xred} The Recognitions
\end{frame}

\begin{frame}{Packet P1 Question 28}
An essay by this author praises Coriolanus  \tsquare{xred} and Antony and Cleopatra as Shakespeare's greatest successes. He compared a different Shakespeare play to the ``Mona Lisa'' and argued that it is ``an artistic failure'' in that essay, ``Hamlet and His Problems.'' A poem by this author begins with a quote from Dante about Guido da Montefeltro; that poem's title character declares that he is ``not Prince Hamlet, nor was meant to be,'' after comparing the evening sky to a ``patient  \tcircle{xred} etherized upon a table.'' For 10 points,  \hsquare{xgreen}  \htriangle{xgreen} name this author of ``The Love Song  \tdiamond{xgreen} of J. Alfred Prufrock.''

\textbf{Answer}: T.\ S.\ Eliot\\
\tsquare{xred} On the Sublime
\tcircle{xred} The Love Song of J. Alfred Prufrock
\end{frame}

\begin{frame}{Packet P1 Question 29}
This meeting established the short-lived Duchy of Lucca. An agreement  \hdiamond{xgreen}  \tsquare{xgreen} that established Krakow as a free city resolved the  \tcircle{xgreen}  \htriangle{xgreen} Polish-Saxon crisis during this meeting, after France brokered a secret alliance against Russia. As a result of this meeting, the remains of the Holy Roman Empire were combined into a 39-state German Confederation. Its main negotiations were completed during the Hundred Days period. For 10 points, name this meeting that determined the balance of power in Europe after the Napoleonic Wars.

\textbf{Answer}: Congress\ of\ Vienna\\
\end{frame}

\begin{frame}{Packet P1 Question 30}
Torkild Rieber, the CEO  \tcircle{xred} of Texaco, illegally supplied 3.5 million tons of oil to one side of this war. The Thalmann Batallion were a group of European volunteers who fought on one side of this conflict, often in practical and ideological opposition to the Condor Legion. Emilio Mola  \tdiamond{xgreen} coined the term ``fifth  \tsquare{xgreen} column'' to refer  \hcircle{xgreen} to resistance fighters in this war. A German bombing campaign destroyed the town of Guernica during,  \ttriangle{xgreen} for 10 points, what Iberian conflict that led to the establishment of Francisco Franco’s dictatorship?

\textbf{Answer}: Spanish\ Civil\ War\\
\tcircle{xred} Adam Hochschild
\end{frame}

\begin{frame}{Packet P1 Question 31}
Coleman v. Miller established  \hdiamond{xgreen}  \tsquare{xgreen}  \ttriangle{xgreen} Congress's power to set time restrictions on these entities. The president's power to create these entities was limited in the case of Hollingsworth v. Virginia. States' equal representation in the Senate is explicitly protected from these entities. In Federalist No. 84, Alexander Hamilton argued against a set of these, though twelve were introduced by James Madison during the first Congress. The twenty-first of these entities ended the federal policy of prohibition. For 10 points, name these entities, the first ten of which are called the Bill of Rights. \hcircle{xred} 

\textbf{Answer}: Constitutional\ amendment\\
\hcircle{xred} Supreme Court of the United States
\end{frame}

\begin{frame}{Packet P1 Question 32}
A Willy Decker production  \tsquare{xred} of this opera features a giant clock on stage. The tenor lead sings the phrase ``Di quell'amor'' from offstage during the soprano lead's Act I cabaletta, in which  \tcircle{xgreen}  \hsquare{xgreen} she affirms her commitment to pleasure and freedom. The lead soprano of this opera sings ``Sempre libera.'' At the end of this opera's second act, its tenor lead humiliates a woman by throwing his gambling winnings at her. It contains the drinking song ``Libiamo  \tdiamond{xgreen} ne' lieti calici.''  \ttriangle{xgreen} The title character dies of tuberculosis in, for 10 points, what opera about Alfredo and Violetta by Giuseppe Verdi?

\textbf{Answer}: La\ traviata\\
\tsquare{xred} Bus Stop (William Inge play)
\end{frame}

\begin{frame}{Packet P1 Question 33}
Frédéric Chopin based his first work for piano and orchestra on music by this composer. In the slow introduction to one of this composer's works, the instruments enter on C, E-flat, A-flat, and A natural. A Franz Lizst transcription of a choral work by this composer  \tcircle{xred} is the basis of the ``Preghiera'' movement in a Pyotr Tchaikovsky orchestral suite titled after this composer. This composer wrote the ``Dissonance'' string quartet, a five-part fugato to conclude his final symphony, and  \hdiamond{xgreen} a piano sonata containing  \tdiamond{xred} the ``Rondo alla  \tsquare{xred} turca.'' For 10 points,  \hsquare{xgreen} name this composer of the ``Jupiter'' Symphony. \htriangle{xred} 

\textbf{Answer}: Wolfgang\ Amadeus\ Mozart\\
\tcircle{xred} Ludwig van Beethoven
\tdiamond{xred} Ludwig van Beethoven
\tsquare{xred} Ludwig van Beethoven
\htriangle{xred} Ludwig van Beethoven
\end{frame}

\begin{frame}{Packet P1 Question 34}
A 2007 book about this painting by Susan Vreeland imaginatively tells of how its artist created it to represent ``la vie moderne'' in response to a challenge from Emile Zola. A railing divides this work along  \tcircle{xgreen} a diagonal into a crowded scene of people and a swirl of reeds and grass. Gustave Caillebotte wears  \tsquare{xgreen} a sleeveless white shirt on the right side of this painting that depicts its artists's future wife Aline Charigot playing  \ttriangle{xgreen} with a small dog. The Restaurant Fournaise is the setting of, for 10 points, what painting by Pierre-Auguste Renoir titled for a midday  \tdiamond{xgreen} waterfront meal?

\textbf{Answer}: Luncheon\ of\ the\ Boating\ Party\\
\end{frame}

\begin{frame}{Packet P1 Question 35}
During a cold open on this show, one character tells another that  \tsquare{xred} he came down with a ``Dianne Wiest infection.'' In an episode of this show, a recurring character leaves the main character some diamonds in a Le Creuset pot at a Korean karaoke establishment. Craig Robinson and Jason Mantzoukas have recurring roles as Doug Judy and Adrian Pimento on this show, whose Halloween episodes involve a thieving contest involving people such as Amy Santiago and Captain Holt. For 10 points,  \hsquare{xgreen} name this sitcom set in an NYPD precinct that stars Andy Samberg  \tdiamond{xgreen}  \ttriangle{xgreen} as Jake Peralta. \hcircle{xred} 

\textbf{Answer}: Brooklyn\ Nine-Nine\\
\tsquare{xred} The Big Bang Theory
\hcircle{xred} Brooklyn Nine-Nine
\end{frame}

\begin{frame}{Packet P1 Question 36}
The province of Bushehr, which borders this body of water, was once part of the Fars province. Bubiyan Island and Warbah Island harbor military installations at the northern end of this body of water. The Safaniya Field is a major center of economic activity in this body of water. The U.S. Fifth Fleet is headquartered in this body of water, in part to protect the safe passage of oil through the Strait of Hormuz. The Shatt  \tsquare{xgreen} al-Arab delta of  \tcircle{xgreen} the Tigris and the  \tdiamond{xgreen} Euphrates empties into, for 10 points, what body of water that gave its name to a 1991 war between Iraq  \ttriangle{xgreen} and the U.S.?

\textbf{Answer}: Persian\ Gulf\\
\end{frame}

\begin{frame}{Packet P1 Question 37}
On the tv show Parks and  \tsquare{xred} Recreation, Leslie Knope performs this action while wearing roller skates after discovering that citizens of Eagleton could be deprived of  \tcircle{xred} their right to vote. On Scandal, Mellie Grant takes a break from performing this action when the Vice President interrupts with a question about gonorrhea; that action leads to the successful funding of Planned Parenthood. On The West Wing, Howard Stackhouse performs this action for eight hours because he has a grandson who is autistic. For 10 points, identify this action performed by Jefferson Smith for twenty-four hours in Mr. Smith Goes to Washington. \hdiamond{xred}  \htriangle{xred} 

\textbf{Answer}: Filibuster\\
\tsquare{xred} Bob's Burgers
\tcircle{xred} Kristen Bell
\hdiamond{xred} Drowning
\htriangle{xred} Suicide
\end{frame}

\begin{frame}{Packet P1 Question 38}
By transformingto an abstract `shape-sphere', researchers in 2013 discovered the first new families of solutions to this problem since the Brouke-Henon family.  Expanding the coordinates as a function of the cube root of t was the technique used by Sundman to create  \hsquare{xgreen} a series expansion for this problem.  Another family of  \tcircle{xgreen} solutions is named after Euler and a mathematician who lends his name to their solutions, known as `Lagrange points'. A  \tdiamond{xgreen} third family is named for their characteristic motion pattern, the figure-eight. For 10 points, name this celestial mechanics problem, which requires calculating the motions of three masses influenced by each other's gravity from a given position and velocity. \htriangle{xred} 

\textbf{Answer}: Three-body\ problem\\
\htriangle{xred} Multi-armed bandit
\end{frame}

\begin{frame}{Packet P1 Question 39}
A leader of this country denounced the invasion of a nearby nation in his ``August 21st'' speech. Jews in this country were massacred at a kosher slaughterhouse by members of the Legionnaires’ Rebellion. In this country, political prisoners at Pitesti were reeducated by the Iron Guard. Many children became  \tdiamond{xgreen} orphans with this country's Decree 770, issued by a leader who wanted to restrict abortion and create  \tcircle{xgreen} “hero mothers.” A leader of this country and his wife Elena were killed by  \tsquare{xgreen}  \htriangle{xgreen} a firing squad in Timisoara. For 10 points, name this country once led by Nicolae Ceaușescu.

\textbf{Answer}: Romania\\
\end{frame}

\begin{frame}{Packet P1 Question 40}
This country, which banned the book The Past Is Not Like Smoke,  \hcircle{xgreen} is the subject of  \htriangle{xgreen} several books by the historian Frank Dikotter. This country  \hdiamond{xgreen} replaced sparrows with cockroaches in a list of pests to eliminate after killing  \tcircle{xred} sparrows led to a famine known as the Three Bitter Years. Critics of its government were punished after its leader asked for criticism in the Hundred Flowers campaign. This country disastrously required farmers to make steel mills in their backyards. For 10 points, name this country that experienced the “Great Leap Forward” and “Cultural Revolution” under Mao Zedong. \hsquare{xred} 

\textbf{Answer}: China\\
\tcircle{xred} Netherlands
\hsquare{xred} China
\end{frame}

\begin{frame}{Packet P1 Question 41}
Sword Lake, which is in  \tsquare{xred} this country's capital, contains the Turtle Tower in its center. In this country, two huge, stone hands hold up a golden bridge in the Ba Na Hills region. Alexandre De Rhodes founded a script primarily used by languages  \tdiamond{xgreen} in this country. This  \hsquare{xgreen} country's ``Central Highlands'' lie in the Annamite Range. The delta of the Red  \tcircle{xgreen} River lies in this country, as does that of a river that shoots namesake ``fireballs,'' the Mekong. Like China, this country borders the Gulf of Tonkin. For 10 points, name this country that contains Saigon and its capital, Hanoi. \htriangle{xred} 

\textbf{Answer}: Vietnam\\
\tsquare{xred} Excalibur
\htriangle{xred} Canada
\end{frame}

