\begin{frame}{Packet P2 Question 1}
This law created tribunals called “half-chambers”  \tsquare{xred} or “parted houses,” which had exactly equal representation from two religious groups. Proponents of this law argued that it was violated by the royal establishment of a parliament in Bearn. This law included fifty six secret articles  \hsquare{xgreen} that gave funding to safe havens such as the fortress at La Rochelle. This law  \hdiamond{xgreen} expanded upon a proclamation made by Catherine  \hcircle{xgreen} de Medici named after the month of January. For 10 points, name this 1562 law by which Henry IV granted tolerance to French Protestants. \htriangle{xred} 

\textbf{Answer}: Edict\ of\ Nantes\\
\tsquare{xred} Ex parte
\htriangle{xred} Second law of thermodynamics
\end{frame}

\begin{frame}{Packet P2 Question 2}
The minima of a flow named  \tsquare{xred} for one form of this quantity solve the isoperimetric problem. The local form of one theorem relates the sum of exterior angles of a simple  \hcircle{xgreen} surface to the sum of integrals of two forms of this quantity, and the global form relates those integrals to the Euler characteristic. As the Hessian's eigenvalues give a form of this quantity, the Hessian's determinant at extrema determines a function's concavity. Under an arc length parametrization, this quantity  \hsquare{xgreen} is the magnitude of the derivative of the tangent vector.  \hdiamond{xgreen} For 10 points, name this measure of a surface's bending. \htriangle{xred} 

\textbf{Answer}: Curvature\\
\tsquare{xred} Theodor W. Adorno
\htriangle{xred} Curvature
\end{frame}

\begin{frame}{Packet P2 Question 3}
At thirty, this thinker had an epiphany about the natural world while visiting the classified cabinets of Paris’s Jardin des Plantes. The importance  \tsquare{xred} of this thinker’s aunt Mary Moody to his ideas is traced in a Robert Richardson’s biography subtitled “the mind on fire.” He described Emanuel Swedenborg as “the Mystic” in his book Representative Men. An oft-quoted passage from an essay by this man states “I am part or particle of God`` and ''I become a transparent eyeball." For 10  \hdiamond{xgreen} points, name this American philosopher who  \hsquare{xgreen} wrote the essays “Nature” and “Self-Reliance.” \hcircle{xred}  \htriangle{xred} 

\textbf{Answer}: Ralph\ Waldo\ Emerson\\
\tsquare{xred} Julio Cortázar
\hcircle{xred} Ralph Waldo Emerson
\htriangle{xred} Ralph Waldo Emerson
\end{frame}

\begin{frame}{Packet P2 Question 4}
People in this place built temporary homes known as tilts and annually fled inland in a practice called winterhousing. John Guy’s Cuper's Cove company was established in this home of the Beothuk people. It’s not in Maryland, but George Calvert established the colony of Avalon in this place. The colony of L'Anse aux Meadows was discovered in this place, and represents the earliest evidence of a European presence in the Americas. Joseph Smallwood led the Confederation  \tcircle{xred} campaign on, for 10 points, what Canadian island near  \tsquare{xred} Labrador that takes  \tdiamond{xred} its name from Leif Eriksson's 11th century  \ttriangle{xred} visit?

\textbf{Answer}: Newfoundland\ (island)\\
\tcircle{xred} Newfoundland and Labrador
\tsquare{xred} Newfoundland and Labrador
\tdiamond{xred} Newfoundland and Labrador
\ttriangle{xred} Newfoundland and Labrador
\end{frame}

\begin{frame}{Packet P2 Question 5}
This quantity names a kind of crystal experimentally verified in 2016 in a chain of ytterbium atoms driven by laser pulses. In quantum mechanics,  \tcircle{xred} this quantity is negated by an antiunitary operator that produces degenerate states according to Kramers theorem. Invariance under changes in this quantity  \tsquare{xred} implies energy conservation as per Noether’s Theorem. The RC constant for a circuit has units of this quantity, as does the inverse of the radioactive decay constant. This quantity is the non-spatial dimension in Minkowski space. For 10 points, name this quantity measured in SI units of seconds. \hdiamond{xred}  \htriangle{xred} 

\textbf{Answer}: Time\\
\tcircle{xred} Bose–Einstein condensate
\tsquare{xred} Symmetry
\hdiamond{xred} Time
\htriangle{xred} Temperature
\end{frame}

\begin{frame}{Packet P2 Question 6}
With James Watson, this physicist founded  \tsquare{xred} a discussion group for scientists concerning the genetic code called the RNA Tie Club. In a novel by this man, he describes people on bicycles undergoing Lorentz contractions to illustrate special relativity. This man proposed an early nuclear model where it is treated as an incompressible fluid, the liquid drop model. This man used quantum tunneling to show  \hsquare{xgreen} how nuclear fusion occurs despite Coulomb repulsion. Known  \hcircle{xgreen} for his work on Big Bang nucleosynthesis, for 10 points, name  \ttriangle{xgreen} this physicist who humorously authored a paper along with  \tdiamond{xgreen} Alpher and Bethe.

\textbf{Answer}: George\ Gamow\\
\tsquare{xred} Francis Crick
\end{frame}

\begin{frame}{Packet P2 Question 7}
One type of this structure proposed by Bentley quickly finds the nearest neighbor of an input, and its elements represent splitting planes. A proof of the n log(n)  \hdiamond{xgreen}  \tcircle{xred} lower bound for comparison based sorting builds one of these structures, and notes it must have at least n factorial of a certain type of element. The inverse Ackermann function appears when analyzing an algorithm that uses a union-find data structure to find one of these structures. A greedy algorithm by Kruskal finds the minimum spanning type of this structure. For 10 points, name these acyclic  \ttriangle{xred} graphs with root and leaf nodes. \hsquare{xred} 

\textbf{Answer}: Tree\ (data\ structure)\\
\tcircle{xred} Quicksort
\ttriangle{xred} Tree
\hsquare{xred} Tree (data structure)
\end{frame}

\begin{frame}{Packet P2 Question 8}
Increased response to this chemical is initiated when galantamine  \tcircle{xred} binds to its 5-HT3 receptor, and its overproduction can result in a condition described with the mnemonic ``SLUDGE syndrome.'' Receptors for this chemical are  \hcircle{xgreen} classified in whether they employ a second messenger system or gated ion channels and are respectively muscarinic and nicotinic.  \tsquare{xgreen} Receptors  \tdiamond{xgreen} of this neurotransmitter  \ttriangle{xgreen} are attacked in myasthenia gravis. Latrotoxin causes its supply to be rapidly released whereas curare poison inhibits the uptake of this small molecule. For 10 points, name this neurotransmitter that activates muscle contractions, an ester of acetic acid and choline.

\textbf{Answer}: Acetylcholine\\
\tcircle{xred} Zoltán Kodály
\end{frame}

\begin{frame}{Packet P2 Question 9}
Development of these structures results from asymmetric cell division after SPCH production is inhibited by YODA. In response to elevated carbon  \tcircle{xgreen} dioxide levels, an increase in the number of these structures  \hdiamond{xgreen} has been observed  \hsquare{xgreen} to be regulated by the HIC gene. The pericytic type found in ferns are surrounded by a single donut-like cell, while monocots possess two  \tsquare{xred} peripheral lens-like cells in the gramineous type. Uptake of potassium ions increases turgor pressure  \ttriangle{xgreen} within these structures causing them to swell and open. Flanked by two guard cells, for 10 points, name these pores found on the surfaces of plant leaves.

\textbf{Answer}: Stoma\\
\tsquare{xred} Meristem
\end{frame}

\begin{frame}{Packet P2 Question 10}
This technique can identify weak points in polypropylene or aramid fibers as applied stress affects the  \tsquare{xred} fibers’ response to this technique. In a variant of this technique, a depolarization ratio greater than three-fourths shows that the sample has asymmetric vibrations. This technique penetrates deep beneath surfaces in its spatially offset variant. The results of this technique are characterized by the change in scattered photon energy and  \hsquare{xgreen} are known as Stokes and anti-Stokes shifts.  \tdiamond{xgreen}  \htriangle{xgreen} For 10 points,  \tcircle{xgreen} name this technique used to probe low frequency molecular modes, named for an Indian physicist.

\textbf{Answer}: Raman\ spectroscopy\\
\tsquare{xred} Plastic
\end{frame}

\begin{frame}{Packet P2 Question 11}
In 2017 this body was shown to be surrounded by cold blobs of  \tsquare{xred} protons by the JADE instrument. The convergence of currents around this body forms a radially outward current known as the CEC. A prominent feature of this body is produced by the  \tcircle{xred} dissociation of sulfur dioxide ejected by an interior moon and is known as the plasma torus. This planet’s magnetosphere is generated by a rotating layer of metallic hydrogen and interacts locally with magnetic moments of Io and Ganymede. For 10 points, identify this planet that has the largest magnetic structure in the solar system, the  \tdiamond{xred}  \htriangle{xgreen} fifth from the Sun.

\textbf{Answer}: Jupiter\\
\tsquare{xred} Pillow lava
\tcircle{xred} Titan (moon)
\tdiamond{xred} Mercury (planet)
\end{frame}

\begin{frame}{Packet P2 Question 12}
A common mistake when calculating the index error of these devices occurs when converting between the Kew and Fortin types. Printed sheets explaining how to interpret readings from these devices were included on the reverse of the ones named for HMS Beagle captain Admiral FitzRoy. Airplanes usually make use of the smaller aneroid type of these devices. One often factors in the temperature and gravity when using a mercury-based device of this type. Some of these devices offer readings in millibars. For 10 points, name this type of device which measures the pressure of the atmosphere. \hdiamond{xred}  \hcircle{xred}  \hsquare{xred}  \htriangle{xred} 

\textbf{Answer}: Barometer\\
\hdiamond{xred} Flip-flops
\hcircle{xred} Fuel cell
\hsquare{xred} Compass
\htriangle{xred} Laser
\end{frame}

\begin{frame}{Packet P2 Question 13}
Claude le Jay and Jean Codure met the founder of this organization in Paris. Joanna of Austria may have been secretly admitted to this organization. While living in a Manresa cave, its founder wrote a text that instructs the reader to imagine ``wailing'' and ``screaming.'' A book by Ludolph of Saxony influenced  \tsquare{xred} its founder, who was wounded near Pamplona. This group  \tcircle{xgreen} ran the San Ignacio Guazu reduction but was expelled from Spain in 1767. The Spiritual Exercises are a central text of, for 10 points, what Catholic religious order founded by Ignatius  \ttriangle{xgreen} of Loyola known  \tdiamond{xgreen}  \hsquare{xgreen} for its support of education?

\textbf{Answer}: Society\ of\ Jesus\\
\tsquare{xred} Ignatius of Loyola
\end{frame}

\begin{frame}{Packet P2 Question 14}
This artist chewed out her eventual biographer David Yaffe for calling her music “middle class” in the Times. While in Crete, this artist of “Don Juan’s Reckless Daughter” met Cary Raditz, who was immortalized in her lyrics as a ``redneck on a Grecian isle.'' The opening of one of her biggest hits riffs on ``Jingle Bells'' and contains the line, ``I made my baby cry.” She appeared on the Dick Cavett Show instead of performing at Woodstock, but then wrote the track ''Woodstock`` made famous by CSNY. A 2017 NPR list was topped by her album, Blue. For 10 points, name this folk singer behind ''River". \hdiamond{xred}  \hcircle{xred}  \hsquare{xred}  \htriangle{xred} 

\textbf{Answer}: Joni\ Mitchell\\
\hdiamond{xred} Ritchie (album)
\hcircle{xred} Amy Winehouse
\hsquare{xred} Tom Petty
\htriangle{xred} Georgia O'Keeffe
\end{frame}

\begin{frame}{Packet P2 Question 15}
In a novel by this author, a doctor who is treating bee stings has a boating accident  \tsquare{xred} with an estranged friend as they watch a nearby religious festival. A character created by this writer visits the hypnotist Dr. Lasker Jones,  \hcircle{xgreen} falls in love with the gamekeeper Alec Scudder, and appears  \tcircle{xred} in a novel published posthumously in 1971. Cyril Fielding misses a train in a plot point devised by this author, who wrote about the nature of homosexual relationships in early 20th-Century Britain in his novel Maurice.  \tdiamond{xgreen} For 10 points, name this author of A Passage to India. \htriangle{xred} 

\textbf{Answer}: E.\ M.\ Forster\\
\tsquare{xred} Formate
\tcircle{xred} Maurice (novel)
\htriangle{xred} E. M. Forster
\end{frame}

\begin{frame}{Packet P2 Question 16}
This man’s spring at Barenton was a popular pilgrimage site. French sources usually  \tsquare{xred} referred to this man’s mother as Optima. If his namesake tree, also known as the Priory Oak, was cut down, then the town of Carmarthen would be destroyed. He pointed out that a pool was why Vortigern’s tower kept falling  \hdiamond{xgreen}  \tcircle{xgreen} down. He convinced Aurelius Ambrosius  \htriangle{xgreen} to venture to Ireland to retrieve the stones to build Stonehenge.  \ttriangle{xred} Igraine slept with Uther Pendragon through the machinations  \hsquare{xgreen} of this man, who then organized the sword-in-the-stone contest. For 10 points, name this magician in Arthurian legends.

\textbf{Answer}: Merlin\\
\tsquare{xred} Chartres
\ttriangle{xred} Uther Pendragon
\end{frame}

\begin{frame}{Packet P2 Question 17}
Robert Garland described these events as a ``three-act drama with precise regulations'' in his 1985 book on them. Egkhystristriai made blood sacrifices during these events, where an epikedeion was sung. These events concluded with the prothesis. In the Pre-Classical period, a part of these events involved women beating their breasts and tearing out their hair. During the Hellenistic  \hcircle{xgreen} period, a Charon piece was inserted in their first stage. Pericles gave an oration during a massive one of these events during the Peloponnesian War. For 10 points, name these events centering on deceased Greeks. \hdiamond{xred}  \hsquare{xred}  \htriangle{xred} 

\textbf{Answer}: Funeral\\
\hdiamond{xred} Olympic Games
\hsquare{xred} Thucydides
\htriangle{xred} Witch-hunt
\end{frame}

\begin{frame}{Packet P2 Question 18}
A character in this film receives a frugal Christmas gift of a  \tsquare{xred} pillow with the phrase ``Golfers Never Diet They Just Exist On Greens'' knit on it. In this film, a football coach uses X's and O's to diagram The Tempest. The protagonist throws herself out of a car after listening to an audiobook of The Grapes of Wrath and writes an essay on Sacramento. Lucas Hedges plays the closeted Danny O’Neill in this film. Laurie Metcalf’s character cries after dropping her daughter off to leave for college in, for 10 points, what 2017 coming-of-age film directed by Greta Gerwig and starring Saoirse Ronan? \hdiamond{xred}  \hcircle{xred}  \htriangle{xred} 

\textbf{Answer}: Lady\ Bird\ (film)\\
\tsquare{xred} The Polar Express
\hdiamond{xred} John Wick
\hcircle{xred} Zelda Fitzgerald
\htriangle{xred} Citizen Kane
\end{frame}

\begin{frame}{Packet P2 Question 19}
In a version of this film directed by Melanie Mayron, the characters work to sell plaid kid’s clothes to Sandra Bernhard. The Hives are discussed in a version of this film featuring “Asian voodoo.” The first version of this film, based on a Mary Rodgers novel, cast Jodie Foster as a water skier. Heidi Blickenstaff is a caterer alongside Cozi Zuehlsdorff in a 2018 musical version of this film for the Disney Channel. An earlier version had Jamie Lee Curtis and Lindsay Lohan each playing two characters. For 10 points, name these films about a mother and daughter who swap bodies on the title day. \hdiamond{xred}  \hcircle{xred}  \hsquare{xred}  \htriangle{xred} 

\textbf{Answer}: Freaky\ Friday\\
\hdiamond{xred} The Golden Boy
\hcircle{xred} Love and Mercy (film)
\hsquare{xred} Mean Girls
\htriangle{xred} Selma (film)
\end{frame}

\begin{frame}{Packet P2 Question 20}
On this show’s episode “Penguin One, Us Zero,” a character has an existential crisis when a bagel doesn’t come out of a toaster. A character on this show repeatedly hires prostitutes to shoot her while wearing a bulletproof vest. Its penultimate episode features a confrontation between a bearded and clean-shaven version of the same character, police chief Kevin Garvey. The Guilty Remnant is a cult on this series co-created by Lost's Damon Lindelof and based on books by Tom Perrotta. For 10 points, name this HBO series where 2 percent of the Earth's population vanishes in The Departure. \hdiamond{xred}  \hcircle{xred}  \hsquare{xred}  \htriangle{xred} 

\textbf{Answer}: The\ Leftovers\ (TV\ series)\\
\hdiamond{xred} True Blood
\hcircle{xred} Parks and Recreation
\hsquare{xred} The Wire
\htriangle{xred} Invader Zim
\end{frame}

\begin{frame}{Packet P2 Question 21}
After this man gave a funeral sermon proclaiming ``Where thy treasure is, there is also thy heart'', a moneylender’s still-beating heart was found. This saint is often depicted next to the infant Jesus with a psalter and a book that he retrieved from a thief. He studied at an Augustinian monastery in Coimbra before joining the Franciscans. While at the Marecchia River, he preached to the fishes. A prayer is said to this patron saint of Portugal to retrieve lost  \tsquare{xred} items. For 10 points,  \ttriangle{xred} name this saint who resettled in Padua and who shares his name with a saint who underwent temptations in the desert. \hdiamond{xred}  \hcircle{xred} 

\textbf{Answer}: Anthony\ of\ Padua\\
\tsquare{xred} Andrew the Apostle
\ttriangle{xred} Jude the Apostle
\hdiamond{xred} Saint Christopher
\hcircle{xred} Jude the Apostle
\end{frame}

\begin{frame}{Packet P2 Question 22}
Packing for a vacation to this location inspires a book’s narrator to exclaim “throw the lumber over, man!” after comparing luxuries to “useless lumber.” Daniel Deronda saves Mirah Lapidoth from committing suicide in this location. This location is called ``sweet'' in the final line of each stanza of Edmund Spenser's ``Prothalamion.'' An 1889 book mostly set in this place centers on the narrator J., his friends George and Harris, and the dog Montmorency; that book is Jerome K. Jerome’s Three Men in a Boat. For 10 points, name this river that flows through London. \hdiamond{xred}  \hcircle{xred}  \hsquare{xred}  \htriangle{xred} 

\textbf{Answer}: River\ Thames\\
\hdiamond{xred} Three Men in a Boat
\hcircle{xred} Pendleton Civil Service Reform Act
\hsquare{xred} England
\htriangle{xred} Mount Olympus
\end{frame}

\begin{frame}{Packet P2 Question 23}
In this novel, the only book that a woman takes on a trip is The Betrothed, but she never reads it. A character in this novel wakes up with what he thinks is pig’s blood on his penis before realizing that  \tcircle{xgreen} it’s his wife’s menstrual blood. Two servants in this novel are called “Our Jim” and “My Jim.” A chief in this novel reveals he knows English when he speaks to Maureen, who later  \tdiamond{xgreen} chases after a helicopter at its end. The white Smales flee a war-torn Johannesburg to live with the  \tsquare{xgreen} title character in, for 10 points, what Nadine Gordimer novel  \ttriangle{xgreen} that shares part of its name with a summer month?

\textbf{Answer}: July's\ People\\
\end{frame}

\begin{frame}{Packet P2 Question 24}
The protagonist of this story suggests that by signing crosses in the air “it will be scattering curses abroad in the likeness of holy symbols!” This story, whose purported author is M. de l'Aubepine, includes the tale of a beautiful, dangerous Indian woman who was gifted to Alexander the Great. Dame Lisabetta points out  \tcircle{xgreen} a secret door to its protagonist, who later kills a spider  \tsquare{xgreen} by breathing on it. Dr. Pietro Baglioni  \tdiamond{xgreen}  \ttriangle{xgreen} provides a chemical antidote that kills this story’s title character. For 10 points, name this Nathaniel Hawthorne story about the title poisonous girl.

\textbf{Answer}: Rappaccini's\ Daughter\\
\end{frame}

\begin{frame}{Packet P2 Question 25}
A deity proclaims ``I am something supernatural / not exactly god,  \tcircle{xred} ghost, spirit, angel, principle or element'' in a 2017 translation of this play accompanied by the poem ``I Wish I Were Two Dogs Then I Could Play With Me'' by Anne Carson. A “juggling charmer from Lydia” escapes prison during an earthquake in this play, and later boasts that he's caused "the whole bursting female seed-pod” of the city to worship him. Agave does not realize her son's head is impaled upon her spear in, for 10 points, what Euripides play where  \hcircle{xgreen}  \ttriangle{xgreen} Pentheus is torn  \tsquare{xgreen} apart by crazed followers  \tdiamond{xgreen} of Dionysus?

\textbf{Answer}: The\ Bacchae\\
\tcircle{xred} Common sense
\end{frame}

\begin{frame}{Packet P2 Question 26}
This poem evokes images of ``Ohio's shores and flashing Missouri,''  \hdiamond{xgreen}  \tcircle{xgreen} with the speaker himself located among the ``spires, and the sparkling and hurrying tides'' of the city. An aside in this poem declares that if a creature wasn't able to sing it would ``surely die''. One object in this poem is located ``fronting an old farm-house near the white-wash'd palings.'' The ``tolling tolling bells' perpetual clang'' mark a passing of a  \tsquare{xgreen} coffin in this poem. It describes a ``great star disappear'd'' and a solitary thrush. For 10 points, name this Walt Whitman elegy for Abraham  \ttriangle{xgreen} Lincoln titled for some purple flowers.

\textbf{Answer}: When\ Lilacs\ Last\ in\ the\ Dooryard\ Bloom'd\\
\end{frame}

\begin{frame}{Packet P2 Question 27}
This author wrote of her  \tsquare{xred} father admiring the naked body of the Venus of Urbino in  \ttriangle{xred} a eulogy for John Berger. This author wrote of how “I feels like too straight and singular a phoneme” in an essay written after Obama’s election and wrote another essay about Dana Schutz's Open Casket painting. This author of ``Speaking in Tongues'' and ``Getting In and Out'' wrote a novel in which has Irie Jones gets her hair straightened, Marcus Chalfen works  \hsquare{xgreen} on the FutureMouse program, and Archie Jones is best friends with Samad Iqbal. For  \tdiamond{xgreen}  \tcircle{xgreen}  \htriangle{xgreen} 10 points, name this British author of White Teeth.

\textbf{Answer}: Zadie\ Smith\\
\tsquare{xred} Maria Edgeworth
\ttriangle{xred} Titian
\end{frame}

\begin{frame}{Packet P2 Question 28}
A Bayer employee in this novel uses dolls to reenact car accidents, and a Jehovah's Witness asks for a letter opener to cut off his penis and prove he didn’t rape a young girl. In this novel, Pascual often writes about ``some pyromaniac in Turkey'' rather than the local news. This book’s narrator works for the Genaros and tries to find a priest that will marry him  \ttriangle{xgreen} to a divorcee. An  \tcircle{xgreen} Argentine-hating character in this novel is committed after confusing his plots and killing off his characters in an earthquake. Pedro Camacho cranks out radio  \hsquare{xgreen} serials in, for 10 points, what Mario Vargas  \tdiamond{xgreen} Llosa novel?

\textbf{Answer}: Aunt\ Julia\ and\ the\ Scriptwriter\\
\end{frame}

\begin{frame}{Packet P2 Question 29}
The reporter who broke this scandal tricked lawyer George Latimer into showing him a charge sheet against a man involved in it. The obscure Dispatch News Service first reported this scandal because of a disagreement with the New York Review of Books. Ron Ridenhour wrote to Congress about this event, during which Hugh Thompson  \hdiamond{xgreen} saved lives using a helicopter. Seymour  \tcircle{xgreen} Hersch ran away from JAGs while trying to track down evidence of this scandal, which took place in a village in Quang Ngai Province and was ordered by Lieutenant William Calley.  \tsquare{xgreen} For 10 points, name this 1968 massacre in Vietnam. \htriangle{xred} 

\textbf{Answer}: My\ Lai\ Massacre\\
\htriangle{xred} My Lai Massacre
\end{frame}

\begin{frame}{Packet P2 Question 30}
Voltaire admired an imagined  \tcircle{xred} speech by an indigenous leader in this modern-day country named Colocob. Pedro de Ona was commissioned to write a rival account to the conquest of this country by Garcia Hurtado de Mendoza. The era of conquest in this country ended with the Disaster of Curalaba. The Basque conquistador Alonso de Ercilla turned the  \tsquare{xred} conquest of this country into an epic poem, La Araucana.  \hcircle{xgreen} Pedro de Valdivia fought against the Mapuche in this country. In 1578, Francis Drake attacked this country's port of Valparaiso. For 10 points,  \tdiamond{xgreen} name this rival ABC power to Argentina and Brazil. \htriangle{xred} 

\textbf{Answer}: Chile\\
\tcircle{xred} Candide
\tsquare{xred} Mapuche
\htriangle{xred} Spain
\end{frame}

\begin{frame}{Packet P2 Question 31}
This document inspired Maya Angelou's ``To  \tsquare{xred} Form a More Perfect Union,'' which was carried by a torch relay to a 1977 conference in Houston. This document, one of whose sixteen main points attacks tyrants who have ``monopolized nearly all the profitable employments,''  \tcircle{xgreen}  \hsquare{xgreen} opens by quoting an earlier text’s “inalienable rights.” The phrase ``We hold these truths to be self-evident:  \ttriangle{xgreen} that all men and women are created equal'' appears in this document, which was largely written by Elizabeth Cady Stanton. For 10 points, name this 1848 document drafted  \tdiamond{xgreen} at the Seneca Falls Convention.

\textbf{Answer}: Declaration\ of\ Sentiments\\
\tsquare{xred} I Know Why the Caged Bird Sings
\end{frame}

\begin{frame}{Packet P2 Question 32}
This town lends its name to a 1910 exhibition in New York of the paintings of Lawton Parker, Richard Miller, and Guy Rose.  \hdiamond{xgreen} A traffic cone and some shopping carts appear in a Banksy parody of a painting made in this town. One artist working at this location created the Grandes Decorations and Nympheas cycles. A series of paintings made in this town now comprise  \ttriangle{xred} almost 300 feet of continuous wall space in the Orangerie. A garden in this commune contains a noted Japanese footbridge. For 10 points, name  \tsquare{xgreen} this commune in Northern France where Claude Monet painted  \tcircle{xgreen} water lilies.

\textbf{Answer}: Giverny\\
\ttriangle{xred} Virginia City, Nevada
\end{frame}

\begin{frame}{Packet P2 Question 33}
A photographer from this  \tsquare{xred} country made photos  \hcircle{xgreen} where ``you could look at them forever'' in his New Pictures from Paradise and captured patrons viewing Las Meninas in his Museum Photographs. Images of workers  \tcircle{xred} in this country were captured in the Face  \htriangle{xgreen} of Our Time series. A photographer from here showed the endless shelves of a grocery store in 99 Cent. An artist from here made blurred photo paintings. An artist born here made Homage to the Square but fled to the US after the 1933 closure of the Bauhaus. For 10 points, name this birthplace of Gerhard Richter, Josef  \tdiamond{xgreen} Albers, and the Dusseldorf School.

\textbf{Answer}: Germany\\
\tsquare{xred} Henri Cartier-Bresson
\tcircle{xred} Vietnam
\end{frame}

\begin{frame}{Packet P2 Question 34}
In 1963, Erwin Ratz’s “critical edition” of a symphony by this composer switched the order of its inner movements. The scherzo of this composer’s fourth symphony calls for a violin tuned a whole tone higher to represent “Freund Hein,” a personification of death. His fourth symphony ends with a soprano singing about a child’s vision of heaven. The death of his oldest daughter and his diagnosis with a heart condition inspired the giant wooden mallet in his sixth symphony which delivers  \ttriangle{xred} three blows of fate. For 10 points, name this Austrian composer whose sixth  \tdiamond{xgreen}  \tsquare{xred} symphony is nicknamed “Tragic.” \hcircle{xred} 

\textbf{Answer}: Gustav\ Mahler\\
\ttriangle{xred} Anton Bruckner
\tsquare{xred} Anton Bruckner
\hcircle{xred} Anton Bruckner
\end{frame}

\begin{frame}{Packet P2 Question 35}
S. S. Stewart made these instruments with  \tsquare{xred} a silver wrapped rim. Dock Boggs was plucked from obscurity to play this instrument in Asheville in  \hsquare{xgreen} 1963. Gus Cannon was sometimes nicknamed for this instrument and played in the “old-time” style. Pete Seeger wrote a book  \hdiamond{xgreen} on this instrument, and invented a long-neck variant of it. Laurent Dubois’s history of this “African Instrument” traces its origins from the “rude guitar” used by slaves. A three finger plucking technique for playing it was developed by Earl Scruggs. For 10 points, name this stringed instrument common in bluegrass bands. \hcircle{xred}  \htriangle{xred} 

\textbf{Answer}: Banjo\\
\tsquare{xred} Steelpan
\hcircle{xred} Violin
\htriangle{xred} Violin
\end{frame}

\begin{frame}{Packet P2 Question 36}
In a recent performance of an opera by this man, Robert Burt as Iro gets hit over the head by the harp player as he starts plucking the strings. He's not Bach, but the conductor John Eliot Gardiner founded a choir named for this composer. He wrote a slow-paced aria with echoing ascending and descending scales that is addressed to Charon and titled ``Possente spirito.'' This composer  \tcircle{xgreen} of The Return of Ulysses to his Homeland  \tdiamond{xgreen} wrote an opera in which Ottavia is banished  \tsquare{xgreen} by the Roman emperor for her role in a murder plot. For  \ttriangle{xgreen} 10 points, name this early Italian composer of The Coronation of Poppea and Orfeo.

\textbf{Answer}: Claudio\ Monteverdi\\
\end{frame}

\begin{frame}{Packet P2 Question 37}
While working in this  \ttriangle{xred} style, a painter showed a giant red ``X'' superimposed on a Race Track, and frequently painted ships such as in SS Independence with Cote d'Azur. Another artist who worked in this style placed lipstick above a skull that is reflected in a mirror next to symbols of gambling in her painting Wheel of Fortune. Malcolm Morley and Audrey Flack worked in his style, which was used to depict a series of phonebooths by Richard Estes. For 10 points, Big Nude was the first  \tsquare{xgreen} painting by Chuck Close in what style  \hdiamond{xgreen} that tried to simulate the precision of the camera? \hcircle{xred} 

\textbf{Answer}: Photorealism\\
\ttriangle{xred} Speechwriter
\hcircle{xred} Minimalism
\end{frame}

\begin{frame}{Packet P2 Question 38}
Historians Audrey Truschke and Wendy Doniger have been targeted by Section 295A of this country's penal code. The so-called ``King of Good Times'' fled from this country owing a billion dollars in debt after his airline business collapsed in 2012. A newspaper in this country spent just \$8 to access its supposedly secure national ID system called UIDAI. The Amazon rival Flipkart is based here. This country's prime minister has introduced a nationwide Goods and Services Tax and controversially demonetized larger bank notes. For 10 points, name this country ruled by BJP leader Narendra Modi. \hdiamond{xred}  \hcircle{xred}  \hsquare{xred}  \htriangle{xred} 

\textbf{Answer}: India\\
\hdiamond{xred} Libya
\hcircle{xred} North Korea
\hsquare{xred} Hungary
\htriangle{xred} France
\end{frame}

\begin{frame}{Packet P2 Question 39}
Buildings in this city  \tsquare{xred} erected before 1770 have upper stories that almost touch because of their ``retreating facades.'' The word ``urbanization'' was coined by the man who built this city’s octagonal blocks in a plan known as  \hcircle{xgreen} the ``Eixample''. This  \hdiamond{xgreen} city’s radical mayor wrote the book Mortgaged Lives and is named Ada Colau. Freddie Mercury died before he could perform  \hsquare{xgreen} a song title for this city at an event whose mascot was the sheepdog Cobi. The first Dream Team won gold in this city. For 10 points, name this host of the 1992 Summer Olympics, a Catalan city home to La Sagrada Familia. \htriangle{xred} 

\textbf{Answer}: Barcelona\\
\tsquare{xred} Summer camp
\htriangle{xred} New York City
\end{frame}

\begin{frame}{Packet P2 Question 40}
Brutalist art fans are campaigning to save buildings in this country  \tcircle{xred} such as the H-shaped Golden Mile Tower. Becca D'Bus was a star of the drag scene along Bugis Street in this country. Linguist Jakob Leimgruber has studied a variant of English in this country where ``lah'' is often added to the end of phrases. Grant Associates created 18 steel “Supertrees” in this country. The Capella Hotel on a former pirate haven in this country was where the U.S. agreed to stop joint military exercises after meeting with North Korea in 2018. For 10 points, Lee Kuan Yew ruled  \tdiamond{xgreen}  \tsquare{xgreen} what Asian city state? \htriangle{xred} 

\textbf{Answer}: Singapore\\
\tcircle{xred} I. M. Pei
\htriangle{xred} Peru
\end{frame}

\begin{frame}{Packet P2 Question 41}
A 1997 Economist cover story called this politician a “Serial Blunderer” after he was forced to provide an antidote in a botched assassination attempt. This former  \ttriangle{xred} UN Ambassador did CNN interviews wearing a gas mask during the Gulf War. He’s received controversial gifts from Hollywood mogul Arnon Milchan and may have been bribed to buy German submarines. In 2018, a minority population in his country had their language downgraded to “special.” He got Donald Trump to move the US Embassy in his country and chairs the Likud party. For 10 points, name this Prime  \hsquare{xgreen} Minister of Israel. \hdiamond{xred}  \hcircle{xred} 

\textbf{Answer}: Benjamin\ Netanyahu\\
\ttriangle{xred} Abdullah II of Jordan
\hdiamond{xred} Benjamin Netanyahu
\hcircle{xred} Cristina Fernández de Kirchner
\end{frame}

