\begin{frame}{Packet P3 Question 1}
Processes named for this  \ttriangle{xred} man can be constructed on an arbitrary symmetric inner product space with a countable basis using  \tcircle{xred} the Ito isometry. Weiner processes such as Brownian motion are examples of a broader class of processes named for this man. The pdf of this man's namesake distribution is a rescaling of e to the negative x minus mu squared over 2 times the variance. For 10 points, name this German mathematician whose  \ttriangle{xyellow} namesake distribution is commonly called  \tcircle{xyellow} a bell curve. \tdiamond{gray}  \tsquare{gray} 

\textbf{Answer}: Carl\ Friedrich\ Gauss\\
\ttriangle{xred} Matrix decomposition
\tcircle{xred} David Hilbert
\tdiamond{gray} Bernhard Riemann
\tsquare{gray} Bernhard Riemann
\end{frame}

\begin{frame}{Packet P3 Question 2}
John  \tcircle{xred} Graham-Cumming's Plan 28 is a modern-day effort to build an early version of these machines described in paper by Luigi Manabrea. The court case Honeywell v. Sperry Rand determined that John Atanasoff, rather than Mauchly and Eckert, designed the first version of these machines. Early versions of these machines, such as ENIAC, used ring counters made of vacuum tubes to store numbers. For 10 points, name these machines that can be used to run programs. \tdiamond{gray}  \tcircle{gray}  \tsquare{gray}  \ttriangle{gray} 

\textbf{Answer}: Computer\\
\tcircle{xred} Symmetric matrix
\tdiamond{gray} Bicycle
\tcircle{gray} Symmetric matrix
\tsquare{gray} Vending machine
\ttriangle{gray} Autoclave
\end{frame}

\begin{frame}{Packet P3 Question 3}
This is the shape of a  \tsquare{xred} work containing the phrase ``causarum cognitio''  \tdiamond{xyellow}  \tcircle{xred} that is located above Raphael's School of Athens. God is placed within this shape as the largest figure in the mosaic on the ceiling of the Florence Cathedral. Tondos are works of art with this shape. Both Cimabue's Santa Trinita Maesta and Giotto's Ognissanti Madonna depict golden objects with this shape surrounding the head of the Virgin Mary. Along with a square, Leonardo da Vinci's Vitruvian Man is placed within, for 10 points, what shape used by Renaissance artists to draw a halo? \tcircle{gray}  \tsquare{gray}  \ttriangle{gray} 

\textbf{Answer}: Circle\\
\tsquare{xred} Cone
\tcircle{xred} The School of Athens
\tcircle{gray} The School of Athens
\tsquare{gray} Cone
\ttriangle{gray} Parabola
\end{frame}

\begin{frame}{Packet P3 Question 4}
While Einstein provided the groundwork, this physicst was the first to write E equals m c squared in his 1907 paper on the elementary electrical charge.  However, in 1922 he called Einstein and Sommerfeld a bad influence in his ``The Present Crisis in German Physics'' before joining with Lenard to lead  \tcircle{xred}  \tsquare{xred} the ``Deutsche Physik'' movement.  An effect known for this man allows fast switching in QCSE optical modulators.  Winning the 1919 Nobel prize for showing that an electric field splits  \tsquare{xyellow} the spectral lines of a dipole, for  \ttriangle{xred} 10 points, name this German physicist who names the electric analog of the Zeeman  \tdiamond{xgreen} effect. \tcircle{gray}  \ttriangle{gray} 

\textbf{Answer}: Johannes\ Stark\\
\tcircle{xred} Photoelectric effect
\tsquare{xred} Photoelectric effect
\ttriangle{xred} Stark effect
\tcircle{gray} Photoelectric effect
\ttriangle{gray} Stark effect
\end{frame}

\begin{frame}{Packet P3 Question 5}
Although it has nothing  \tsquare{xred} to do with ergodic theory, any spherically symmetric solution to a set of equations name for this system must be static and asymptotically flat according to Birkhoff's theorem. The exchange of virtual photons between two otherwise uncharged plates placed in this system causes a net force in the Casimir effect. When the energy-momentum tensor equals zero in a region, the Einstein field equations  \tcircle{xred} are named for this system. For 10 points, what system consists of space devoid of all matter? \tdiamond{xgreen}  \tcircle{gray}  \tsquare{gray}  \ttriangle{gray} 

\textbf{Answer}: Vacuum\\
\tsquare{xred} Flavor
\tcircle{xred} General relativity
\tcircle{gray} General relativity
\tsquare{gray} Flavor
\ttriangle{gray} Email
\end{frame}

\begin{frame}{Packet P3 Question 6}
In one novel, spirits flock to obtain this product and pepper soup from Madame Koto. While on a quest to obtain this stuff, a character defeats  \tcircle{xyellow} the red-fish and red-bird that are terrorizing the Red-town, and rescues his future wife from a “complete gentleman” who is really just a skull. That character obtains a magic egg from a servant who made this substance  \tcircle{xred} for him after he finds him in Deads’ Town. Jugs of this substance are drunk throughout The Famished Road and Things Fall  \tsquare{xred} Apart. Amos Tutuola titled a novel for a “drinkard” of, for 10 points, the “palm” type of what alcohol beverage? \tdiamond{gray}  \tsquare{gray}  \ttriangle{gray} 

\textbf{Answer}: Wine\\
\tcircle{xred} Kola Ogunmola
\tsquare{xred} Ben Okri
\tdiamond{gray} Kola Ogunmola
\tsquare{gray} Ben Okri
\ttriangle{gray} Kola Ogunmola
\end{frame}

\begin{frame}{Packet P3 Question 7}
A set of these objects depicting the hunt were designed for the brother of Maximilian II by the teacher of Albrecht Durer. An entry in a five-part series about these objects by Paul Cezanne depicts two  \tdiamond{xyellow} men in brown seated at a table with their hands in front of a wine bottle. A boy's  \tsquare{xyellow} adversary holds a set of these objects behind his back in a painting by Caravaggio. Brown and Bigelow  \tcircle{xgreen} commissioned Cassius Coolidge to create a series in which animals interact with these objects. For 10 points, name these objects held by dogs as they play poker in His Station and Four Aces. \ttriangle{gray} 

\textbf{Answer}: Playing\ card\\
\ttriangle{gray} Skull
\end{frame}

\begin{frame}{Packet P3 Question 8}
The firm that handled international public relations for this organization, Robert R. Mullen and Company, was also a CIA front.  In 1868, it purchased the Eagle Emporium to form ZCMI which used the slogan ``America's First Department Store''.   The 1887 Edmunds-Tucker act dissolved this organization and seized its assets, and Senator Reed Smoot's membership was the subject of a four year hearing.  This religious organization owns Deseret Industries and the world's largest Family History Library.  For 10 points, name this church founded by Joseph Smith and headquartered  \tsquare{xyellow} in Salt  \tcircle{xyellow}  \ttriangle{xyellow} Lake City.  \tdiamond{xgreen} 

\textbf{Answer}: The\ Church\ of\ Jesus\ Christ\ of\ Latter-day\ Saints\\
\end{frame}

\begin{frame}{Packet P3 Question 9}
In a liquid mixture, the i-th compound's value for this quantity can be computed by differentiating the excess Gibbs energy with respect to x\_i. Another model computes this quantity by differentiating the virial expansion  \tsquare{xgreen} of the excess Gibbs  \tcircle{xgreen} energy with respect to molality. In addition to using the Margules and Pitzer models, you can compute this quantity with the Debye-Huckel equation. For 10 points,  \ttriangle{xgreen} name this dimensionless quantity that  \tdiamond{xgreen} models a liquid's deviation from being an ideal solution.

\textbf{Answer}: Activity\ coefficient\\
\end{frame}

\begin{frame}{Packet P3 Question 10}
This process is compromised by a nonsense mutation in dogs leading to Tarui's disease. An intermediate in this process is formed by an aldol cleavage before being processed by a catalytically perfect enzyme.  \tcircle{xgreen} That anion is a byproduct of the breakdown of fructose  \tdiamond{xyellow} 1,6 biphosphate and is DHAP. This process  \tsquare{xred} begins with the phosphorylation carried  \tsquare{xyellow} out by hexokinase, while its products are ultimately converted into acetyl-coA. For 10 points, name this anaerobic process, the first step in cellular respiration. \ttriangle{gray} 

\textbf{Answer}: Glycolysis\\
\tsquare{xred} Catalase
\ttriangle{gray} Citric acid cycle
\end{frame}

\begin{frame}{Packet P3 Question 11}
An exact answer to how this quantity changes between two states is given by the Zwanzig relation or exponential averaging. The change in this quantity between two systems in the same configuration can be approximated with the BAR method. This quantity is equal to negative k times temperature times the logarithm of the partition function. This  \tsquare{xgreen}  \ttriangle{xyellow} quantity represents the maximum obtainable work from a reversible  \tcircle{xgreen} process and  \tdiamond{xgreen} is equal to the internal energy minus entropy times temperature. For 10 points, name this free energy not named for Gibbs.

\textbf{Answer}: Helmholtz\ free\ energy\\
\end{frame}

\begin{frame}{Packet P3 Question 12}
An indirect agglutination assay used to detect  \tsquare{xred} this disease first sensitizes gelatin particles to antigens of this disease before checking for gelatin clumping. Lyophilized  \tcircle{xred} suspensions of this disease's causative agent are mixed with the patient's serum in another test for this disease. Screening methods for this disease such as VDRL are followed  \tcircle{xyellow} by TPPA and FTP-ABS tests for it. Painless lesions called  \tsquare{xyellow} chancres often  \tdiamond{xgreen} accompany the early stages of this disease, while many patients with its late-stage form go insane. For 10 points, name this sexually transmitted disease that is  \ttriangle{xyellow} caused by Treponema pallidum.

\textbf{Answer}: Syphilis\\
\tsquare{xred} ELISA
\tcircle{xred} Collagen
\end{frame}

\begin{frame}{Packet P3 Question 13}
This time signature is  \tdiamond{xyellow}  \tsquare{xred} used for most of the  \ttriangle{xred} ``Aria'' from Heitor Villa-Lobos's Bachianas brasileiras. This time signature is used in the opening and closing sections of Sergei Rachmaninoff's Isle of the Dead to represent the motion of water. It alternates with a triple meter time signature in the ``Promenade'' section of Pictures at an Exhibition. A two-note piano vamp plays throughout a piece in this time signature from the album Time Out by David Brubeck. For 10 points, give this time signature whose beats often have a ``strong-weak-weak-medium-weak'' pattern. \tcircle{gray}  \tsquare{gray}  \ttriangle{gray} 

\textbf{Answer}: Quintuple\ meter\\
\tsquare{xred} Mahavishnu Orchestra
\ttriangle{xred} Triple metre
\tcircle{gray} Night
\tsquare{gray} Mahavishnu Orchestra
\ttriangle{gray} Triple metre
\end{frame}

\begin{frame}{Packet P3 Question 14}
This policy is the subject of much of Barry Eichengreen's work, which claims that its ``fetters'' were a prime cause of instability during the interwar period. The  \tsquare{xred} 1926 general strike in Britain partly resulted from the re-implementation of this policy by Winston Churchill. The U.S. abandoned this policy in the ``Nixon Shock,'' effectively ended the Bretton Woods system. Adhering to this policy would ``press down upon the brow of labor this crown of thorns'' according to a speech against it from the 1896 DNC. For 10 points, name this policy under which coinage is backed by a single precious metal. \tdiamond{gray}  \tcircle{gray}  \tsquare{gray}  \ttriangle{gray} 

\textbf{Answer}: Gold\ standard\\
\tsquare{xred} Stanley Baldwin
\tdiamond{gray} Cross of Gold speech
\tcircle{gray} Conscription
\tsquare{gray} Stanley Baldwin
\ttriangle{gray} Conscription
\end{frame}

\begin{frame}{Packet P3 Question 15}
Examples of these structures include the megalithic Hagar Qim complex, which was built during the Ggigantija period on Malta. Wooden objects called xoana were typically found within these structures. Another of these buildings contains 92 carved plaques called metopes and was financed with appropriations from the Delian treasury. One of these structures in Ephesus was among the Seven Wonders of the ancient world. Several of them contained exquisite chryselephantine statues sculpted by Phidias. For  \tcircle{xred} 10 points, name these buildings exemplified by the Parthenon. \tdiamond{gray}  \tcircle{gray}  \tsquare{gray}  \ttriangle{gray} 

\textbf{Answer}: Temple\\
\tcircle{xred} Parthenon
\tdiamond{gray} Ephesus
\tcircle{gray} Parthenon
\tsquare{gray} Parthenon
\ttriangle{gray} Mosque
\end{frame}

\begin{frame}{Packet P3 Question 16}
A song titled “Hey, [these  \ttriangle{xred} people]” was first sung at a meeting named for this group that a young Mikhail Bakunin attended. Prince Windischgratz broke up that 1848 congress named for these people that was organized by František Palacký. A kingdom whose name means “the land of [this group]” was founded under Peter I, whose  \tsquare{xred} son Alexander I was killed in Marseilles in 1934. The Nazi  \tcircle{xred} concept of “Drang nach Osten” targeted the lands of these people, who name a state that resisted the Nazis with Partisans led by Josip Tito. For 10 points, name this people that includes Russians and Serbs. \tdiamond{gray}  \tcircle{gray}  \tsquare{gray}  \ttriangle{gray} 

\textbf{Answer}: Slavs\\
\ttriangle{xred} Give My Regards to Broadway
\tsquare{xred} International Workingmen's Association
\tcircle{xred} Huguenots
\tdiamond{gray} Chetniks
\tcircle{gray} Huguenots
\tsquare{gray} International Workingmen's Association
\ttriangle{gray} Give My Regards to Broadway
\end{frame}

\begin{frame}{Packet P3 Question 17}
This sort of natural feature  \tsquare{xred} names Vere Gordon Childe’s theory that the invention of agriculture arose from climate change. Independent city-states based on features of this sort, such as Karakhoja and Khotan, were defeated during Emperor Taizong’s campaigns in the Tarim Basin. An oracle of Amun Ra was located in one of these places called Siwa. The caravanserai inns of the Silk Road were typically built in these areas. For 10 points, name these areas surrounding water sources in deserts. \tdiamond{gray}  \tcircle{gray}  \tsquare{gray}  \ttriangle{gray} 

\textbf{Answer}: Oasis\\
\tsquare{xred} Sound
\tdiamond{gray} Xinjiang
\tcircle{gray} Committee for the Promotion of Virtue and the Prevention of Vice (Saudi Arabia)
\tsquare{gray} Sound
\ttriangle{gray} Royal forest
\end{frame}

\begin{frame}{Packet P3 Question 18}
The priest Fernando Cardenal led a campaign for this goal launched by the Sandinistas in 1980. That campaign was inspired by a 1961 campaign for this goal, which  \tcircle{xred} featured groups such as the “Conrado Benitez” Brigade and was masterminded by Che Guevara in Fidel Castro’s  \tsquare{xred} Cuba. The UNESCO award for initiatives promoting this goal is named for  \ttriangle{xred} King Sejong, who is credited with an invention that increased the rate of this quality among the ordinary people of Korea; that invention was the Hangul script. For 10 points, give this term for the ability to read and write. \tdiamond{gray}  \tcircle{gray}  \tsquare{gray}  \ttriangle{gray} 

\textbf{Answer}: Literacy\\
\tcircle{xred} Irish Home Rule movement
\tsquare{xred} Bay of Pigs Invasion
\ttriangle{xred} Irish Home Rule movement
\tdiamond{gray} Cuba
\tcircle{gray} Irish Home Rule movement
\tsquare{gray} Bay of Pigs Invasion
\ttriangle{gray} Irish Home Rule movement
\end{frame}

\begin{frame}{Packet P3 Question 19}
This person was made the monarch of Poland via an oath given in Lwów by John II Casimir. Miners skirmished with the German soldiers who were sent to break up crowds after this person supposedly visited the town of Marpingen. Lúcia dos Santos wrote down three secrets allegedly authored by this person.  \tsquare{xred} Three children claimed to have seen this person in 1917 in Fatima, Portugal, while Bernadette Soubirous claimed to have seen her in Lourdes in 1858. For 10 points, name this religious figure whose alleged apparitions have earned her titles like “Our Lady of Guadulpe.” \tdiamond{gray}  \tcircle{gray}  \tsquare{gray}  \ttriangle{gray} 

\textbf{Answer}: Mary,\ mother\ of\ Jesus\\
\tsquare{xred} Our Lady of Fátima
\tdiamond{gray} Our Lady of Fátima
\tcircle{gray} Anne Boleyn
\tsquare{gray} Our Lady of Fátima
\ttriangle{gray} Clarence Earl Gideon
\end{frame}

\begin{frame}{Packet P3 Question 20}
At the climax of this novel, a shield-toting, fur-clad man on a black horse tries to get the main character hanged. Chapter 5 of this novel is occupied with a blind old man’s speech about “the Founder.” After bringing a wealthy man to a shack where a sharecropper describe how he impregnated his daughter, then taking him  \tdiamond{xyellow} to a brothel where he passes out, the protagonist of this novel is expelled from school. This novel’s narrator describes how he came to live in a brightly-lit basement after working as a spokesperson for the Brotherhood.  \ttriangle{xyellow} For 10 points, name this magnum opus of Ralph Ellison. \tcircle{xgreen}  \tsquare{xgreen} 

\textbf{Answer}: Invisible\ Man\\
\end{frame}

\begin{frame}{Packet P3 Question 21}
In a scene from this novel, a blind man named  \tdiamond{xyellow} Pew is trampled  \tcircle{xgreen}  \tsquare{xyellow} to death by a group of horsemen in the street. A boy in this novel hides behind a door with a man who is missing two fingers, and who is later revealed to be named Black Dog. An animal in this novel repeats the phrase ``Pieces of Eight'' and is named for his former owner, Captain Flint. In this novel, a man with one leg plans a mutiny aboard the Hispanola to find a buried treasure that is marked by an ``X'' on a map. For 10 points, name this novel by Robert Louis Stevenson. \ttriangle{xgreen} 

\textbf{Answer}: Treasure\ Island\\
\end{frame}

\begin{frame}{Packet P3 Question 22}
Beverly Watson discusses a line of poetry implied to be spoken by this title group, ``Life is very long,'' in August: Osage County. The voices of this group are compared to ``rats' feet over broken glass /  \tdiamond{xyellow} In our dry cellar.'' This group is said to ``grope together / And avoid speech / Gathered on the banks of the tumid river.'' This group's members are described as ``Leaning together, headpiece filled with straw'' and are implied  \tsquare{xgreen} to recite the lines,  \tcircle{xgreen} ``Here we go round the prickly pear.''  \ttriangle{xgreen} For 10 points, what group titles a T. S. Eliot poem in which the world ends ``not with a bang, but a whimper?''

\textbf{Answer}: The\ Hollow\ Men\\
\end{frame}

\begin{frame}{Packet P3 Question 23}
An author described life with his Swedish immigrant parents in a city in this state in the memoir Always the Young Strangers. Edmund Wilson’s Patriotic Gore mocks a popular two-volume biography of a man from this state whose second volume, The War Years, won the the 1940 Pulitzer. A place in this state is told “I have seen your painted women under the gas lamps luring the farm boys” in a poem that calls it a “Tool Maker,” “Stacker of Wheat, Player with Railroads,” and “Hog Butcher for the World.”  \ttriangle{xred} For 10 points, Carl Sandburg wrote a biography  \tcircle{xred}  \tsquare{xred} of what state’s native son Abraham Lincoln? \tdiamond{gray}  \tcircle{gray}  \tsquare{gray}  \ttriangle{gray} 

\textbf{Answer}: Illinois\\
\ttriangle{xred} Chicago (poem)
\tcircle{xred} Chicago (poem)
\tsquare{xred} Chicago (poem)
\tdiamond{gray} Chicago
\tcircle{gray} Chicago (poem)
\tsquare{gray} Chicago (poem)
\ttriangle{gray} Chicago (poem)
\end{frame}

\begin{frame}{Packet P3 Question 24}
In one of these works, the invisible Titivillus plots to plant weeds in the protagonist’s corn. One of these works inspired the title of a Philip Roth novel about a man who dies during a stent surgery. In one of these works, the protagonist’s cousin complains of a toe cramp to avoid going on a journey with him. At the end of a work in this genre, the protagonist climbs into his coffin with Good Deeds, having been abandoned by his Kindred and Goods. Mankind and Everyman exemplify,  \tdiamond{xyellow} for 10 points, what medieval genre of  \tsquare{xred} drama that evolved from similarly-themed Mystery Plays? \tcircle{gray}  \tsquare{xgreen}  \ttriangle{gray} 

\textbf{Answer}: Morality\ play\\
\tsquare{xred} Everyman
\tcircle{gray} Gibbs free energy
\ttriangle{gray} Harry Potter fandom
\end{frame}

\begin{frame}{Packet P3 Question 25}
This author’s love poetry is collected in a volume titled A String of Flowers, Untied. Richard Bowring translated a diary by this author that famously calls another writer “dreadfully  \tdiamond{xred} conceited.” A term meaning “the pathos of things” originates from studies of this author’s works. This author’s pen-name derives from a character who is attacked by the living ghost of her husband’s mistress. A novel by this author includes “Vanished Into the Clouds,” a blank chapter that signifies the protagonist’s death. For 10 points, name this lady-in-waiting who wrote The  \tdiamond{xyellow} Tale of Genji. \tcircle{gray}  \tsquare{gray}  \ttriangle{gray} 

\textbf{Answer}: Murasaki\ Shikibu\\
\tdiamond{xred} Sarah Orne Jewett
\tcircle{gray} Agatha Christie
\tsquare{gray} Jun'ichirō Tanizaki
\ttriangle{gray} Jane Austen
\end{frame}

\begin{frame}{Packet P3 Question 26}
One man concludes that a character with this profession killed himself by jumping out of a window and striking some rocks before being found in a bed of straw. Another man with this profession is found with his head sticking down in a vat of pig's blood on the second day. Characters of this profession serve as the librarians  \tcircle{xred} of the Aedificium and include Berengar of Arundel, who is found murdered two days after Adelmo. Jorge of Burgos is a blind character with, for 10 points, what job that William of Baskerville and Adso of Melk have in  \tsquare{xred} The Name of the Rose? \tdiamond{gray}  \tcircle{gray}  \tsquare{gray}  \ttriangle{gray} 

\textbf{Answer}: Monk\\
\tcircle{xred} Teacher
\tsquare{xred} The Name of the Rose
\tdiamond{gray} Firefighter
\tcircle{gray} Teacher
\tsquare{gray} The Name of the Rose
\ttriangle{gray} Detective
\end{frame}

\begin{frame}{Packet P3 Question 27}
In this election, a candidate's habit of scheduling games of catch with his press secretary was criticized in the piece ``Insider Baseball.'' An ad during this campaign excoriated one candidate's veto of mandatory minimums for drug dealers while criticizing his ``revolving door'' policy. That ad was created by the controversial Lee Atwater, a campaign manager in this election. The ``Weekend Passes'' advertisement about the furlough of William Horton ran during this election. For 10 points, name this election in which Michael Dukakis was defeated  \tdiamond{xyellow}  \tcircle{xyellow}  \tsquare{xgreen} by George H.W. Bush? \ttriangle{gray} 

\textbf{Answer}: United\ States\ presidential\ election,\ 1988\\
\ttriangle{gray} United States presidential election, 1960
\end{frame}

\begin{frame}{Packet P3 Question 28}
The United Nations commonly uses the ratio of this quantity to GDP as a growth indicator, with Guinea  \tcircle{xyellow} having the highest value of that ratio at about 75%. For a closed economy, this quantity is exactly equal to savings. The  \tdiamond{xyellow} ``net'' amount of this quantity is positive when the total stock is increasing over  \tsquare{xred} time, and can be calculated as its ``gross'' amount minus total depreciation costs. An identity sets GDP equal to consumption, plus government expenditure, plus net exports, plus this quantity. For 10 points, give this quantity which equals  \tcircle{xred} total expenditure on capital in an economy. \tsquare{gray}  \ttriangle{gray} 

\textbf{Answer}: Investment\\
\tsquare{xred} Gross domestic product
\tcircle{xred} Gross domestic product
\tsquare{gray} Gross domestic product
\ttriangle{gray} Density
\end{frame}

\begin{frame}{Packet P3 Question 29}
A passage about this object was copied wholesale for a poem about Cycnus’s defeat by Heracles. A field high with grain, a field being ploughed, a star map featuring Orion and Ursus Major, a city at peace, and a city at war are among the many images on this object. This object, which  \tcircle{xred} is described in Book 18 of a poem in the first known example of ekphrasis, is  \tdiamond{xyellow}  \ttriangle{xyellow} forged along with armor by Hephaestus at the request of Thetis. For 10 points, identify this defensive object that a Greek hero wears on his arm during his fight with Hector in the Iliad. \tcircle{gray}  \tsquare{gray} 

\textbf{Answer}: The\ Shield\ of\ Achilles\\
\tcircle{xred} Sun
\tcircle{gray} Sun
\tsquare{gray} Achilles
\end{frame}

\begin{frame}{Packet P3 Question 30}
As an adjective, this  \tsquare{xred} word denotes a movement whose “Sidhi program” is supposed to allow “yogic flying” and whose teaching in public schools is advocated by the David Lynch Foundation. This word denotes a type of meditation developed by Maharishi Mahesh Yogi. The movement of this name included Elizabeth Peabody, who published  \tdiamond{xyellow}  \tsquare{xyellow} the first English translation of the Lotus Sutra, in its magazine The Dial. Some New Age religious movements have adopted the idea of the “Over-Soul” introduced by a member of this movement. For 10 points, name this movement that included  \tcircle{xyellow} Ralph Waldo Emerson. \ttriangle{xgreen} 

\textbf{Answer}: Transcendentalism\\
\tsquare{xred} Perfection
\end{frame}

\begin{frame}{Packet P3 Question 31}
A thinker of this school monistically claimed that the idea of external relations leads to an infinite regress. A.J. Ayer mocked a thinker of this movement for writing that “the Absolute  \tcircle{xred} enters into, but is itself incapable of, evolution and progress.” J.E.M. McTaggart and F.H. Bradley exemplified the “British” branch of this school, which analytic philosophy developed in reaction to. To argue for this position, a philosopher formulated the “master argument” and claimed that “to be is to be perceived.” For 10 points, name this position of George Berkeley,  \tsquare{xyellow} which holds that reality is dependent on mind. \tdiamond{gray}  \tcircle{gray}  \ttriangle{gray} 

\textbf{Answer}: Idealism\\
\tcircle{xred} Pragmatism
\tdiamond{gray} George Berkeley
\tcircle{gray} Pragmatism
\ttriangle{gray} George Berkeley
\end{frame}

\begin{frame}{Packet P3 Question 32}
A 3rd century BC text titled for the “Oracle of” a user of this tool prophecies the  \ttriangle{xred} destruction caused by the rule of the “beltwearers.” A god commonly associated with this tool features  \tcircle{xred} in royal birth myths with his wife, the frog goddess Heqet, and was worshipped at Esna and on Elephantine Island. This  \tsquare{xred} tool is used to create human babies by the ram-headed god Khnum. This tool was used to create” red-figure” and “black-figure” artworks in ancient Greece. For 10 points, name this device used to shape wet clay into ceramics. \tdiamond{gray}  \tcircle{gray}  \tsquare{gray}  \ttriangle{gray} 

\textbf{Answer}: Potter's\ wheel\\
\ttriangle{xred} Smallpox vaccine
\tcircle{xred} Smallpox vaccine
\tsquare{xred} Khnum
\tdiamond{gray} Vase
\tcircle{gray} Smallpox vaccine
\tsquare{gray} Khnum
\ttriangle{gray} Smallpox vaccine
\end{frame}

\begin{frame}{Packet P3 Question 33}
While he is surrounded by wild animals, the possessor of this object hears pipes in the distance and sings ``Wie stark ist nicht dein Zauberton.'' A quintet sings ``Hm! Hm! Hm! Hm!'' after  \tcircle{xgreen} this object and a set of silver bells are distributed by three women. The possessor of this object undergoes a trial  \tsquare{xgreen} by silence, then is protected by it when undergoing trials of fire and water in the Temple of Ordeal with his lover Pamina.  \tdiamond{xyellow} For 10 points, Tamino is given what title object in an opera by Wolfgang Amadeus Mozart? \ttriangle{xgreen} 

\textbf{Answer}: The\ Magic\ Flute\\
\end{frame}

\begin{frame}{Packet P3 Question 34}
An event centered on works  \tsquare{xred} of this musical genre began with the arrival of the leader of “The Insane Coho Lips” and the model Lorelei. At the urging of Willie Stargell, a team adopted a song in this genre as a symbol en route to overcoming a 3-1 deficit in the World Series against the Orioles. Bill Veeck organized an event opposing this genre. The White Sox were forced to forfeit a game due to a riotous “Demolition Night” for music of this genre. The “We are Family” Pirates team took their nickname from a song in, for 10 points, what genre popularized by the film Saturday Night Fever. \tdiamond{gray}  \tcircle{gray}  \tsquare{gray}  \ttriangle{gray} 

\textbf{Answer}: Disco\\
\tsquare{xred} 1939 New York World's Fair
\tdiamond{gray} Satire
\tcircle{gray} Film noir
\tsquare{gray} 1939 New York World's Fair
\ttriangle{gray} Wuxia
\end{frame}

\begin{frame}{Packet P3 Question 35}
A song titled for this  \ttriangle{xred} man begins with the singer correcting Ken Scott’s pronunciation of this man’s name. This person inspired the name of a Courtney Taylor-Taylor-fronted band that scored the sleeper hit “Bohemian Like You” in 2001. David Bowie included a song titled for this non-Bob Dylan man on Hunky Dory, and played him in the film Basquiat. This man’s Exploding Plastic Inevitable events showcased  \tdiamond{xyellow} a band who sang “Sunday morning, brings the dawning” on an album whose cover  \tsquare{xred} he designed. For 10 points, what artist created the banana print that adorns the Velvet Underground’s debut album? \tcircle{gray}  \tsquare{gray}  \ttriangle{gray} 

\textbf{Answer}: Andy\ Warhol\\
\ttriangle{xred} Give My Regards to Broadway
\tsquare{xred} The Velvet Underground
\tcircle{gray} Banana
\tsquare{gray} The Velvet Underground
\ttriangle{gray} Give My Regards to Broadway
\end{frame}

\begin{frame}{Packet P3 Question 36}
In a 2017 film, two characters make a pinky promise at a memorial to this person after impulsively driving 300 miles in the middle of the night. As depicted in The Disaster Artist, Tommy Wiseau took the line “You’re tearing me apart, Lisa!” from a movie starring this actor. In La La Land, Sebastian and Mia watch a film starring this actor, then dance at the Griffith Observatory where he was challenged to a knife fight. This actor starred in East of Eden and Giant prior to his 1955 death in a car crash. For 10 points, name this star of Rebel Without a Cause. \tdiamond{xgreen}  \tcircle{gray}  \tsquare{xgreen}  \ttriangle{gray} 

\textbf{Answer}: James\ Dean\\
\tcircle{gray} George Clooney
\ttriangle{gray} Tom Cruise
\end{frame}

\begin{frame}{Packet P3 Question 37}
It's not New York, but  \tcircle{xred} a viral video of Black  \tsquare{xred} bloc protesters directing traffic and harassing drivers sparked a violent Proud Boys march in this state. Those protests were held in the wake of the police shooting of Patrick Kimmons. Ricky Best and Taliesin Namkai-Meche were stabbed to death on a train in this state after condemning the anti-Muslim tirade of the white nationalist Jeremy Christian. Backlash against Antifa activities in this state helped Knute Buehler's campaign in this state's 2018 gubernatorial election. For 10 points, what state recently re-elected Kate Brown as its governor? \tdiamond{gray}  \tcircle{gray}  \tsquare{gray}  \ttriangle{gray} 

\textbf{Answer}: Oregon\\
\tcircle{xred} Japan
\tsquare{xred} The Fox (What Does the Fox Say?)
\tdiamond{gray} Idaho
\tcircle{gray} Japan
\tsquare{gray} The Fox (What Does the Fox Say?)
\ttriangle{gray} Pennsylvania
\end{frame}

\begin{frame}{Packet P3 Question 38}
In an opera titled for this object, a woman known as the ``Muscovite Venus'' reminisces about singing Laurette's aria before Madame de Pompadour.  \tcircle{xred} The resident of Room 17 at the Obuhov hospital obsessively mutters a six-word phrase whose final word refers to this object. By possessing this object and thirteen objects of a different kind, one can ``shoot the moon'' in Hearts. This object is usually used as the namesake card of Old Maid. In a story, this object appears after a three and a seven, causing Herman to go insane. For 10 points, name  \tsquare{xyellow} this card that titles an Alexander Pushkin story. \tdiamond{gray}  \tcircle{gray}  \ttriangle{gray} 

\textbf{Answer}: Queen\ of\ spades\\
\tcircle{xred} Georges Bizet
\tdiamond{gray} Light
\tcircle{gray} Georges Bizet
\ttriangle{gray} Moon
\end{frame}

\begin{frame}{Packet P3 Question 39}
After this treaty was signed in the Jerónimos Monastery, its signatories took a ride in an electric tram  \tsquare{xred} together as a show of unity. A second referendum on this treaty was controversially held in Ireland, resulting in its acceptance after it was initially rejected by voters. This 2007 treaty set the maximum number of MEPs at 750 and created Article 50, which allows for the withdrawal process that Brexiteers seek to implement. For 10 points, name this treaty which amended the EU Constitution created in the Maastricht treaty, and which is named for the capital of Portugal. \tdiamond{gray}  \tcircle{gray}  \tsquare{gray}  \ttriangle{gray} 

\textbf{Answer}: Treaty\ of\ Lisbon\\
\tsquare{xred} Treaty of Nystad
\tdiamond{gray} Fontainebleau
\tcircle{gray} Maastricht Treaty
\tsquare{gray} Treaty of Nystad
\ttriangle{gray} Treaty of Versailles
\end{frame}

\begin{frame}{Packet P3 Question 40}
This building's piazza  \tsquare{xred} is defined by a colonnade of double Tuscan  \tdiamond{xyellow} columns that grow into an enormous elliptical circle. This building contains a reconstruction of  \tcircle{xgreen}  \tsquare{xyellow} Giotto's depiction of Christ walking on the water, the Navicella. Its piazza contains an Egyptian obelisk known as ``The Witness'' as well as a fountain designed by the creator of this building's facade, Carlo Maderno. Bramante drew the original design for this building, before it was modified by Michelangelo. Pope Urban  \ttriangle{xgreen} VIII hired Gian Bernini to complete, for 10 points, what massive church at the heart of the Vatican City?

\textbf{Answer}: St.\ Peter's\ Basilica\\
\tsquare{xred} Baptistery
\end{frame}

\begin{frame}{Packet P3 Question 41}
This instrument partly titles a piece whose third movement begins with the xylophone playing a rhythm based on the Fibonacci sequence. Gustav Holst used wind instruments, a female chorus, and this instrument in the score of ``Neptune, the Mystic.'' This instrument often plays the glockenspiel part in The Magic Flute since it has a similar sound. The third movement of the Nutcracker Suite begins with a solo for this instrument, and is titled ``Dance of the Sugar Plum Fairy.'' For 10 points, Bela Bartok wrote a piece for ``strings,  \tcircle{xred} percussion,''  \tdiamond{xgreen} and what keyboard instrument with a ``heavenly''  \tsquare{xgreen} sound? \tcircle{gray}  \ttriangle{gray} 

\textbf{Answer}: Celesta\\
\tcircle{xred} Harp
\tcircle{gray} Harp
\ttriangle{gray} Violin
\end{frame}

