\begin{frame}{Packet P4 Question 1}
The Boomerang Nebula is  \tsquare{xred} the closest natural place in the universe that approaches this concept. In a lab, sodium atoms at MIT were made to approach 0.1 nano of this concept. The Bose-Einstein condensate and superconductivity exist close to this  \hsquare{xgreen} level. The Rankine zero is another scale for this concept. This concept marks the point where the entropy of an ideal gas reaches its minimum level and thermodynamic temperature scale reaches its lower limit. For 10 points, name the lowest temperature possible. \hdiamond{xred}  \hcircle{xred}  \htriangle{xred} 

\textbf{Answer}: Absolute\ zero\\
\tsquare{xred} Orion Nebula
\hdiamond{xred} Third law of thermodynamics
\hcircle{xred} Knowledge
\htriangle{xred} Knowledge
\end{frame}

\begin{frame}{Packet P4 Question 2}
A character created by this author claims that he murdered a prostitute because she wanted his “lilac  \tcircle{xred} blossom.” A play by this author is set in a prison cell that is run by the convict Green-Eyes. The sounds  \hsquare{xgreen} of an alarm clock, a telephone, and a doorbell cause breaks in the action in a play by this man, in which one of the title characters tries to seduce the milkman Mario. This  \tdiamond{xgreen}  \tsquare{xred} author of Deathwatch wrote a play in which  \hcircle{xgreen} Claire and Solange plan to murder Madame using poisoned tea.  \ttriangle{xred} For 10 points, name this French playwright of The Maids.

\textbf{Answer}: Jean\ Genet\\
\tcircle{xred} Sleeping Beauty
\tsquare{xred} The Maids
\ttriangle{xred} The Maids
\end{frame}

\begin{frame}{Packet P4 Question 3}
A scholar working in this dynasty established the principles governing the camera obscura to describe the function of the human eye. This dynasty funded the construction of the first paper mill. During the rule of this dynasty, three brothers collectively known as the Banu Musa wrote the Book of Ingenious Devices while working at the House of Wisdom. The Barmakid family advised several  \tcircle{xgreen} rulers of this dynasty, including Harun Al-Rashid. For  \tsquare{xgreen}  \htriangle{xgreen} 10 points, name this third Islamic caliphate that established  \tdiamond{xgreen} a capital at Baghdad and that succeeded the Umayyads.

\textbf{Answer}: Abbasid\ Caliphate\\
\end{frame}

\begin{frame}{Packet P4 Question 4}
The production and trade of this commodity is governed by a set of three “flexible mechanisms” including the use of the CDM. William Nordhaus  \tcircle{xred} was one of the first economists to recommend the taxation of this commodity, which Justin Trudeau announced in October 2018 would begin in Canada at a rate of twenty dollars per ton. Many economists recommend placing a heavy Pigouvian tax on  \ttriangle{xred} this commodity, in line with recommendations made in the 2015 Paris Agreement. For 10 points, name this commodity, a gas believed to be responsible for global warming. \hdiamond{xred}  \hsquare{xred} 

\textbf{Answer}: Carbon\ dioxide\\
\tcircle{xred} Paul Samuelson
\ttriangle{xred} Ivory
\hdiamond{xred} Fish
\hsquare{xred} Kyoto Protocol
\end{frame}

\begin{frame}{Packet P4 Question 5}
An architect employed the motto “For everyone a garden” in designing an apartment complex in this city, all of whose units have access to rooftop plots. Saint Joseph’s Oratory is in this city, where Buckminster  \hsquare{xgreen} Fuller designed a geodesic dome on St. Helen’s Island for a U.S. pavilion that today serves as the Biosphere environmental  \tsquare{xred} museum. In this city, an apartment complex consisting of 354 prefabricated concrete forms was designed by Moshe Safdie. Habitat  \tcircle{xgreen} 67 was built for an Expo in, for 10 points, what most populous city of Quebec named  \tdiamond{xgreen} after Mount Royal? \htriangle{xred} 

\textbf{Answer}: Montreal\\
\tsquare{xred} Buckminster Fuller
\htriangle{xred} New York City
\end{frame}

\begin{frame}{Packet P4 Question 6}
Cheung and Klots use this  \tsquare{xred} datastructure to store intermediate computations in computing the CDF of the Mann-Whitney-Wilcoxon  \tcircle{xred} distribution.  This was the subject of the 1975 Turing Award and was first implemented at the RAND  \hdiamond{xgreen} corporation for the IPL language by Newell and Simon, and one is constructed using the ``cons'' command  \hcircle{xgreen}  \hsquare{xgreen} in LISP.  For 10 points, what is this basic datastructure that chains data items  \htriangle{xgreen} together with forward pointers?

\textbf{Answer}: Linked\ list\\
\tsquare{xred} Transaction cost
\tcircle{xred} Central processing unit
\end{frame}

\begin{frame}{Packet P4 Question 7}
To a third party, Einstein described this scientist as ``cold as a fish'' but offered the advice to ``stop reading that drivel''.  That drivel was news reports that this scientist was unworthy to shake the hand of the King of Sweeden because of a romantic relationship with Paul Langevin.  Baron de Rothschild built a laboratory for this scientist to process ore from Madagascar for use in sterilization vans.  Her work led to the discovery of Radium and Polonium, named  \tdiamond{xgreen}  \tcircle{xgreen}  \tsquare{xred} for her native Poland.  For 10 points,  \hsquare{xgreen} name this two-time Nobel winner who developed a theory of radioactivity with Becquerel and her husband,  \ttriangle{xgreen} Pierre.

\textbf{Answer}: Marie\ Curie\\
\tsquare{xred} Curie
\end{frame}

\begin{frame}{Packet P4 Question 8}
This is the only color  \tcircle{xred} of multiple pieces of paper in the middle portion of the cut-out The Snail. The nose and forehead of the subject of the 1905 painting Woman with a Hat are this color. This is the color of the tree trunk that dominates the left border of The Joy of Life. The bottom-most section of both versions of The Dance are this color. This color dominates the right background of a Fauvist portrait of the artist’s wife Amélie in which her face is divided by a vertical band of this color. For 10 points, name this color, a stripe of which titles an Henri Matisse painting. \hdiamond{xred}  \hsquare{xred}  \htriangle{xred} 

\textbf{Answer}: Green\\
\tcircle{xred} Gorilla
\hdiamond{xred} Green
\hsquare{xred} Blue
\htriangle{xred} Blue
\end{frame}

\begin{frame}{Packet P4 Question 9}
Connie Gersick applied this theory to six independent fields, originating its application to organizational transformations. Richard Dawkins discussed  \hcircle{xgreen} versions of this theory by analyzing the journey of the Israelites across the desert in the ninth chapter of The Blind Watchmaker. This theory builds upon  \tcircle{xred} Ernst Mayr’s theories of speciation,  \tsquare{xgreen} argues that periods of cladogenesis alternate  \tdiamond{xgreen} with periods of stasis, and is contrasted with phyletic gradualism. Niles  \ttriangle{xgreen} Eldredge and Stephen Jay Gould proposed, for 10 points, what theory predicting that evolution usually proceeds slowly but is interspersed by short bursts of rapid change?

\textbf{Answer}: Punctuated\ equilibrium\\
\tcircle{xred} Sociobiology
\end{frame}

\begin{frame}{Packet P4 Question 10}
The ``forked-line'' method, using multiplication rather than combination, is an alternative to this mechanism. Using this method, one can visualize the Hardy-Weinberg principle. The results of this method,  \tcircle{xred} created by a friend of Hardy, can be translated into ratios or percentages. However, this method will not give accurate results if the genes involved do not follow Mendel's laws of inheritance. This table-based method that uses the genetic traits of parents to predict the genetic traits of their children. For 10 points, name this method of predicting the results of--for example--breeding pea plants  \tsquare{xred} with purple versus white flowers and predicting how many offspring of each color will result. \hdiamond{xred}  \htriangle{xred} 

\textbf{Answer}: Punnett\ square\\
\tcircle{xred} Genetic drift
\tsquare{xred} Gregor Mendel
\hdiamond{xred} Gregor Mendel
\htriangle{xred} Chemotherapy
\end{frame}

\begin{frame}{Packet P4 Question 11}
This entity exists on  \tsquare{xred} each of the terrestrial planets, as well as at least 3 different moons. Most of them--including Earth's--are primarily composed of silicate rock, but Triton has  \tcircle{xred} one made of ice. The Kola Super Deep Borehole took 20 years to drill here. Subduction occurs when a tectonic plate of the Earth is pushed into this layer, which  \htriangle{xgreen} had upper, lower, and transition zones. For 10 points, name this layer of a planetary  \hcircle{xgreen} body that lies below the crust but  \tdiamond{xgreen}  \hsquare{xgreen} above the core, and is typically molten.

\textbf{Answer}: Mantle\ (geology)\\
\tsquare{xred} Anti-Life Equation
\tcircle{xred} Neptune
\end{frame}

\begin{frame}{Packet P4 Question 12}
In a story by this writer, a man recites Byron’s “So We'll Go No More a Roving” in honor of a group of characters who died of chickenpox. This author wrote a story in which William Stendhal kills off a group of government inspectors by reenacting the plots of Edgar Allan Poe’s stories. A Sara Teasdale poem provides the title of this man’s story in which an automated house prepares  \tcircle{xgreen}  \tsquare{xred} meals for a family who died in a nuclear blast. “--And the Moon Be Still as Bright,” “Usher II,” and  \ttriangle{xred} “There Will Come Soft Rains” are by,  \hdiamond{xgreen} for 10 points, what author of The Martian Chronicles?

\textbf{Answer}: Ray\ Bradbury\\
\tsquare{xred} The Martian Chronicles
\ttriangle{xred} The Martian Chronicles
\end{frame}

\begin{frame}{Packet P4 Question 13}
“A Minor Nation celebrates / It's unobtrusive Mass” in this author’s poem that begins “Further in Summer than the Birds.” The speaker of a poem by this author calls the flight of a bird a softer motion than oars dividing the ocean and observes the bird eating an “Angle Worm.” This author described a feeling seen in “the chillest land - / And on the strangest Sea” as “the little Bird / That kept so many warm.” This woman wrote the poems “A Bird, came down the Walk” and “Hope is the thing with feathers.” For 10 points,  \tdiamond{xgreen} name this reclusive poet who called Amherst,  \ttriangle{xgreen} Massachusetts  \tcircle{xgreen}  \tsquare{xgreen} her home.

\textbf{Answer}: Emily\ Dickinson\\
\end{frame}

\begin{frame}{Packet P4 Question 14}
This character describes an owl as a “fatal bellman, / Which gives the stern'st good-night.” This character’s final spoken lines, including the statement “What's done cannot be undone,” are unusually written in prose rather than in verse. This character urges spirits to fill her with “direst cruelty”  \hdiamond{xgreen} and ``unsex me now'' as  \tcircle{xgreen} she wipes bloody knives onto the clothes of some sleeping servants. This character  \ttriangle{xgreen} says that “all the / perfumes of Arabia will not sweeten this little / hand” in her sleepwalking scene. For 10 points,  \tsquare{xgreen} name this spouse of a Scottish nobleman in a William Shakespeare play.

\textbf{Answer}: Lady\ Macbeth\\
\end{frame}

\begin{frame}{Packet P4 Question 15}
A stanza of this poem compares the successes of “Worldly Hope” to “Snow upon the Desert's dusty Face.” The pen name of H.H. Munro comes from this poem, which inspired  \tcircle{xred} the title of Eugene O’Neill’s only comedy. A mystic in this poem asks “Who is the Potter, pray,  \hcircle{xgreen} and who the Pot?” This  \hdiamond{xgreen} poem states that “Wilderness were Paradise enow” if the speaker could have “A Book of Verses underneath the Bough, / A Jug of Wine, a Loaf  \tsquare{xgreen} of Bread- and Thou.”  \ttriangle{xgreen} Edward FitzGerald translated the quatrains of, for 10 points, what poem by Omar Khayyam?

\textbf{Answer}: Rubaiyat\ of\ Omar\ Khayyam\\
\tcircle{xred} Meghadūta
\end{frame}

\begin{frame}{Packet P4 Question 16}
His use of the letter ``P'' led to some confusion, but he later explained that he meant it to be a portmanteau, ``prolaag'', in  \tcircle{xred} contrast to V, which stood for ``increase'' in his paper ``Cooperating sequential processes'', which introduced the semaphore framework.  He developed the shunting-yard algorithm for  \ttriangle{xgreen} evaluating infix notation and originated  \hcircle{xgreen} the phrase “considered harmful” in his notorious hate for the “GOTO” statement.  \tsquare{xgreen} He created an algorithm that is the basis for the A-star algorithm  \tdiamond{xgreen} and that can fail when the edge weights of its input graph are negative. For 10 points, what Dutch computer scientist formulated a namesake shortest path algorithm?

\textbf{Answer}: Edsger\ W.\ Dijkstra\\
\tcircle{xred} Rob Roy (novel)
\end{frame}

\begin{frame}{Packet P4 Question 17}
This man, who disagreed with his student Lucy Mair by arguing against the reconstruction of past native cultures, once defined culture as a “well organized unity” consisting of “a body of artifacts and a system of customs.” This man described a ritual in which red shell necklaces were  \tcircle{xgreen} traded for white shell armbands. He  \tsquare{xgreen} discussed the use of spells in agriculture in Coral Gardens  \tdiamond{xgreen}  \ttriangle{xgreen} and Their Magic and explained the role of the Kula Ring exchange among the Trobriand Islanders. For 10 points, what Polish anthropologist wrote Argonauts of the Western Pacific?

\textbf{Answer}: Bronisław\ Malinowski\\
\end{frame}

\begin{frame}{Packet P4 Question 18}
In a test in this city, Gabriel offered a prophet a choice between drinking water, wine, or milk, and the prophet’s instincts correctly led him to drink the milk. The Al-Qibli Chapel is in this city, which is held to be the location of the “farthest mosque” in Sura 17 of the Qur’an. Muhammad traveled  \tcircle{xgreen} on the steed Buraq to this city, where he undertook the Isra and the Mi'raj. The Al-Aqsa Mosque and  \tsquare{xred} the Dome of the Rock  \ttriangle{xgreen} commemorate Muhammad’s  \tdiamond{xgreen} Night Journey to this city. For 10 points, name this city where those religious  \hsquare{xgreen} buildings were constructed on the Temple Mount.

\textbf{Answer}: Jerusalem\\
\tsquare{xred} Buraq
\end{frame}

\begin{frame}{Packet P4 Question 19}
Members of this denomination celebrate a dinner  \tsquare{xred} near Easter where they prepare but do not eat bread and  \tcircle{xred} wine called the Lord’s Evening Meal, and they believe that Jesus was killed upon a stake instead of a cross. This denomination, whose members believe that exactly  \hsquare{xgreen} 140,000 people are anointed, gather for worship in Kingdom Halls. This denomination  \hcircle{xgreen} distributes evangelical magazines such as The Watchtower and Awake! Charles Taze Russell founded,  \tdiamond{xgreen}  \htriangle{xgreen} for 10 points, what Christian denomination whose members preach door-to door?

\textbf{Answer}: Jehovah's\ Witnesses\\
\tsquare{xred} United Methodist Church
\tcircle{xred} Shia Islam
\end{frame}

\begin{frame}{Packet P4 Question 20}
For over ten years, the cornetist Charles “Buddy” Bolden led a  \tcircle{xred} successful band based  \hsquare{xgreen} in this city, which was where “Kid” Ory gave performances out of the Economy Hall. Fate Marable led a band out of this city that performed on boats such as the Sidney and the Capitol. Before moving to Chicago, King Oliver was based out of  \tsquare{xred} this city, which was  \tdiamond{xgreen} also the birthplace of the performer of the “Jelly Roll Blues,” the pianist Jelly Roll Morton. For 10 points, name this birthplace of Louis Armstrong where many Creole and Dixieland  \hcircle{xgreen} bands were formed in the Jazz Age. \htriangle{xred} 

\textbf{Answer}: New\ Orleans\\
\tcircle{xred} Michael Ondaatje
\tsquare{xred} Louis Armstrong
\htriangle{xred} New York City
\end{frame}

\begin{frame}{Packet P4 Question 21}
Tourist sites in this region include a park that memorializes the Battle of Wilson’s Creek and the Crystal Bridges Art Museum. This region was once known for its lead and zinc mining in the vicinity of  \tcircle{xred} Joplin. Buffalo Lookout is the highest point  \hcircle{xgreen} in this region, which contains the Boston Mountains and  \tsquare{xred} the St. Francois Mountains.  \hsquare{xgreen} This region  \hdiamond{xgreen} contains the headquarters of Wal-Mart in the city of Bentonville and is found to the immediate southwest of St. Louis. For 10 points, name this hilly region of southern Missouri and northern Arkansas. \htriangle{xred} 

\textbf{Answer}: Ozarks\\
\tcircle{xred} Yukon
\tsquare{xred} Black Hills
\htriangle{xred} Brittany
\end{frame}

\begin{frame}{Packet P4 Question 22}
These objects are the main subject of Vasily Vereshchagin’s painting  \tcircle{xgreen} The Apotheosis of War. A photograph by Philippe Halsman shows Salvador Dali standing in front of one of these objects formed from the bodies of seven nude women. The subtitle “Red, White, and Blue” is appended to a Georgia O’Keefe painting of one of these objects that originally belonged to a cow. An anamorphic one of these objects is stretched across the floor of Hans Holbein’s The Ambassadors. For 10 points,  \tsquare{xgreen}  \ttriangle{xgreen} name these objects often used as a vanitas  \tdiamond{xgreen} symbol of death.

\textbf{Answer}: Skull\\
\end{frame}

\begin{frame}{Packet P4 Question 23}
Roe created a characterization  \tsquare{xred} of this function from a series of functions with constraints  \hcircle{xgreen} on their derivatives and antiderivates.  Shirali showed that a seventh-century approximation of it by Bhaskara-Aryabhata was better than approximations derived using modern methods.  Its first through third derivatives at zero are one, zero, and negative one, making a series approximation easy to derive.  With a range between negative one and one, for ten points name this trigonometric function  \hdiamond{xgreen} whose derivative  \ttriangle{xgreen} is cosine.

\textbf{Answer}: Sine\\
\tsquare{xred} Abortion
\end{frame}

\begin{frame}{Packet P4 Question 24}
The main character of this novel dreams of a cursed man who once cut out his cousin's heart after he falls asleep in a cave. This novel's protagonist wears his name on his back during a parade, and then talks to a massive brass head that is actually manned by a servant in an adjacent room in Barcelona. After losing a duel to the Knight of the White Moon, the title  \hdiamond{xgreen} character of this novel is forced to give up his adventures for the span of a year. The fictional heroine Dulcinea  \tcircle{xgreen}  \tsquare{xgreen}  \ttriangle{xgreen} and Sancho Panza appear in, for 10 points, what novel about a nobleman addicted to chivalry by Miguel de Cervantes?

\textbf{Answer}: Don\ Quixote\\
\end{frame}

\begin{frame}{Packet P4 Question 25}
In a novel by this author, two people wish that they had been born on a bus, believing that they would then have gotten free bus fares for life. This author first achieved fame when she accused the director of the film Bandit Queen of glorifying rape. A character created by this writer is ashamed when a group of communists force her to wave a red flag. She wrote a novel in which Sophie drowns when a  \tdiamond{xred} boat capsizes, leading to the death of the untouchable Velutha and causing haunting memories for the  \tsquare{xred} twins Rahul and Estha. For 10 points, name this Indian author of The God of Small Things. \htriangle{xred}  \hcircle{xred} 

\textbf{Answer}: Arundhati\ Roy\\
\tdiamond{xred} Thomas Hardy
\tsquare{xred} The God of Small Things
\htriangle{xred} Arundhati Roy
\hcircle{xred} Water on Mars
\end{frame}

\begin{frame}{Packet P4 Question 26}
As aspect of this deity was an axe-wielding  \hdiamond{xgreen} man who killed a king and his many warriors to reclaim a wish-granting cow that had been stolen from his father. An aspect of this god killed a demon at the exact transition between day and night and had the head of a lion, but the body of a human. This deity took the form of a turtle to support a mountain during the churning of the cosmic ocean. Dashavatara,  \hsquare{xgreen} Parashurama, and Kurma are aspects of,  \tsquare{xred} for 10 points, what Hindu preserver god  \tcircle{xgreen}  \ttriangle{xgreen} who was married to Lakshmi and had ten avatars?

\textbf{Answer}: Vishnu\\
\tsquare{xred} Dashavatara
\end{frame}

\begin{frame}{Packet P4 Question 27}
In the U.K., participants in this situation are subject to the RPI-X rule. Values approaching one for  \tcircle{xred} the Lerner index characterize  \hdiamond{xgreen}  \hcircle{xgreen} this situation. The Coase conjecture predicts the price in this situation across an infinite time horizon. The ``natural'' form of this situation is characterized by high barriers  \tsquare{xgreen} to entry and by economies of scale. In this situation, the quantity is determined by taking the marginal revenue equal to marginal cost, leading to a higher profit and price  \ttriangle{xgreen} than in perfect competition. For 10 points, name this situation in which one company is the sole provider of a commodity.

\textbf{Answer}: Monopoly\\
\tcircle{xred} Information asymmetry
\end{frame}

\begin{frame}{Packet P4 Question 28}
This artist's first project of 2015 was a surprise album that spawned the platinum single ``Energy'' and preceded a collaborative mixtape with Atlanta artist Future. A track on a 2018 album by this artist acknowledged that he had secretly fathered a son, Adonis, a  \tcircle{xred} topic that was first revealed by fellow rapper and rival Pusha-T.  \tsquare{xred} A 2016 song by this man includes the lyrics, ``You used to call me on my cell phone / Late night when you need my  \ttriangle{xred} love.'' For 10 points, name this Canadian rapper behind the albums  \hdiamond{xgreen} Scorpion and If You're Reading This It's Too Late as well as the hit single ``Hotline Bling.''

\textbf{Answer}: Drake\ (musician)\\
\tcircle{xred} John Coltrane
\tsquare{xred} Lil Wayne
\ttriangle{xred} T.I.
\end{frame}

\begin{frame}{Packet P4 Question 29}
Barack Obama claimed that  \tsquare{xred} this event would send its country to the ``back of the queue.'' Stephen Barclay and David Davis have both served as ``secretary of state'' for negotiations related to this event, which created the rejected ``Chequers Plan''  \tcircle{xred} and will likely involve a ``Divorce Bill'' mandating payments of about fifty billion euros. Following this event, David Cameron resigned as prime minister, and  \hdiamond{xgreen} he was replaced by Theresa May. For 10 points, name this event in which an island nation elected to leave a multinational organization. \htriangle{xred} 

\textbf{Answer}: Brexit\\
\tsquare{xred} Rick Warren
\tcircle{xred} German reunification
\htriangle{xred} Great Famine (Ireland)
\end{frame}

\begin{frame}{Packet P4 Question 30}
A friend nicknamed ``Uncle Nate'' once aided this athlete. This player was released after rumors surfaced that he partied in Las Vegas while under the concussion protocol. As a college freshman, this player led his team to a win over Oklahoma in  \tcircle{xred} the Cotton Bowl on route to winning the Heisman Triophy. In July 2018, this player was traded to the CFL's Montreal Alouettes after being stuck behind Jeremiah Masoli on the Hamilton Tiger-Cats. He was drafted in the 2014 NFL and MLB drafts out of Texas A\&M. For 10 points, name this troubled former Cleveland Browns  \tsquare{xgreen} quarterback. \hdiamond{xred}  \htriangle{xred} 

\textbf{Answer}: Johnny\ Manziel\\
\tcircle{xred} LeBron James
\hdiamond{xred} Darren McFadden
\htriangle{xred} Dwight Howard
\end{frame}

\begin{frame}{Packet P4 Question 31}
Thomas Ferry cited a lack of constitutional direction in his decision not to cast an executive vote in this election. In this  \htriangle{xgreen} election, Oregon governor La Fayette  \tcircle{xgreen} Grover tried to rule one of his state's electors ineligble. According to legend, the wife of this election's winner refused to serve alcohol in the White House, leading to her nickname ``Lemonade Lucy.'' This election was marred by accusations of voter fraud in  \tsquare{xgreen} Louisiana, Florida, and South Carolina. Reconstruction was  \tdiamond{xgreen} ended by, for 10 points, what U.S. presidential election in which Rutherford Hayes defeated Samuel Tilden?

\textbf{Answer}: United\ States\ presidential\ election,\ 1876\\
\end{frame}

\begin{frame}{Packet P4 Question 32}
This man called a pact  \tsquare{xred} partly named for Lord Irwin a ``humiliating spectacle,'' contributing to his permanent break from Stanley Baldwin. This man wrote about his posting as a journalist with a unit that fought against Mohmand rebels in his book The Story of the Malakind Field Force. This man's war cabinet  \htriangle{xgreen} prioritized shipping and food distribution  \hcircle{xgreen} for British soldiers, contributing to a 20th-Century Bengal Famine. For 10 points, name this two-time British prime minister whose sparring with Mahatma Gandhi may have contributed to his landslide loss in the 1945 general election. \hdiamond{xred} 

\textbf{Answer}: Winston\ Churchill\\
\tsquare{xred} Kellyanne Conway
\hdiamond{xred} Neville Chamberlain
\end{frame}

\begin{frame}{Packet P4 Question 33}
A movie about the lives of the perpetrators of this event was controversially banned in its country prior to its 2014 release and is called Gems of the Community, or Kaum De Heere. This event's target was en route to an interview with the actor Peter Ustinov. Secretary R.K. Dhawan was cleared of complicity in this event. It was an act of revenge for Operation Blue Star, which destroyed parts of a temple in Amritsar. Sikhism  \tdiamond{xgreen}  \tsquare{xgreen} adherents Satwant Singh and Beant  \tcircle{xgreen} Singh fired 33 fatal  \ttriangle{xgreen} shots in, for 10 points, what event that resulted in the death of a female Indian prime minister?

\textbf{Answer}: Assassination\ of\ Indira\ Gandhi\\
\end{frame}

\begin{frame}{Packet P4 Question 34}
This artist showed serpents crawling around the exterior of a dead man's visage, with the image of the visage repeated in its mouth and eye sockets. This artist of The Face of War created a painting in which a stone hand grasps an egg from which emerges a flower, echoing a figure to the left who stares into a pool. A swarm of ants appear on  \tsquare{xgreen} an orange surface in a painting by this  \tcircle{xgreen} artist of The Metamorposhis of Narcissus. The Catalan coast appears in the background of this artist's painting of melting clocks. For 10 points,  \tdiamond{xgreen} name this surrealist painter of The  \ttriangle{xgreen} Persistence of Memory.

\textbf{Answer}: Salvador\ Dalí\\
\end{frame}

\begin{frame}{Packet P4 Question 35}
In a concerto, this composer called for the strings to strum four-note chords in imitation of banjos in the ``piu mosso'' from the second-movement andante; that concerto by this man opens with four tympani strokes, a cymbal clash, a bass drum thud, and a snare drum roll, all followed by a ``Charleston'' motif.  Walter Damrosch conducted the premiere of a piece by this composer that uses four taxi horns.  \tdiamond{xgreen}  \tcircle{xgreen} This composer of the Concerto in F wrote a jazz-influenced piece that opens with a clarinet glissando.  \tsquare{xgreen} For 10 points, name  \ttriangle{xgreen} this composer of An American in Paris and Rhapsody in Blue.

\textbf{Answer}: George\ Gershwin\\
\end{frame}

\begin{frame}{Packet P4 Question 36}
In a song from this musical, interjections of ``no'' and ``terrible'' are interspersed between a gossip chain that ends with a character affirming cases of the measles and the mumps. ``The Rumor'' appears in  \hsquare{xgreen} this musical, whose main character fakes having a nightmare in which the ghost of his grandmother gives  \tsquare{xred} a dire warning. Two parents sing about how their daughter has grown up on her wedding day in this musical's song ``Sunrise, Sunset.'' ``Tradition'' and ``If I Were  \hdiamond{xgreen} a Rich Man'' appear near the start of, for 10 points, what musical set in Anatevka about the family of the Jewish milkman Tevye? \hcircle{xred}  \htriangle{xred} 

\textbf{Answer}: Fiddler\ on\ the\ Roof\\
\tsquare{xred} Wicked (musical)
\hcircle{xred} Into the Woods
\htriangle{xred} West Side Story
\end{frame}

\begin{frame}{Packet P4 Question 37}
In a novel partly titled  \tsquare{xred} for these beings, a woman demonstrates the strength of her hands by balancing herself on a single fingertip and then walking around on her fingers. A group of women form the “Pentagram of Death” to ward off these beings, who are often referred to as the “sorry stricken” or the “unmentionables.” These beings kill 18 people in Netherfield Park in a 2009 novel that tells of how Charlotte Lucas gradually turns into one of them. For 10 points, name these beings that Seth Grahame-Smith added to a horror mashup of Pride and Prejudice. \hdiamond{xred}  \hcircle{xred}  \htriangle{xred} 

\textbf{Answer}: Zombie\\
\tsquare{xred} Lightness
\hdiamond{xred} Zombie
\hcircle{xred} Fairy
\htriangle{xred} Amesha Spenta
\end{frame}

\begin{frame}{Packet P4 Question 38}
Olaf I used one of these  \tsquare{xred} animals to execute Raud the Strong. One of these animals was baited using the  \tcircle{xred} head of a pack animal nicknamed “the heaven breaker.” Utgard-Loki disguised one of these animals as a cat, rendering Thor unable to lift the feline from the ground. A liquid secreted by one of these animals drips onto Loki’s face as part of his eternal punishment. Thor used the head of one of Hymir’s oxen to bait one of these animals from the ocean. For 10 points, name these animals, one of which named Jormungandr encircles the world in Norse myth. \hdiamond{xred}  \htriangle{xred} 

\textbf{Answer}: Snake\\
\tsquare{xred} Heimskringla
\tcircle{xred} Tiger
\hdiamond{xred} Goat
\htriangle{xred} Horse
\end{frame}

\begin{frame}{Packet P4 Question 39}
Tristan de Luna y Arellano founded a colony in this state whose site was thought to be lost until its 2015 rediscovery. Jean Ribault’s men were massacred by Spanish forces in the state near the short-lived French colony at Fort Caroline. This state, whose fishing grounds are the homeland of the Calusa and Tequesta native  \tsquare{xred} peoples, was first governed by Pedro Menendez de Aviles. The goal of the ill-fated Narvaez Expedition was to establish garrisons in this state. For 10 points, name this state where Ponce de Leon supposedly sought the Fountain of Youth. \hdiamond{xred}  \hcircle{xred}  \htriangle{xred} 

\textbf{Answer}: Florida\\
\tsquare{xred} Spanish Florida
\hdiamond{xred} Florida
\hcircle{xred} Texas
\htriangle{xred} Pennsylvania
\end{frame}

\begin{frame}{Packet P4 Question 40}
As a state governor, this  \tsquare{xred} future president reformed primary voting practices through the Geran Bill and pushed through workers’ protection measures in a foreshadow of his attacks on what he termed the “Triple Wall of Privilege.” This man feuded with Andrew Fleming West over the placement of a graduate school as a university president. He beat out Champ Clark for the Democratic nomination after serving as the president of Princeton and the governor of New Jersey. For 10 points, name this president  \tdiamond{xgreen}  \hcircle{xgreen}  \htriangle{xgreen} who won the Election of 1912 and who led the U.S. during World War One.

\textbf{Answer}: Woodrow\ Wilson\\
\tsquare{xred} Indiana
\end{frame}

\begin{frame}{Packet P4 Question 41}
The first three Acts of Uniformity laid out the mandatory use of this text, which set dress codes through the Ornaments Rubric. The Battle of Clyst Heath relieved a siege of Exeter in a rebellion named  \htriangle{xgreen} for this text, which included a defeat of Cornish upstarts in the Battle of Sampford  \tdiamond{xgreen} Courtenay. The  \tsquare{xgreen} Thirty Nine Articles were incorporated into this text, which  \tcircle{xgreen} was developed by Thomas Cranmer during the rule of king Edward VI but then set aside during the Catholic rule of Mary I. For 10 points, name this text that provides words of worship in Anglican services.

\textbf{Answer}: Book\ of\ Common\ Prayer\\
\end{frame}

