\begin{frame}{Packet P5 Question 1}
A generic, non-patented  \tsquare{xred} relative of this substance developed by Paul Schlack requires a ring-opening polymerization of six carbon Caprolactam  \tsquare{xyellow} molecules. This substance’s patented “6-6” type refers to the six carbons in the adipic acid and hexamethylenediamine  \tcircle{xred} used in its synthesis, originally by Wallace Carouthers at DuPont. The US Government  \tcircle{xyellow} diverted production of this material to make tents and parachutes in the second  \tdiamond{xgreen} World War. For 10 points name this synthetic material made from polyamides also used to make women’s stockings. \ttriangle{gray} 

\textbf{Answer}: Nylon\\
\tsquare{xred} Mifepristone
\tcircle{xred} Cyclohexane
\ttriangle{gray} Glass
\end{frame}

\begin{frame}{Packet P5 Question 2}
He chaired a parliament  \tsquare{xred} select committee that declared in 1772 that Robert Clive's Plassey fortune was illegally obtained. To celebrate the marriage of his friend Lord Stanley in 1774, he wrote a play about a shepherdess who turns out to be the Lady Bab Lardoon in the Maid of the Oaks.  He led the victorious  \tdiamond{xyellow}  \tsquare{xyellow}  \ttriangle{xgreen} British forces at the battle of Alcantara  in support of Portugal in the Seven Years' War.  During the Revolutionary War, he led a force from Canada to split the colonies but was defeated by Horatio Gates.  For ten points, name this British general who lost an early, crucial 1777 battle at Saratoga. \tcircle{xgreen} 

\textbf{Answer}: John\ Burgoyne\\
\tsquare{xred} United States House Committee on Ways and Means
\end{frame}

\begin{frame}{Packet P5 Question 3}
His name is associated  \tsquare{xred} with a Northern Irish group formed by former members of Torgas Valley Reds.  This man’s “optimism fell at the first hurdle” in ``Waiting for the Great Leap Forward'' by Billy Bragg.  \ttriangle{xred} This man seduces his wife by performing a Baudelaire poem and asks “three person’d God” to “Batter My Heart” in his act-closing aria adapted from John Donne. Like Richard Nixon and Leon Klinghoffer, John Adams wrote him as a baritone. For 10 points, what title character of Doctor Atomic organizes the  \tdiamond{xyellow} 1945 Trinity test? \tcircle{xgreen}  \tsquare{gray}  \ttriangle{gray} 

\textbf{Answer}: J.\ Robert\ Oppenheimer\\
\tsquare{xred} Harlan F. Stone
\ttriangle{xred} Mao Zedong
\tsquare{gray} Harlan F. Stone
\ttriangle{gray} Mao Zedong
\end{frame}

\begin{frame}{Packet P5 Question 4}
Bradley Bailey speculated  \tsquare{xred} that the odd number of birds in this artist's Manchurian Cranes may be a commentary on monogamy, and his 1812 ``A Quick Guide to Painting'' focused on finding geometric forms in the visible world.   In 1817, he drew a temple on an 18 meter sheet of paper.  When he had a falling out with a novelist collaborator, Takizawa Bakin, the publisher opted to keep him rather than the novelist.  His Fine Wind, Clear Morning from  \tdiamond{xyellow} his thirty-six views of Mount Fuji helped  \tsquare{xyellow}  \ttriangle{xred} cement his reputation.  For ten points, name this Japense artist of The Grate Wave off Kanagawa. \tcircle{gray}  \ttriangle{xgreen} 

\textbf{Answer}: Hokusai\\
\tsquare{xred} It's a Wonderful Life
\ttriangle{xred} The Great Wave off Kanagawa
\tcircle{gray} Color
\end{frame}

\begin{frame}{Packet P5 Question 5}
This organ primarily derives  \tdiamond{xyellow} from the endoderm, specifically the ventral side. However, certain cells from the neural crest eventually migrate into this organ and give rise to its characteristic colors. Elevated levels of corticosteroids have been implicated in striae development in this organ. When this  \tsquare{xred} organ repairs itself with an overgrowth of granulation tissues, keloids may develop from excessive collagen. The linea nigra that often develops in pregnant women comes from placental hormones that stimulate melanocytes in this organ. For 10 points what organ in humans is covered in hair follicles and is composed of  \tsquare{xyellow} the dermis and epidermis? \tcircle{xgreen}  \ttriangle{gray} 

\textbf{Answer}: Skin\\
\tsquare{xred} Somite
\ttriangle{gray} Liver
\end{frame}

\begin{frame}{Packet P5 Question 6}
A 1920 address entitled  \tsquare{xred} ``This and the Theory of Relativity'' claimed that its only mechanical quality under Lorentz, its immobility, had been lost. The Jefferson Lab at Harvard was built  \tcircle{xred} without iron nails to undertake the measurements of it postulated by Maxwell. In Cleveland, an experiment to understand it tested whether two light beams interfered with each other after passing through a half-silvered mirror and bouncing  \ttriangle{xred} back; this material was famously disproven with the null results of that 1887 experiment. For 10 points the Michelson-Morley  \tdiamond{xyellow} experiment cast  \tdiamond{xred}  \ttriangle{xyellow} doubt on the existance of what hypothesized medium through  \tsquare{xyellow} which light traveled? \tcircle{gray} 

\textbf{Answer}: Luminiferous\ aether\\
\tsquare{xred} Lincoln Memorial
\tcircle{xred} Willard Van Orman Quine
\ttriangle{xred} Michelson–Morley experiment
\tdiamond{xred} Interferometry
\tcircle{gray} Willard Van Orman Quine
\end{frame}

\begin{frame}{Packet P5 Question 7}
It’s not sulfur, but a solid, dark red allotrope of this element  \ttriangle{xyellow} is made by pressurizing  \tdiamond{xyellow} it into the epsilon phase, which yields an eight-atom molecular lattice.  \tcircle{xgreen} In another allotropic form, two of atoms of this element can temporarily exist in a singlet form where all electrons are spin paired. In yet  \tsquare{xgreen} another allotropic form, three elements of this atom can combine to form a potent greenhouse gas with a pungent odor. The Space Shuttle main engine combined liquid hydrogen with a liquid form of this element. For 10 points what gaseous element, with atomic number 8, is a byproduct of photosynthesis?

\textbf{Answer}: Oxygen\\
\end{frame}

\begin{frame}{Packet P5 Question 8}
The clustering of viola  \tsquare{xred} tricolor was an application of a process with this name by Svedberg. Conway and Maxwell adapted the distribution with this name to model overdispertion and underdispersion. The distribution with this name has a single mode if its parameter lambda is not an integer but two modes  \tcircle{xred} if it is and for large lambda can be well approximated by a normal distribution with mean lambda and variance lambda.   \ttriangle{xred} For 10 points, what French statistician lends his name to a discrete probability distribution used to calculate the number of independent events occurring in a fixed interval at a constant rate? \tdiamond{gray}  \tcircle{gray}  \tsquare{gray}  \ttriangle{gray} 

\textbf{Answer}: Siméon\ Denis\ Poisson\\
\tsquare{xred} Small-world network
\tcircle{xred} Poisson distribution
\ttriangle{xred} Poisson distribution
\tdiamond{gray} Poisson distribution
\tcircle{gray} Poisson distribution
\tsquare{gray} Small-world network
\ttriangle{gray} Poisson distribution
\end{frame}

\begin{frame}{Packet P5 Question 9}
In computational linguistics,  \tsquare{xred} ``projective'' sentences refer to dependency parses that have this property.  Scheinerman's theorem states that every graph with this property is the intersection graph of line  \tcircle{xred} segments.  Fáry's theorem says that graphs with this property can also be drawn with straight line  \tsquare{xyellow} segments.  Kuratowski's theorem states that a graph has this poperty if and only if it does not contain a minor or subgraph isomorphic to K3,3 or K5.  For ten points, name this property of graph theory describing graphs that can be drawn  \ttriangle{xred} without overlapping lines.  \tdiamond{gray}  \tcircle{gray}  \ttriangle{gray} 

\textbf{Answer}: Planar\ graph\\
\tsquare{xred} Stephen Wolfram
\tcircle{xred} Differentiable function
\ttriangle{xred} Planarity
\tdiamond{gray} Planarity
\tcircle{gray} Differentiable function
\ttriangle{gray} Planarity
\end{frame}

\begin{frame}{Packet P5 Question 10}
In issue No. 364, this character ``croaks'' ... in that he is turned into a frog. He visits a doctor at 177A Bleecker Street in New York and is given a cup of tea that transforms into a beer stein that continually refills itself. This character falls through a wormhole and arrives in New Mexico where he meets Darcy Lewis and Dr. Erik Selvig after being exiled from his homeworld of Asgard. For 10 points what Avenger played by Chris Hemsworth wields the hammer Mjolnir? \tdiamond{gray}  \tcircle{gray}  \tsquare{xgreen}  \ttriangle{xgreen} 

\textbf{Answer}: Thor\ (Marvel\ Comics)\\
\tdiamond{gray} Thor
\tcircle{gray} Mass spectrometry
\end{frame}

\begin{frame}{Packet P5 Question 11}
A 1984 song by this band references the fictional revolutionary group La Luna and the Eventide synthesizer. This band commissioned artist Patrick Nagel for one album cover and repeats “please, please tell me now” in another of their songs. This band references dancing through fire in both their title song to Roger Moore’s final James Bond movie and “New Moon on  \tdiamond{xyellow}  \tsquare{xgreen} Monday.” This band’s classic lineup includes three unrelated members surnamed Taylor along with Nick Rhodes and Simon LeBon. For 10 points what band performs songs like “Rio” and “Hungry Like the Wolf”? \tcircle{gray}  \ttriangle{gray} 

\textbf{Answer}: Duran\ Duran\\
\tcircle{gray} Arcade Fire
\ttriangle{gray} Weezer
\end{frame}

\begin{frame}{Packet P5 Question 12}
A composer from this country included a chorus singing “Dear Lord  \tdiamond{xyellow} and Father of Mankind” in his “Elegy for Dunkirk.” Henry Mancini rearranged a song by a composer from this country into the song “A Time for Us.” A composer from this country wrote the score for Atonement. The “Love Theme” from 1969’s Romeo and Juliet is by  \tsquare{xyellow} a composer from this country, as is “The Ecstasy of Gold,”  \tcircle{xyellow} which plays as Eli Wallach runs through a cemetery in The Good, The Bad and the Ugly. For 10 points,  \ttriangle{xyellow} name this birthplace of Dario Marianelli, Nino Rota, and Ennio Morricone.

\textbf{Answer}: Italy\\
\end{frame}

\begin{frame}{Packet P5 Question 13}
Thomas Edison patronized  \tsquare{xred} a prototype of these machines called the Mauch Chunk. Layers of laminated wood are retrofitted with steel in the ``i''-box technique developed by Rocky Mountain Construction for these machines. Stress-minimizing innovations to these machines included the introduction of clothoid loops and moving the axis of rotation to chest level in the heartline roll configuration. Arrow Dynamics introduced tubular steel to these machines in a prototype installed at Disneyland known as the  \ttriangle{xred} Matterhorn. Lift hills and loops are often features of, for 10 points, what amusement park attractions? \tdiamond{xgreen}  \tcircle{gray}  \tsquare{xgreen}  \ttriangle{gray} 

\textbf{Answer}: Roller\ coaster\\
\tsquare{xred} General Electric Company
\ttriangle{xred} Autoclave
\tcircle{gray} Loom
\ttriangle{gray} Autoclave
\end{frame}

\begin{frame}{Packet P5 Question 14}
The Generalized Method of Moments was developed at this university by Lars Peter Hansen. A scholar at this university, Eugene Fama, co-developed the three-factor model in asset pricing  \tcircle{xyellow} with Kenneth French. A scholar joined the faculty of this university in 1964, four years after publishing his controversial  \tsquare{xred} paper “The Problem of Social Cost.” A longtime researcher at this university espoused monetarism and wrote the book Capitalism and Freedom. Ronald Coase  \tdiamond{xyellow} and Milton Friedman worked at, for 10 points, what midwestern university that names a ``freshwater'' school of economics? \tsquare{gray}  \ttriangle{gray} 

\textbf{Answer}: University\ of\ Chicago\\
\tsquare{xred} Robert J. Shiller
\tsquare{gray} Robert J. Shiller
\ttriangle{gray} University of Texas at Austin
\end{frame}

\begin{frame}{Packet P5 Question 15}
“High-Quality Supportive Environments” and “Nurturing and Responsive Relationships” are two of the key components at the bottom of a childhood educational model named for this type of object. When paired with ``population,''  \ttriangle{xred} this type of object provides the usual name of an age-sex graph. This type of object names a pseudoscientific nutritional model created by the USDA. In a model first published as “A Theory of Human Motivation,” this is the shape of a diagram in which “self-actualization” appears at the apex. For 10 points, name this shape of Abraham Maslow’s  \tdiamond{xred} hierarchy of needs. \tdiamond{gray}  \tcircle{gray}  \tsquare{gray}  \ttriangle{gray} 

\textbf{Answer}: Pyramid\\
\ttriangle{xred} Veil
\tdiamond{xred} Maslow's hierarchy of needs
\tdiamond{gray} Maslow's hierarchy of needs
\tcircle{gray} Maslow's hierarchy of needs
\tsquare{gray} Abraham Maslow
\ttriangle{gray} Veil
\end{frame}

\begin{frame}{Packet P5 Question 16}
This man discussed how India was divided along  \ttriangle{xred} linguistic lines by the British in an essay about ``Primordial  \tcircle{xred} Sentiments and Civil Politics in the New States,'' “Integrative Revolution.” This man discussed the term ``lek,'' which is often misrepresented as ``shame,'' in his chapter ``Person Time and Conduct in Bali.'' This man described viewing an illegal sporting event with his wife in  \tcircle{xyellow} an essay titled after Jeremy Bentham's term for an extremely high-stakes game. For 10 points, name this anthropologist who  \tdiamond{xgreen}  \tsquare{xgreen} wrote ``Deep Play''  \ttriangle{xyellow} and The Interpretation of Cultures.

\textbf{Answer}: Clifford\ Geertz\\
\ttriangle{xred} Ernst Kapp
\tcircle{xred} Octavio Paz
\end{frame}

\begin{frame}{Packet P5 Question 17}
This character asks another if he would lie about the answer to three times seven hudred to an ignorant man. This character promises that, if he should be fined thirty minae, then Apollodorus will guarantee he pays his debt. He relates that he is the smartest man in the world because he is aware of what  \tsquare{xyellow} he does not know. This man presents the ``cyclical argument'' and the ``theory of recollection'' as part of four arguments for the immortality  \tsquare{xred} of the soul before  \ttriangle{xred} his death in Phaedo. For 10 points, what  \tdiamond{xyellow} philosopher offers an ``Apology'' prior  \tcircle{xgreen} to drinking hemlock in a Platonic dialogue? \ttriangle{gray} 

\textbf{Answer}: Socrates\\
\tsquare{xred} Phaedo
\ttriangle{xred} Phaedo
\ttriangle{gray} Phaedo
\end{frame}

\begin{frame}{Packet P5 Question 18}
A librarian from this  \tsquare{xred} city explored “ring numbers” and “snake numbers” to decode astronomical tables. Yuri Knorozov deciphered a syllabary by examining works named for Madrid, Paris, and this city. Reading an object named for this city was instrumental in deciphering “bar and dot” numerals and the Long Count calendar. This European city was where the oldest surviving book from the Americas was rediscovered, a Codex written in Mayan hieroglyphs. For 10 points what German city firebombed during World  \tsquare{xyellow} War II is home to  \tdiamond{xyellow} the Saxon State Library? \tcircle{gray}  \ttriangle{gray} 

\textbf{Answer}: Dresden\\
\tsquare{xred} Melvil Dewey
\tcircle{gray} Prague
\ttriangle{gray} New York City
\end{frame}

\begin{frame}{Packet P5 Question 19}
After a British monarch is appointed by a  \tsquare{xred} lottery during this year, he reinstututes local flags reminiscent of medieval heraldry. A critically-exalted manuscript named Air Chrysalis is published in this  \tcircle{xred} year. Adam Wayne protests against a highway shortly after Auberon Quin assumes power in this year in The Napoleon of Notting Hill. A man rents a room above Mr. Charrington's shop  \tcircle{xyellow} in this year, when he also begins an affair with Julia. For 10 points, events in what year title a 2010 Haruki Murakami novel and inspire Winston Smith to admit that “he loved Big  \tdiamond{xgreen} Brother”? \tsquare{gray}  \ttriangle{gray} 

\textbf{Answer}: Nineteen\ Eighty-Four\\
\tsquare{xred} George III of the United Kingdom
\tcircle{xred} Butterfly
\tsquare{gray} George III of the United Kingdom
\ttriangle{gray} 1968
\end{frame}

\begin{frame}{Packet P5 Question 20}
A member of this family  \tsquare{xred} cuts her hand after being ordered to punch out a window pane. Shortly before dying, a woman provides this family money by prostituting herself and by selling her hair and two of her teeth. The matriarch of this family dies in prison after they change their name to Jondrette. This family includes a street urchin named Gavroche, as well as daughters Anzelma and Eponine. This family mistreats Cosette while working as innkeepers. For 10 points, what family of troublemakers are the secondary antagonists in Victor Hugo’s Les Miserables? \tdiamond{gray}  \tcircle{gray}  \tsquare{gray}  \ttriangle{gray} 

\textbf{Answer}: Thénardiers\\
\tsquare{xred} ATP-binding cassette transporter
\tdiamond{gray} As I Lay Dying
\tcircle{gray} House of Habsburg
\tsquare{gray} ATP-binding cassette transporter
\ttriangle{gray} House of Medici
\end{frame}

\begin{frame}{Packet P5 Question 21}
While carrying firewood, this character laments a group of “adders who with cloven tongues do hiss me into madness.” After being given alcohol, this man promises to “show thee the best springs” and “pluck thee berries.” This character is confined to a rock after attempting to rape his master’s daughter, and believes that that sorcerer is sending spirits after him. This character regrets mistaking Trinculo and Stephano for gods as he remains stranded on a remote island. For 10 points, what son of Sycorax is the slave  \tsquare{xgreen}  \ttriangle{xgreen} of Prospero in William  \tdiamond{xgreen}  \tcircle{xred} Shakespeare’s The Tempest? \tcircle{gray} 

\textbf{Answer}: Caliban\\
\tcircle{xred} The Tempest
\tcircle{gray} The Tempest
\end{frame}

\begin{frame}{Packet P5 Question 22}
At the end of this play, a man uses his bus fare to play ``Little Man'' on a jukebox. A character in this  \tcircle{xgreen} play complains that his partner Hilda has reported him for not paying child support. After he is released from a hospital, an alcoholic father in this play forces its title character to massage his amputated leg stump. The main characters of this play reminisce about when they created a kite from garbage after they practice ballroom dancing  \tdiamond{xgreen} inside a tea shop. Sam and Willie endure racially-motivated abuse in Apartheid-era  \ttriangle{xgreen} South Africa  \tsquare{xred} in, for 10 points, what play by Athol Fugard? \tsquare{gray} 

\textbf{Answer}: ``Master\ Harold''...and\ the\ Boys\\
\tsquare{xred} Athol Fugard
\tsquare{gray} Athol Fugard
\end{frame}

\begin{frame}{Packet P5 Question 23}
This author created the character of Easy, who appears speaking English in a gibberish adaptation of Hamlet and reappears speaking gibberish in  \tcircle{xred} an English version of Macbeth performed in front of the secret police. This author parodied The Mousetrap in a play about the theater critics Moon and Birdboot, The Real Inspector  \tcircle{xyellow} Hound. In an absurdist  \tsquare{xgreen} play by this man, a troupe of tragedians prepare to stage  \tdiamond{xgreen} The Murder of Gonzago in Denmark. For 10 points what playwright wrote about two of Hamlet's friends  \ttriangle{xgreen} in Rosencrantz and Guildenstern are Dead?

\textbf{Answer}: Tom\ Stoppard\\
\tcircle{xred} Cyrano de Bergerac
\end{frame}

\begin{frame}{Packet P5 Question 24}
The climax of this poem asks ``Is it death or is it life?'' and answers in the next stanza with ``Life out of death.'' A character in this poem asks for a silver penny back after she declines to join in a feast. This poem presents the story of Jeanie, who died and ``fell  \tcircle{xgreen} with the first snow.'' This poem describes how a girl “suck’d and suck’d and suck’d the more... She suck’d until her lips were sore." This poem inspired an engraving by its author’s brother, Dante Gabriel. Sisters Lizzie and Laura hear  \tsquare{xgreen}  \ttriangle{xgreen} cries of “come buy, come buy” in, for 10 points, what poem about fruit vendors by  \tdiamond{xgreen} Christina Rosetti?

\textbf{Answer}: Goblin\ Market\\
\end{frame}

\begin{frame}{Packet P5 Question 25}
This object shows “sprawling flamboyant patterns committing every artistic sin.” Part of this object displays a pattern that looks ``like a broken neck and two bulbous eyes.'' Staring at this object makes a woman want to resume writing and to visit her Cousin Henry  \tdiamond{xyellow} and Julia. A physician named John moves  \tcircle{xgreen} his wife and children to the house containing this object, which is “a dull yet lurid orange in some places, a sickly sulpher tint in others.” For 10 points, a woman goes crazy fixating on what title object of a short story by Charlotte Perkins  \tsquare{xgreen} Gilman? \ttriangle{xgreen} 

\textbf{Answer}: The\ Yellow\ Wallpaper\\
\end{frame}

\begin{frame}{Packet P5 Question 26}
Stephen, a writer with this surname, committed plagiarism in articles written for The New Republic in the late 1990s. A woman with this surname plays bass in the punk band La Llorona and is the lover of Maggie Chascarrillo in Jaimie Hernandez's comics. While using the alias Black, children with this surname win money on the radio quiz “It’s A Wise Child.” This surname is shared by a woman who dates Lane Coutell and her brother, whose behavior frustrates Sybil Carpenter in ``A Perfect Day for Bananafish.'' For 10 points,  \tcircle{xred} what surname is shared by Franny and Seymour in J.D. Salinger's short fiction? \tdiamond{gray}  \tcircle{gray}  \tsquare{gray}  \ttriangle{gray} 

\textbf{Answer}: Glass\ family\\
\tcircle{xred} J. D. Salinger
\tdiamond{gray} Love
\tcircle{gray} J. D. Salinger
\tsquare{gray} The Spell (novel)
\ttriangle{gray} Epstein
\end{frame}

\begin{frame}{Packet P5 Question 27}
Oliver Cromwell destroyed  \tsquare{xred} a set of coronation regalia from this monarch used for several centuries. Osbert of Clare edited a two-part manuscript about the life of this ruler. Robert the Magnificent undertook an unsuccessful invasion to install this man as king; later, this man would later succeed his half-brother Harthacnut. This man was the  \tdiamond{xyellow}  \tsquare{xyellow} first king to be buried in a Romanesque church that he commissioned at Westminster. The short reign of Harold Godwinsson  \tcircle{xgreen} followed the rule of, for 10 points, what Anglo-Saxon king nicknamed for his  \ttriangle{xyellow} piety?

\textbf{Answer}: Edward\ the\ Confessor\\
\tsquare{xred} English Civil War
\end{frame}

\begin{frame}{Packet P5 Question 28}
A banking act passed under  \tsquare{xred} this prime minister gave the Bank of England the exclusive right to issue new banknotes. A man whose goal was to assassinate this prime minister, Daniel M'Naghten, names an insanity  \tcircle{xgreen} test. This man requested the queen to dismiss several  \tsquare{xyellow} of her ladies in waiting, precipitating the Bedchamber crisis. This prime minister, who served 20 years as an MP from Tamworth, repealed unpopular grain tariffs called the Corn Laws in response to the Irish Potato Famine. For 10 points, what  \tdiamond{xgreen} founder of modern British conservatism  \ttriangle{xgreen} inspired the nickname of London's police officers?

\textbf{Answer}: Robert\ Peel\\
\tsquare{xred} Glass–Steagall legislation
\end{frame}

\begin{frame}{Packet P5 Question 29}
Mark Lane’s best-selling book Rush to Judgment is critical of the actions of this group. Hale Boggs and  \tdiamond{xyellow}  \tcircle{xyellow} Gerald Ford were the  \ttriangle{xgreen} two representatives who were members of this group. It researched the ``curtain rod story,'' a trip to obtain passage to Cuba via Mexico City, and the murder of patrolman J.D. Tippit. Several members  \tsquare{xgreen} of this group disagreed with the magic bullet theory, though it officially concluded that Jack Ruby and Lee Harvey Oswald both acted alone.  \tcircle{xred} For 10 points, what group charged with exploring the assassination of JFK was chaired by the sitting Chief Justice?

\textbf{Answer}: Warren\ Commission\\
\tcircle{xred} Assassination of John F. Kennedy
\end{frame}

\begin{frame}{Packet P5 Question 30}
Tachi swords were notably  \tsquare{xred} ineffective against the leather armor worn by these people. Interactions with these people inspired the construction of a ``Borui'' stone wall, whose placement led to the battle of Koan. These people departed from Masan and were able to seize Iki and Tsushima during an expedition where they were repelled at Hakata Bay. An inability to pay  \tsquare{xyellow} the Samurai who fought these people presaged the downfall of the Kamakura shogunate.  \tcircle{xred} Kamikaze typhoons thwarted two attempted invasions of Japan by, for 10 points, what people under Kublai Khan? \tdiamond{gray}  \tcircle{gray}  \ttriangle{gray} 

\textbf{Answer}: Mongols\\
\tsquare{xred} Oath of the Horatii
\tcircle{xred} Maya civilization
\tdiamond{gray} Kamakura shogunate
\tcircle{gray} Maya civilization
\ttriangle{gray} Vikings
\end{frame}

\begin{frame}{Packet P5 Question 31}
One participant in this event noted that “Mikoyan liked very peppery soup, I do not” and would later claim that he would surpass his opponent in only seven years. The guest at this event argued that, although his host had better rockets, he had color television. A discussion over the purchasing power of miners and soldiers framed this event in Sokolniki Park between an American vice president and a Soviet first secretary. For 10 points, name this July 1959 debate between Nikita Kruschev and Richard Nixon held in a model  \tsquare{xyellow} home filled with refrigerators and dishwashers. \tdiamond{gray}  \tcircle{gray}  \ttriangle{gray} 

\textbf{Answer}: Kitchen\ Debate\\
\tdiamond{gray} Congress of Vienna
\tcircle{gray} Gerald Ford
\ttriangle{gray} San Diego Comic-Con
\end{frame}

\begin{frame}{Packet P5 Question 32}
The Yatenga kingdom of the Mossi people launched a raid that sacked Macina and this city in the mid-14th Century. Many manuscripts from this city are preserved in its Ahmed Baba Institute. Scholars fled from Walata to this city after the fall of the Ghana Empire, presaging its status as a center of learning based around the Sidi Yahya Mosque,  \tcircle{xgreen} the Sankore University,  \tsquare{xgreen} and the Djinguereber Mosque. Caravans  \tdiamond{xgreen}  \ttriangle{xyellow} brought salt to this city south from the Taghaza and Taoudenni mines to the Niger River. For 10 points, what cultural center of Mali flourished under the reign of Mansa Musa?

\textbf{Answer}: Timbuktu\\
\end{frame}

\begin{frame}{Packet P5 Question 33}
In a scene by this director, a man awakens in his plane to reveal hundreds of planes silently flying away from him. In a movie directed by this man, the two main characters hide in an abandoned mine after they are pursued by Captain Dola's pirates. This man directed a scene where a girl waits at a bus stop in the rain next to an enormous spirit creature, and formed  \tdiamond{xyellow} a production company following the success of Nausicaä of the Valley of the Wind. For 10 points what Japanese animator directed Porco Rosso, Castle in the Sky, and My Neighbor Totoro at Studio Ghibli? \tcircle{gray}  \tsquare{xgreen}  \ttriangle{gray} 

\textbf{Answer}: Hayao\ Miyazaki\\
\tcircle{gray} The Frogs
\ttriangle{gray} Stanley Kubrick
\end{frame}

\begin{frame}{Packet P5 Question 34}
One of these features  \tcircle{xred} appears in the foreground of a painting subtitled “Page From An American Textbook” by Robert Colescott. Another of these features inspired works depicting the Schreiber and Biglin brothers. One of these features is the focus of ``View from Mount Holyoke, Northampton, Massachusetts, after a Thunderstorm'' by Thomas Cole;  \ttriangle{xred} Cole and Frederic Church were members of a school of landscape painters named for  \tsquare{xred} one of these features in New York state. For 10 points, what type of natural feature dominates the foreground of Emanuel Leutze’s Washington Crossing the Delaware? \tdiamond{gray}  \tcircle{gray}  \tsquare{gray}  \ttriangle{gray} 

\textbf{Answer}: River\\
\tcircle{xred} Dune
\ttriangle{xred} Dune
\tsquare{xred} Hudson River School
\tdiamond{gray} FLAGS
\tcircle{gray} Dune
\tsquare{gray} Hudson River School
\ttriangle{gray} Dune
\end{frame}

\begin{frame}{Packet P5 Question 35}
The tenor soloist sings  \tsquare{xred} falsetto to represent  \tcircle{xred} one of these roasting animals in the “Olim lacus colueram” aria from Carl Orff’s Carmina Burana. Sixteen of these creatures inspired a horn theme that precedes six isolated chords in the finale of the fifth symphony by a Finnish composer. Saint-Saens represents this animal with a cello played over two pianos while the English horn is used for these creatures as they float through the realm of the dead in a tone poem from the Leminkainen Suite. For 10 points, a story from the Kalevala about what birds floating through Tuonela inspired Jean Sibelius? \tdiamond{gray}  \tcircle{gray}  \tsquare{gray}  \ttriangle{gray} 

\textbf{Answer}: Swan\\
\tsquare{xred} Choral symphony
\tcircle{xred} Carmina Burana (Orff)
\tdiamond{gray} Ralph Vaughan Williams
\tcircle{gray} Carmina Burana (Orff)
\tsquare{gray} Choral symphony
\ttriangle{gray} Snake
\end{frame}

\begin{frame}{Packet P5 Question 36}
The death of Jean Charles de Menezes inspired  \tsquare{xred}  \ttriangle{xred} a song performed around this object. “The bleeding hearts and artists” are said to “make their stand” outside of this place. Animated sequences by Gerald Scarfe are projected onto this object which is traditionally constructed by stagehands with cardboard boxes. This object is ordered destroyed at the end of “The Trial.” David Gilmour would stand on top of this object to perform “Comfortably Numb.” For 10 points “all in all we’re just another brick” in what title object of a concept album from Pink Floyd? \tdiamond{gray}  \tcircle{gray}  \tsquare{gray}  \ttriangle{gray} 

\textbf{Answer}: The\ Wall\\
\tsquare{xred} Bomb
\ttriangle{xred} Metropolitan Police Service
\tdiamond{gray} Pink Floyd – The Wall
\tcircle{gray} Moon
\tsquare{gray} Bomb
\ttriangle{gray} Metropolitan Police Service
\end{frame}

\begin{frame}{Packet P5 Question 37}
This television series  \ttriangle{xred} used selections from Hans Zimmer’s score  \tcircle{xred} to Backdraft. One regular on this series would arrive accompanied by a string quartet and was challenged by a series of opponents known as the Serie A after a soccer league. The host of this series would sometimes bite into a raw yellow pepper. Regular personalities on this series included French-trained Hiroyuki Sakai and Chen Kenichi. Contestants had sixty minutes to utilize the secret ingredient in, for 10 points, what cult Japanese cooking series that  \tsquare{xgreen} inspired an American adaptation starring Masaharu Morimoto and Bobby Flay? \tdiamond{gray}  \tcircle{gray}  \ttriangle{gray} 

\textbf{Answer}: Iron\ Chef\\
\ttriangle{xred} Cartoon Network
\tcircle{xred} Gladiator
\tdiamond{gray} The Hunger Games
\tcircle{gray} Gladiator
\ttriangle{gray} Cartoon Network
\end{frame}

\begin{frame}{Packet P5 Question 38}
Over 20,000 grebes died near this body of water in 2013 after it played host to an enormous outbreak of West Nile Virus, possibly transmitted by its shrimp population. This body of water, which is separated from the Tooele Valley by the Oquirrh Mountains, names the most populous city in the Wasatch Front.  \tsquare{xgreen} An artist visiting Rozel Point created  \tcircle{xgreen} a 1500-foot-long counterclockwise coil that jets into this body of water, Robert Smithson's Spiral Jetty. This body of water is directly east of the Bonneville Flats. For 10 points, what Utah lake  \tdiamond{xgreen} is named for its extreme salinity? \ttriangle{gray} 

\textbf{Answer}: Great\ Salt\ Lake\\
\ttriangle{gray} Gulf of California
\end{frame}

\begin{frame}{Packet P5 Question 39}
A person indicted for  \tsquare{xred} her role in these events was a former dental hygienist who treated a man who was attacked by a marble statue at a political rally. These events  \tcircle{xred} may take their name from a joke about two people who are captured and sentenced to death by an African chief. An underage girl nicknamed Ruby the Heartstealer  \tdiamond{xyellow} attended several of these events, which were held at a villa in Milan and involved  \tcircle{xyellow} exotic dancers dressed in costumes  \tsquare{xyellow} as nuns or as Barack Obama. For 10 points, give the repetitive, nonsensical name of a series of sex parties hosted by Silvio Berlusconi. \ttriangle{gray} 

\textbf{Answer}: Bunga\ bunga\\
\tsquare{xred} Raymond J. Donovan
\tcircle{xred} Haymarket affair
\ttriangle{gray} Witch-hunt
\end{frame}

\begin{frame}{Packet P5 Question 40}
A man has a vision of  \tsquare{xred} these characters after seeing a woman in a floating basket. In another depiction, these characters arrive from a whirlwind with ``feet of brass'' and reveal a different face on each side of their heads. Ezekiel and Zechariah observe analogs of these characters, one of whom instructs “do not damage the oil and the wine” while holding a pair of scales. John of Patmos describes these characters as arriving after the Lamb of God opens the first four of the seven seals. For 10 points, name these harbingers of the Last Judgment described in the Book of Revelation. \tdiamond{gray}  \tcircle{gray}  \tsquare{gray}  \ttriangle{gray} 

\textbf{Answer}: Four\ Horsemen\ of\ the\ Apocalypse\\
\tsquare{xred} Jacob's Ladder
\tdiamond{gray} 7
\tcircle{gray} Book of Revelation
\tsquare{gray} Jacob's Ladder
\ttriangle{gray} Rosencrantz and Guildenstern
\end{frame}

\begin{frame}{Packet P5 Question 41}
A holder of this title faced a non-French rebellion from relatives called the War of the Three Henries and attempted to secure the release of the jailed Pope Benedict VI, who was then murdered in prison. Another holder of this title arranged his son’s marriage to princess Theophanu to strengthen ties with the Byzantines. The holder of this title defeated the Magyars at the Battle of Lechfeld and conquered  \tcircle{xred}  \tsquare{xred} the Kingdom of  \ttriangle{xred} Italy after working to unify the German tribes. For 10 points, what title taken by Otto the Great was a callback to Charlemagne and refers to an earlier Italian civilization? \tdiamond{gray}  \tcircle{gray}  \tsquare{gray}  \ttriangle{gray} 

\textbf{Answer}: Holy\ Roman\ Emperor\\
\tcircle{xred} Ottonian dynasty
\tsquare{xred} Ottonian dynasty
\ttriangle{xred} List of monarchs of Hawaii
\tdiamond{gray} List of French monarchs
\tcircle{gray} Ottonian dynasty
\tsquare{gray} Ottonian dynasty
\ttriangle{gray} List of monarchs of Hawaii
\end{frame}

