\begin{frame}{Packet P6 Question 1}
This man described his vision for Europe as a “common European home.” This leader met with the U.S. president at the Reykjavik Summit. This man's foreign policy approach was dubbed the Sinatra Doctrine- referencing the song “My Way”- because he did not interfere in domestic issues of eastern European countries. He permitted private ownership of foreign trade businesses as part of his ``restructuring'' reform, or perestroika. For 10 points,  \tsquare{xgreen}  \ttriangle{xgreen} name this leader whom Ronald Reagan told  \tdiamond{xgreen} to tear down the Berlin Wall shortly before  \tcircle{xgreen} the fall of the Soviet Union.

\textbf{Answer}: Mikhail\ Gorbachev\\
\end{frame}

\begin{frame}{Packet P6 Question 2}
John  \tcircle{xred} Prine bemoaned the influence of this industry in his boyhood home in Muhlenberg county in his song “Paradise;” that protest song singled out a company in this industry that filled for Chapter 11 in 2016, only to emerge in the first year of the Trump administration.  \hsquare{xgreen} The term sacrifice zone was adapted from nuclear fallout to describe the effects of this industry. Big Muskie was the largest dragline machine in this industry to use a single bucket design. For 10 points name this industry that often uses stripmining to extracts fossil fuels from mountains. \hdiamond{xred}  \htriangle{xred} 

\textbf{Answer}: Coal\ mining\\
\tcircle{xred} Symmetric matrix
\hdiamond{xred} Coal
\htriangle{xred} Airline
\end{frame}

\begin{frame}{Packet P6 Question 3}
One book titled for these concepts, written by a barnacle expert, discusses the problem of why this concept exists. Ernst Mayr developed the modern version of this concept, based on actual or potential reproductive isolation.  \hdiamond{xgreen} Gause's law says that if two of these are in competition for the same resource, one will eventually drive out the other. The formation of these groups can be caused by barrier introduction, and new ones can emerge from adaptive radiation. For 10 points, this  \tcircle{xred} taxonomic classification below ``genus,'' on whose origin Darwin  \hcircle{xgreen}  \tsquare{xgreen}  \ttriangle{xgreen} wrote.

\textbf{Answer}: Species\\
\tcircle{xred} Speciation
\end{frame}

\begin{frame}{Packet P6 Question 4}
Bjorken and E. A. Paschos  \tsquare{xred} created a model  \tcircle{xred} of how these entities interact with high-energy electrons.  That approach used Feynman's model that these objects are composed of point-like constituents called ``partons''.  The name, meaning massive, was proposed by Lev Okun in 1962 to distingush them from leptons.  Consisting of two or more quarks bound by the strong force, for ten points, name this general class of particles that includes mesons and baryons like protons and neutrons. \hdiamond{xred}  \htriangle{xred} 

\textbf{Answer}: Hadron\\
\tsquare{xred} Deep inelastic scattering
\tcircle{xred} Higgs boson
\hdiamond{xred} Baryon
\htriangle{xred} Atomic nucleus
\end{frame}

\begin{frame}{Packet P6 Question 5}
A technical paper included  \tsquare{xred} in this book borrows Aristotle’s terms of “essence” and “accident” to distinguish between difficulties in designing conceptual constructs and difficulties in representing those conceptual constructs. That chapter of this book argues for the unlikelihood of  \tcircle{xred} finding a “silver bullet” to achieve a order-of-magnitude improvement in productivity based on the author's experience  \hsquare{xgreen} at IBM. This book put forth its author’s namesake law that “Adding manpower to a late software project makes it later.” For 10 points, name this seminal book on software engineering by Fred Brooks, titled  \hcircle{xgreen} after a “mythical” unit of work done by a person in a month. \hdiamond{xred}  \htriangle{xred} 

\textbf{Answer}: The\ Mythical\ Man-Month\\
\tsquare{xred} International Organization for Standardization
\tcircle{xred} Course in General Linguistics
\hdiamond{xred} Non-Euclidean geometry
\htriangle{xred} Fred Brooks
\end{frame}

\begin{frame}{Packet P6 Question 6}
It is conjectured that, if one of these objects has an infinite  \tcircle{xred} number of solutions, then an associated L-function constructed from the Euler product of the points lying on it modulo a prime p will equal zero when the complex variable equals one. The rational points of these objects have a finite basis by Mordell's theorem.  \hcircle{xgreen} Over the complex numbers, these objects correspond to embedding tori in the complex projective plane. A theorem relating  \tsquare{xgreen} these objects over the field of rationals to modular forms was instrumental  \ttriangle{xgreen} in Wiles' proof of Fermat's last theorem. For 10 points, name these curves given by an equation of the form y squared equals  \tdiamond{xgreen} x cubed plus A x plus B.

\textbf{Answer}: Elliptic\ curve\\
\tcircle{xred} Black hole
\end{frame}

\begin{frame}{Packet P6 Question 7}
Soft gamma repeaters and  \tsquare{xred}  \ttriangle{xred} AXP objects are thought  \tcircle{xred} to be stars characterized by high values of this variable according to a theory of Robert Duncan. The death valley for pulsars occurs when this variable goes below a value defined by period. This value for the corona has been inferred from distance between flux ropes and bow shock in CMEs. The splitting of astrophysical hydroxyl masers can be used to measure this quantity due to the Zeeman effect. For 10 points name this quantity, generated by the dynamo effect, which is characteristically enormous for magnetars. \hdiamond{xred} 

\textbf{Answer}: Magnetic\ field\\
\tsquare{xred} Magnetar
\ttriangle{xred} Magnetar
\tcircle{xred} Magnetar
\hdiamond{xred} Magnetar
\end{frame}

\begin{frame}{Packet P6 Question 8}
A 2018 Nature paper realized  \tsquare{xred} this system moving cesium atoms in an optical lattice, and Jarzynski and Mandal devised a solvable model of this system. Zurek used algorithmic randomness to study this system. Szilard explained this thought experiment  \tcircle{xgreen} by placing an energy cost on measurement. Charlie Bennett applied Landauer’s principle to resolve  \hsquare{xgreen} the paradox of this thought experiment, and it involves sorting molecules in its classic formulation. For 10 points name this thought experiment  \ttriangle{xred} where a fiendish agent allegedly violates the second law of thermodynamics,  \tdiamond{xgreen}  \htriangle{xgreen} named for a scottish physicist.

\textbf{Answer}: Maxwell's\ demon\\
\tsquare{xred} Space telescope
\ttriangle{xred} Original position
\end{frame}

\begin{frame}{Packet P6 Question 9}
The Sandmeyer reaction relies on a species of this type replacing the diazo group on an aromatic ring. An important family of concerted reactions named for these  \tdiamond{xred} species is carried out in a polar aprotic solvent and is slowed by steric effects.  \tcircle{xred} These species rely on leaving groups such as tosylates and halides to create  \tsquare{xred} carbocations in a unimolecular family of reactions named for them. For 10 points, name these chemical species that replace  \ttriangle{xred} a substituent in SN1 and SN2 reactions, ‘attacking’ electrophiles.

\textbf{Answer}: Nucleophile\\
\tdiamond{xred} Aryl halide
\tcircle{xred} SN2 reaction
\tsquare{xred} SN2 reaction
\ttriangle{xred} Ion
\end{frame}

\begin{frame}{Packet P6 Question 10}
One protein named for its high value of this property is mutated in patients with cutis laxa. Scientists measured this value for actin filaments using piezoelectrically controlled microneedles. Proteins, such as reslin, that have high values of this property often have a disordered structure, and connect to extracellular matrix glycoproteins like fibrillin. The Windkessel effect, as seen in the aorta, is caused by certain  \tcircle{xred} blood vessels having high values in this property, which can be calculated from a stress strain curve. For 10 points, name this property of proteins that can  \hdiamond{xgreen} store mechanical energy by stretching. \hsquare{xred}  \htriangle{xred} 

\textbf{Answer}: Elasticity\ (physics)\\
\tcircle{xred} Marfan syndrome
\hsquare{xred} Yield (engineering)
\htriangle{xred} Commutative property
\end{frame}

\begin{frame}{Packet P6 Question 11}
One of these physical features includes the pulpit rock and another features the “Seven Sisters Waterfall”. Two of these features in Newfoundland are found near Bonne Bay and Facheux Bay. These are some of the best places in the word to observe killer whales, as Orcas shelter in their waters because of their abundant herring population and warm gulf stream waters. Scoresby Sund,  \hdiamond{xgreen} the longest one of these physical features in the world, is in Greenland. For 10 points, name these narrow steep inlets  \tcircle{xgreen}  \tsquare{xgreen} that comprise most of the coastline of Norway. \htriangle{xred} 

\textbf{Answer}: Fjord\\
\htriangle{xred} Dune
\end{frame}

\begin{frame}{Packet P6 Question 12}
In “On Referring,” Strawson argued that a statement mentioning this country is referring, but the referent is only presupposed. A statement mentioning this country was presented as the second puzzle in a text whose third puzzle concerns ``the golden mountain'' and a ``round square.'' An expression about an individual from this country is analyzed as an “incomplete symbol,” which is neither strictly true nor strictly false, in“On Denoting.” A sample statement by Bertrand Russell describes, for 10 points, what country’s nonexistent present king as bald? \hdiamond{xred}  \hcircle{xred}  \hsquare{xred}  \htriangle{xred} 

\textbf{Answer}: France\\
\hdiamond{xred} England
\hcircle{xred} England
\hsquare{xred} Principia Mathematica
\htriangle{xred} Japan
\end{frame}

\begin{frame}{Packet P6 Question 13}
According to Strabo, priests  \tsquare{xred} of this deity would hold their breaths and crawl into a hole dedicated to Pluto that was filled with toxic fumes to show their immunity. On April 4, this deity was celebrated with theatrical shows called ludi scaenici during the Megalesia  \hsquare{xgreen} festival. Atalanta  \tcircle{xgreen} and Hippomenes once had sex in a temple  \ttriangle{xgreen} to this deity.  \tdiamond{xgreen} The priests of this deity, who were known as the Galli, castrated themselves like this deity’s consort Attis. For 10 points, name this Phrygian goddess who was adopted into the Roman pantheon as Magna Mater, the Great Mother.

\textbf{Answer}: Cybele\\
\tsquare{xred} Statue of Zeus at Olympia
\end{frame}

\begin{frame}{Packet P6 Question 14}
Hermann Weyl added a local symmetry to this theory in his attempt  \tsquare{xred} to unify it with electromagnetism. Cyclic permutations of the indices of one construct defined by this theory must sum to zero according to a result of an Italian mathematician. Hilbert derived the central equation of this theory by requiring the action be invariant under coordinate transformations.  \tcircle{xred} That equation from this theory quantifies curvature with a rank two tensor  \htriangle{xgreen} an includes source terms from momentum and energy density in four dimensional spacetime. For 10 points  \hcircle{xgreen} name this theory  \tdiamond{xgreen} of gravity developed by Einstein.

\textbf{Answer}: General\ relativity\\
\tsquare{xred} Lie
\tcircle{xred} Special relativity
\end{frame}

\begin{frame}{Packet P6 Question 15}
Ahura Mazda sent these  \tsquare{xred} creatures to guard the tree of life in a Zoroastrian story. In a Cherokee creation myth, the first man hits the first woman with one of these animals, causing her to give birth every seven days. The god Enki had these animals as a symbol, and an avatar of Vishnu, Matsya took this form. One of these animals ate nine hazelnuts from the Well  \hsquare{xgreen} of Wisdom, leading  \tdiamond{xgreen} to a drop of its fat giving all of the world's knowledge to Finn Mac Cool. For  \tcircle{xgreen} 10 points, name these animals exemplified by the Zodiac Pisces and the early Christian symbol Ichthys. \htriangle{xred} 

\textbf{Answer}: Fish\\
\tsquare{xred} Angra Mainyu
\htriangle{xred} Horse
\end{frame}

\begin{frame}{Packet P6 Question 16}
This character wishes that the night of his  \tsquare{xred} conception would “hope for light, but have none, nor see the eyelids of the morning" and asks why he was “not as a hidden stillborn child, as infants who never see the light?” This character is told to “Gird up your loins like a man” by another character speaking “out of the whirlwind.” This man declares, “I know that my Redeemer lives” as he defends himself from the accusations of his friends Eliphaz, Zophar, and  \tcircle{xred}  \ttriangle{xred} Bildad. For 10 points, name this Old Testament character who is tested with great suffering. \hdiamond{xred} 

\textbf{Answer}: Job\\
\tsquare{xred} Prince Hamlet
\tcircle{xred} Book of Job
\ttriangle{xred} Book of Job
\hdiamond{xred} Book of Job
\end{frame}

\begin{frame}{Packet P6 Question 17}
A Harvard Business School  \tsquare{xred} case analyzes the  \ttriangle{xred} role of this commodity in Credem's banking operations in northern Italy. A controversy arose in 2014 when the European Union demanded protection for “Geographical Indication`` names for different types of this commodity. An Italian miller compared the mixing of earth, air, water, and fire to the creation of this commodity- which subsequently led to the emergence of angels analogized to worms- as related in a Carlo Ginzburg microhistory. Parmigiano-Reggiano is called the ''king of," for 10 points, what food, a form of curdled milk? \hdiamond{xred}  \hcircle{xred} 

\textbf{Answer}: Cheese\\
\tsquare{xred} Jeff Immelt
\ttriangle{xred} Jeff Immelt
\hdiamond{xred} Cotton
\hcircle{xred} Ivory
\end{frame}

\begin{frame}{Packet P6 Question 18}
According to Plutarch,  \tsquare{xred} people with this occupation would mock the recipients of their services by dressing them up in Roman boots and a toga to  \tcircle{xred} not mistake their identity. Following an incident at Ostia, the activities of people with this occupation were limited by the Lex Gabinia. At the age of 25, Julius Caesar demanded that people with this occupation from Cilicia should have charged him 50 talents  \ttriangle{xred} instead of 20 to release him from captivity. For 10 points, Pompey the Great suppressed what criminal maritime occupation? \hdiamond{xred} 

\textbf{Answer}: Piracy\\
\tsquare{xred} Parallel Lives
\tcircle{xred} Gladiator
\ttriangle{xred} List of historians
\hdiamond{xred} Clown
\end{frame}

\begin{frame}{Packet P6 Question 19}
The “Schedule of Questions” was used by James Bertram to determine whether communities would be allowed  \hdiamond{xgreen} to benefit from one of these institutions. The words “Let there be light” were typically carved above the entrances of these institutions, honoring a request by their sponsor. These institutions pioneered  \tsquare{xgreen} the use of open stacks, making use of a layout with “battleship” desks for  \hcircle{xgreen} circulation. For 10 points, name these libraries that were sponsored in the late 19th and early 20th centuries by a namesake Scottish-American steel magnate. \htriangle{xred} 

\textbf{Answer}: Carnegie\ library\\
\htriangle{xred} Monastery
\end{frame}

\begin{frame}{Packet P6 Question 20}
This lawyer helped Matthew Kilroy and Hugh Montgomery avoid a death sentence by having them claim the benefit of clergy. This lawyer questioned whether a man being hit with a club should be “patient as  \tcircle{xred} Epictetus while his master was breaking his legs with a cudgel” in a speech disparaging a crowd as “a motley rabble of saucy boys, negroes and mulattoes, Irish teagues and outlandish jack tarrs” in defending Captain Thomas Preston for the Boston  \hdiamond{xgreen}  \ttriangle{xred} Massacre.  For 10 points, name this American statesman, first Vice President, second President, and father of the  \hsquare{xgreen} sixth President.

\textbf{Answer}: John\ Adams\\
\tcircle{xred} Abe Fortas
\ttriangle{xred} Boston Massacre
\end{frame}

\begin{frame}{Packet P6 Question 21}
A Renzo Piano building  \tsquare{xred} in this country has  \tdiamond{xred}  \tcircle{xred} a large wavy metal-and-glass roof that blends into it hilly surroundings and houses works of a 20th century artist from here. That artist from this country lived in Germany while producing a Pedagogical Sketchbook for a Bauhaus course. This country is where Hugo Ball recited the first dada manifesto, and it was home to Cabaret Voltaire. One artist from this country depicted stick-bodied birds in an ink and watercolor work called Twittering Machine. For 10  \hdiamond{xgreen} points, name this home country of Paul Klee, where the Dada art movement grew in Zurich. \htriangle{xred} 

\textbf{Answer}: Switzerland\\
\tsquare{xred} Airport
\tdiamond{xred} Italy
\tcircle{xred} Japan
\htriangle{xred} Japan
\end{frame}

\begin{frame}{Packet P6 Question 22}
A book that inspired this movement describes how the author was told to chant sutras or donate money to  \tsquare{xred} be saved, then realized that it would be hard to avoid “evil thoughts” on a daily basis. That book, which was written under the pen name “Student of Good,” is titled Good Words to Admonish the Age. This movement’s founder asked Issachar Jacox  \hdiamond{xgreen} Roberts to interpret  \tcircle{xgreen} a series of dreams  \hsquare{xgreen} he had after repeatedly failing civil service exams, in which he saw that he was a younger brother of Jesus. For 10 points, name this millenarian movement that Hong Xiuquan led  \ttriangle{xgreen} in revolt against the Qing dynasty.

\textbf{Answer}: Taiping\ Rebellion\\
\tsquare{xred} Ice Bucket Challenge
\end{frame}

\begin{frame}{Packet P6 Question 23}
Paul Hardcastle composed  \tsquare{xred}  \ttriangle{xred} a song about this conflict including audio from news broadcasts, titled for the average age of one side’s participants. In a film set during this war, ``These Boots Are Made for Walking'' plays before a scene where the protagonist’s camera is snatched; that film set in this war  \tcircle{xred} features “Paint it Black" during its end  \hdiamond{xgreen} credits. A character blasts Ride of the Valkyries from helicopters and claims to “love the smell of napalm in the morning”  \hcircle{xgreen} in a film set in war. For 10 points, name this war, the setting of Full Metal Jacket and Apocalypse Now.

\textbf{Answer}: Vietnam\ War\\
\tsquare{xred} She Stoops to Conquer
\ttriangle{xred} She Stoops to Conquer
\tcircle{xred} World War I
\end{frame}

\begin{frame}{Packet P6 Question 24}
Cedric Watts claimed that  \tsquare{xred} one author reveled in “stirring things up” by condemning this author. An essay partly titled for this author relates how its author received two letters about ``superstitions'' from school children in Yonkers. In a novel  \tcircle{xred} that is a ``counter-narrative'' or ``inversion'' of a novel by this author, Mustafa states that “I am no Othello, Othello was a lie” and recounts how he killed himself in the Nile; that book is Season of Migration to the North. For 10 points, name this author derided as a racist in Chinua Achebe's “An  \hdiamond{xgreen} Image of Africa” for  \tdiamond{xred} his book Heart of Darkness. \htriangle{xred} 

\textbf{Answer}: Joseph\ Conrad\\
\tsquare{xred} Ivanhoe
\tcircle{xred} Chinua Achebe
\tdiamond{xred} Chinua Achebe
\htriangle{xred} Joseph Conrad
\end{frame}

\begin{frame}{Packet P6 Question 25}
In a short story partly titled for this historical figure, a woman leaves her diaphragm  \tcircle{xred} at her mother's house, ending any chance for her boyfriend to marry into her family's sink manufacturing business. The “Ave Maria” section of The Bridge is about the actions of this person. In a collection titled for this person, Ozzie threatens to jump off his school unless the crowd admits God could allow virgin birth in the story “The Conversion of the Jews.” For 10 points, name this explorer who is said “Goodbye” in the title of a Philip Roth short  \ttriangle{xred} story collection. \hdiamond{xred}  \hsquare{xred} 

\textbf{Answer}: Christopher\ Columbus\\
\tcircle{xred} Ixion
\ttriangle{xred} Goodbye, Columbus
\hdiamond{xred} João Guimarães Rosa
\hsquare{xred} The Illustrated Man
\end{frame}

\begin{frame}{Packet P6 Question 26}
During a feast in this poem, an obese doctor of divinity gorges himself on both food and scripture. In this poem, Patience teaches the virtues of poverty to Haukyn the Active Man. Divided into sections knowns as “passus,”  \hdiamond{xgreen} this poem’s narrator falls asleep in the Malvern Hills and awakes  \tcircle{xgreen} to see a valley  \tsquare{xgreen} teeming with “a fair field of folk.” Its author published this poem in a revised B-version, likely to distance himself from Wat Tyler. Its second section concerns the narrator’s quest to find Do-Well, Do-Better, and Do-Best.  \ttriangle{xgreen} For 10 points, name this allegorical poem by William Langland.

\textbf{Answer}: Piers\ Plowman\\
\end{frame}

\begin{frame}{Packet P6 Question 27}
“Arraignment” by Robin  \ttriangle{xred} Morgan speculates about the true cause of death of this poet. In a poem written about this person, the speaker recalls “Bending so briefly at your open coffin” and describes the “mad, execution uniform” that she wore on her first day of work. This author was memorialized in the poem “The Blue Flannel Suit” by her husband,  \tsquare{xred} Ted Hughes. A poem  \tdiamond{xgreen}  \tcircle{xgreen}  \htriangle{xgreen} by this author describes a “Polish town scraped flat by the roller of wars, wars, wars.” For 10 points name this American writer of “Daddy" who committed suicide in 1963.

\textbf{Answer}: Sylvia\ Plath\\
\ttriangle{xred} Miklós Horthy
\tsquare{xred} Birthday Letters
\end{frame}

\begin{frame}{Packet P6 Question 28}
In one novel set in one of these locations, the narrator tells a story about when he was hit the head by the rector of the Sorbonne and explains how he was fired as head cable fitter for making charts of his coworkers' alcohol  \hdiamond{xgreen} consumption. Lebedev, Rogozhin, and Myshkin meet in one  \tcircle{xred} of these locations in the first chapter  \ttriangle{xred} of The Idiot. Pozdnyshev tells the story of how he killed his wife after she had an affair with a violinist in a novella mostly set in one of these locations, The Kreutzer Sonata. For 10 points, name these vehicles, one of which kills the title character of Anna Karenina. \hsquare{xred} 

\textbf{Answer}: Train\\
\tcircle{xred} The Idiot
\ttriangle{xred} Sacred grove
\hsquare{xred} Leo Tolstoy
\end{frame}

\begin{frame}{Packet P6 Question 29}
A character in this novel  \tcircle{xred} abandons a suicide attempt after seeing himself in the water, though it is later revealed that what he actually saw was a manikin dressed up like him. In order to make amends with his daughter, that character in this novel brings her a goldfinch for her wedding, but it dies before it is found. This novel's title character swears off drinking for 21 years after accepting five guineas in exchange  \hcircle{xgreen}  \tsquare{xgreen} for his wife Susan at an auction. For  \hdiamond{xgreen} 10 points name this Wessex novel that tells of  the decline of Michael Henchard,  \ttriangle{xgreen} a work by Thomas Hardy.

\textbf{Answer}: The\ Mayor\ of\ Casterbridge\\
\tcircle{xred} Latin
\end{frame}

\begin{frame}{Packet P6 Question 30}
Its not water, but Li  \tsquare{xred} Bing developed a process for extracting this commodity from wells. Huo Guang initiated  \hdiamond{xgreen}  \tcircle{xgreen}  \hsquare{xgreen} a series of debates, or ``discourses,'' about a Han Dynasty monopoly on iron and this commodity. The Great Hedge of India was planted along the Inland Customs Line to facilitate the collection of a tax on this good. A nonviolent protest was planned for a center of this commodity's production at Dharasana, but its leader was arrested a month after he arrived in Dandi. For 10 points, name this good whose taxation was protested by a Mohandas  \ttriangle{xgreen} Gandhi march.

\textbf{Answer}: Salt\\
\tsquare{xred} An Lushan Rebellion
\end{frame}

\begin{frame}{Packet P6 Question 31}
Seneca credited Pompey  \tcircle{xred} with first exhibiting the slaughter of these animals in the Circus, which, according to Cicero, led people to think that this animal “has something in common with mankind.” The Romans sometimes called these animals ``Lucanian oxen,'' referencing  \hsquare{xgreen} their decisive use in defeated Roman forces at the Battle of Heraclea. At the Battle of Ipsus, Seleucus I Nicator defeated Antigonus I using a force of these animals that had been given to him by Chandragupta Maurya. For 10 points, name  \tsquare{xred} these war animals with which Hannibal crossed the Alps. \hdiamond{xred}  \htriangle{xred} 

\textbf{Answer}: Elephant\\
\tcircle{xred} Lysosome
\tsquare{xred} Diadochi
\hdiamond{xred} Horse
\htriangle{xred} Horse
\end{frame}

\begin{frame}{Packet P6 Question 32}
A concerto for this instrument  \tcircle{xred} by John Corigliano features a first movement in which the soloist and the orchestra play a “Tuning Game.” Mozart reworked a concerto for this instrument  \hcircle{xgreen} into his D major Flute Concerto No. 2.  \tsquare{xgreen} Besides his Adagio in G minor, Tomaso Albinoni is best known for his Opus 9 which includes twelve concerti for this instrument. This instrument represents the duck in Sergei Prokofiev's  \htriangle{xgreen} Peter and the Wolf. Most orchestras  \tdiamond{xgreen} tune to an A played by, for 10 points, what highest double reed woodwind instrument?

\textbf{Answer}: Oboe\\
\tcircle{xred} Garden
\end{frame}

\begin{frame}{Packet P6 Question 33}
A composer from this country wrote a highly symmetrical piece  \hcircle{xgreen} for solo amplified violin called Strung Out. That composer from here used an ``additive technique'' for works like 1+1, which is played on a table top. A composer from this country used sounds from tin cans, conch shells, and two variable-speed turntables in a set of compositions whose fourth entry calls  \hdiamond{xgreen} for the use of twelve radios. A composer from this country explored the role of chance in his Imaginary Landscapes and called for a duration of ambient noise  \tsquare{xred} in 4'33''. For 10  \tcircle{xred} points name this birthplace of Philip Glass and John Cage. \htriangle{xred} 

\textbf{Answer}: United\ States\\
\tsquare{xred} John Cage
\tcircle{xred} John Cage
\htriangle{xred} France
\end{frame}

\begin{frame}{Packet P6 Question 34}
Philip the Bold commissioned  \tsquare{xred} an international gothic style hexagonal structure named for this person that  \ttriangle{xred} was designed by Claus Sluter; that was  \hdiamond{xgreen} this man's namesake ``well.'' Sigmund Freud wrote an essay that ascribed meaning to the minute, sacrilegous details of a statue of this man, who loosely holds a set of tablets with his right hand. Julius II commissioned that sculpture of this figure for his tomb, and it includes horns commonly seen on this figure in medieval art. For 10 points, name this prophet, whom Michelangelo sculpted holding the Ten Commandments. \hcircle{xred} 

\textbf{Answer}: Moses\\
\tsquare{xred} Duchy of Burgundy
\ttriangle{xred} Walt Disney World Swan
\hcircle{xred} Michelangelo
\end{frame}

\begin{frame}{Packet P6 Question 35}
In the Resurrection from the Isenheim Altarpiece, Jesus unusually wears a garment of this color. Robert  \tcircle{xred}  \htriangle{xgreen} Campin used this color  \tsquare{xred} for Mary’s robe  \hcircle{xgreen} in the annunciation  \hdiamond{xgreen} scene of his Merode Triptych. Tintoretto used a beetle based pigment of this color called carmine in the garments of the title character of his painting Miracle of the Slave. Titian highlighted the central figure in his Assumption of the Virgin using a cinnabar-based pigment of this color, vermillion. The bed in the background of The Arnolfini Wedding is, for 10 points, what primary color used to depict blood?

\textbf{Answer}: Red\\
\tcircle{xred} Blue
\tsquare{xred} Altarpiece
\end{frame}

\begin{frame}{Packet P6 Question 36}
Craig Hartman of Skidmore, Owings and Merrill  \tsquare{xred}  \ttriangle{xred} designed a curving glass facade for this city’s Cathedral of Christ the Light. A portmanteau of this city and Amsterdam names a district north of its downtown, home to “America’s first cannabis college.” Emeryville is located north of this city, which is immediately east of Alameda island. This city’s downtown is near Lake Merritt, and  \hdiamond{xgreen} its train station is part of Jack London square. This city is connected to its western neighbor by the BART subway system. For 10 points, name this city south of Berkeley and across the Bay from San Francisco. \hcircle{xred} 

\textbf{Answer}: Oakland,\ California\\
\tsquare{xred} Burj Khalifa
\ttriangle{xred} Burj Khalifa
\hcircle{xred} Melbourne
\end{frame}

\begin{frame}{Packet P6 Question 37}
A basketball player who  \tsquare{xred} went to a university in this state was a 2 time NBA MVP and led the Hawks to their only NBA Championship. A center for that university in this state went on to break two backboards in the 1992-3 season. While attending school in this state, one player scored 44.2 points per game while coached by his father. A basketball player who went to a university here won Rookie of the Year in 2018 and was the first overall pick in the 2016 NBA Draft. For 10 points, name this state, where Bob Pettit, Pete Maravich, Shaquille O’Neal, and Ben Simmons played for LSU. \hdiamond{xred}  \hcircle{xred}  \htriangle{xred} 

\textbf{Answer}: Louisiana\\
\tsquare{xred} Tracy McGrady
\hdiamond{xred} Kansas
\hcircle{xred} Michael Jordan
\htriangle{xred} Pennsylvania
\end{frame}

\begin{frame}{Packet P6 Question 38}
A November 20 statement on this nation begins “The world is a very dangerous place!” and criticizes Iran. It is home to the Global Center for Combating Extremist Ideology, which was the setting of a photo-op with Abdel Fattah el-Sisi of Egypt and the Trumps. In November, its capital's Ritz-Carlton served as an ad hoc prison during a corruption crackdown that included several princes. For 10 points, what oil-exporting nation led by Crown Prince Mohammad bin Salman was implicated in the murder of the Washington Post reporter Jamal Khashoggi? \hdiamond{xred}  \hcircle{xred}  \hsquare{xred}  \htriangle{xred} 

\textbf{Answer}: Saudi\ Arabia\\
\hdiamond{xred} South Korea
\hcircle{xred} Tiger
\hsquare{xred} George Tenet
\htriangle{xred} Nepal
\end{frame}

\begin{frame}{Packet P6 Question 39}
A palace in this country contains the largest collection of Chinese porcelain outside of China. The Basilica Cistern in this country features two columns supported by Medusa heads, and figures in James Bond's plot to steal the Lektor in From Russia with Love. In this country, the Sarayburnu Promontory contains the historic Topkapi Palace and  \tsquare{xred} borders a waterway called the Golden Horn. One can take a ferry from this country's largest city to Bursa, over the Sea of Marmara. For 10  \tdiamond{xgreen}  \hcircle{xgreen} points, name this country where bridges cross the Bosporus near Istanbul. \htriangle{xred} 

\textbf{Answer}: Turkey\\
\tsquare{xred} Istanbul
\htriangle{xred} India
\end{frame}

\begin{frame}{Packet P6 Question 40}
One of these artworks,  \tcircle{xred}  \tsquare{xred} which consists of a woman holding a baby in her arms, was executed in Siena by Jacopo della Quercia, and was named for Gaia. Another of these works, showing a man kneeling on a shell and drinking from another shell, was commissioned by the Barberini. One of these works was built around an obelisk crowned  \hcircle{xgreen} by a dove holding a tree branch in a piazza next to the Palazzo Pamphili. Nicola Salvi is today remembered for designing one of these works. For 10 points,  \ttriangle{xred} name these works such as the Four Rivers and the Trevi, which include flowing water. \hdiamond{xred} 

\textbf{Answer}: Fountain\\
\tcircle{xred} Tapestry
\tsquare{xred} Medal
\ttriangle{xred} Harry Potter fandom
\hdiamond{xred} Fontana dei Quattro Fiumi
\end{frame}

\begin{frame}{Packet P6 Question 41}
Margo Sappington and the  \tsquare{xred} Milwaukee Ballet created a ballet based on this artist's work titled after his cover of a Pulp song in collaboration with Joe Jackson and Ben Folds. This artist recently covered ``Seeking Major Tom'' on an album that includes versions of ``Space Oddity''. This artist included a speech from Henry V and a spoken word cover culminating in him screaming ``Mr. Tambourine Man'' on his debut  \hdiamond{xgreen} album, The Transformed Man. For 10 points, name this man whose musical career followed up acting  \ttriangle{xred} success on Star Trek where he played Captain  \hsquare{xgreen} Kirk. \hcircle{xred} 

\textbf{Answer}: William\ Shatner\\
\tsquare{xred} The Big Money
\ttriangle{xred} William Hung
\hcircle{xred} Alexander Stirling Calder
\end{frame}

