\begin{frame}{Packet P7 Question 1}
This game contains an easter egg based on fan art of blocks spelling out ``P A M'' and an insect in a top hat, and its launch was declared a holiday by Jim Justice on November 14, 2018.  The ``Personal Matters'' quest requires the player to kill Evan, who was the now-scorched fiancé of the Overseer.  Locations in this game include the Whitespring Resort, which is based on the real-life Greenbrier resort in Solphur Springs, West Virginia.  A multiplayer game centered on a control vault, for ten points name Bathesda's most recent entry in the Fallout franchise.  \tdiamond{gray}  \tcircle{gray}  \tsquare{gray}  \ttriangle{gray} 

\textbf{Answer}: Fallout\ (series)\\
\tdiamond{gray} HaLo
\tcircle{gray} Who Wants to Be a Millionaire?
\tsquare{gray} Halo: Combat Evolved
\ttriangle{gray} The Legend of Zelda: Skyward Sword
\end{frame}

\begin{frame}{Packet P7 Question 2}
In one scene in this movie, a girl orders a Chocolate Milk, cold before presenting her theory of the case to Yoko Ono.  The title place's northern most point is called the Far-away cuticles extending from the Middle Fingers and is visited by an owl who reports the  mayor's death sentence for the main characters, ostensibly becaues they contracted snout fever.  Characters recount their favorite foods-Kobe ribeye, yakitori sausage, green tea ice cream, and Doggy Chop-as they search for the lost dog of Atari, who crash-landed in the title location.  For ten points, name this 2018 stop-motion anamated film about the canine exiles from Magasaki by Wes Anderson.    \tdiamond{gray}  \tcircle{gray}  \tsquare{gray}  \ttriangle{gray} 

\textbf{Answer}: Isle\ of\ Dogs\ (film)\\
\tdiamond{gray} Moonrise Kingdom
\tcircle{gray} Ode on a Grecian Urn
\tsquare{gray} Amarcord
\ttriangle{gray} Django Unchained
\end{frame}

\begin{frame}{Packet P7 Question 3}
Alan Hajek ``waged war'' on it by suggesting a mixed strategy: make the decision based on whether you win the lottery.  His  \tcircle{xred} suggested fixes were to require overriding utility and distinguishable expectations.  Diderot's contemperaneous objection was that it assumed the existance of a single entity, and Schlesinger attempted to refute the ``many gods'' critique by arguing that its formulator's  \tdiamond{xyellow} God was more probable than any other.  Assuming a payoff matrix with an infinite gain regardless of how small the probability, for  \ttriangle{xgreen} ten points, is what philosophical argument for God by French  \tsquare{xgreen} mathematician? \tcircle{gray} 

\textbf{Answer}: Pascal's\ Wager\\
\tcircle{xred} Shirley Jackson
\tcircle{gray} Shirley Jackson
\end{frame}

\begin{frame}{Packet P7 Question 4}
Many creation myths from this country refer to the first sunrise with the phrase “Zep Tepi.” A creation myth from this country holds that human beings were formed from the tears of a disobedient eye that was separated from its holder. In a story from this country, four frog gods and  \tcircle{xred} four snake goddesses combine to form a mound of earth that emerges from a vast, lifeless ocean called Nu. Atum created the first deities, Shu and Tefnut, in a myth that originated in this country’s city of Heliopolis. For 10 points, name this country where other myths explain the origins of Osiris. \tdiamond{gray}  \tcircle{gray}  \tsquare{gray}  \ttriangle{gray} 

\textbf{Answer}: Egypt\\
\tcircle{xred} Japan
\tdiamond{gray} Central African Republic
\tcircle{gray} Japan
\tsquare{gray} Ra
\ttriangle{gray} Japan
\end{frame}

\begin{frame}{Packet P7 Question 5}
In one of these works, a woman earns a living playing a lute during a twelve-year search for her husband. A character in one of these works exhumes the corpse of a woman after dreaming of their mutual love. Performers in these works were often called “Disciples of the Pear Garden.” After Wu Han wrote one of these works that ignited public controversy, all but eight “model” examples of these works were banned during the Cultural Revolution. Tale of the Pipa and The Peony Pavilion  \ttriangle{xred} are, for 10 points, which Chinese works that often include musical performances? \tdiamond{gray}  \tcircle{gray}  \tsquare{gray}  \ttriangle{gray} 

\textbf{Answer}: Opera\\
\ttriangle{xred} Harry Potter fandom
\tdiamond{gray} Constantin Brâncuși
\tcircle{gray} Harry Potter fandom
\tsquare{gray} Amy Tan
\ttriangle{gray} Harry Potter fandom
\end{frame}

\begin{frame}{Packet P7 Question 6}
These molecules can undergo  \tsquare{xred} a change called remolding or recruitment,  \tcircle{xred} perhaps explaining why only twenty two varieties of these molecules are encoded in mitochondrial DNA. The D arm of these molecules is named for the presence of dihydrouridine, and in eukaryotes  \tcircle{xyellow} they possess a CCA tail. A namesake aminoacyl synthetase catalyzes  \tsquare{xyellow} the “charging” of these molecules. The secondary structure of these molecules is often visualized as a clover leaf. Amino acids are carried to the ribosome by, for 10 points, what molecules that  \ttriangle{xgreen} bind to mRNA during  \tdiamond{xgreen} translation?

\textbf{Answer}: Transfer\ RNA\\
\tsquare{xred} Major histocompatibility complex
\tcircle{xred} RNA
\end{frame}

\begin{frame}{Packet P7 Question 7}
An experiment using Chara provided evidence for the pressure-based model of the impact of this phenomenon, by which it can reverse the polarity of cytoplasmic streaming. This phenomenon is perceived by a specialized variety of amyloplast in statolith cells, which then redirects auxins laterally away from the elongation zone. Generally, roots grow in the direction of this phenomenon, while stems grow in the opposite direction of this phenomenon. This phenomenon that, like light, names a “tropism” that prominently shapes plant development. For 10 points, name this fundamental force that pulls plants (and everything else on Earth) downward. \tdiamond{gray}  \tcircle{gray}  \tsquare{gray}  \ttriangle{gray} 

\textbf{Answer}: Gravity\\
\tdiamond{gray} Fire
\tcircle{gray} Polyploid
\tsquare{gray} Phototropism
\ttriangle{gray} Diffraction
\end{frame}

\begin{frame}{Packet P7 Question 8}
This type of reaction occurs in the second, isobaric step of a normal Brayton Cycle. This type of reaction names a type of synthesis also known as SHS that is used to produce nanomaterials. Initiating this type of reaction often requires one reactant to make a forbidden transition from a triplet state to a singlet state.  \tdiamond{xyellow}  \tcircle{xgreen}  \tsquare{xgreen} This type of reaction, whose incomplete form can produce carbon monoxide, occurs at temperatures above the flash point. Catalytic converters process the byproducts  \ttriangle{xred} of, for 10 points, what type of reaction that names an “internal engine” found in automobiles? \ttriangle{gray} 

\textbf{Answer}: Combustion\\
\ttriangle{xred} Addition reaction
\ttriangle{gray} Addition reaction
\end{frame}

\begin{frame}{Packet P7 Question 9}
Ernst Bauer first described a “low energy” variety of these devices that can analyze thin films. The resolution of these devices can be improved by using a lanthanum hexaboride cathode instead of a tungsten cathode. Before use with one type of these devices, samples  \tcircle{xred} are often either stained with osmium or coated in a layer of gold. Surface morphology can be determined using the “scanning” variety of these devices, while their “transmission” variety requires the use of an ultrathin sample. For 10 points,  \tsquare{xyellow} name these magnification devices that use negatively charged particles. \tdiamond{gray}  \tcircle{gray}  \ttriangle{gray} 

\textbf{Answer}: Electron\ microscope\\
\tcircle{xred} Laser
\tdiamond{gray} Ion trap
\tcircle{gray} Laser
\ttriangle{gray} Microscope
\end{frame}

\begin{frame}{Packet P7 Question 10}
Caffarelli et al. showed that a singularity predicted by these equations would not exist for any finite duration of time. They are the subject of a widely cited 1968 paper by Alexandre Chorin. By starting  \tcircle{xred} with these equations in three dimensional cylindrical coordinates, one can apply Newton’s first law to derive the Hagen-Poiseuille equation. The “existence and  \ttriangle{xred} smoothness” problem of completely solving these equations is one of the Millenium Prize problems. Unlike the Euler equations, non-inviscid flow is described by, for 10 points, what equations that describe viscous fluid motion? \tdiamond{gray}  \tcircle{gray}  \tsquare{gray}  \ttriangle{gray} 

\textbf{Answer}: Navier–Stokes\ equations\\
\tcircle{xred} Compact finite difference
\ttriangle{xred} Compact finite difference
\tdiamond{gray} Compact finite difference
\tcircle{gray} Compact finite difference
\tsquare{gray} Lakoff
\ttriangle{gray} Compact finite difference
\end{frame}

\begin{frame}{Packet P7 Question 11}
A speculative NASA project seeks to send small, spiky, “hedgehog” probes to explore a moon of this planet. In 2011, Russia  \tdiamond{xyellow} launched a probe named “grunt” or “ground” intended to sample a moon of this planet, but it never left the earth’s orbit. This planet’s largest, tidally locked moon has a decaying  \tcircle{xred} orbit and will be destroyed within fifty million years. Asaph Hall discovered this planet’s moons, which were photographed by the rovers Spirit and Opportunity. For 10 points, identify  \tsquare{xyellow} this planet whose two moons are named Deimos and Phobos. \tcircle{xgreen}  \ttriangle{gray} 

\textbf{Answer}: Mars\\
\tcircle{xred} Neptune
\ttriangle{gray} Neptune
\end{frame}

\begin{frame}{Packet P7 Question 12}
A version of this formula is used in the first step of deriving the Black-Scholes model to establish the equation for delta V. Faa di Bruno's  \tcircle{xred} formula is a higher-level generalization of this formula, whose counterpart in stochastic calculus is called Ito’s Lemma. By this formula, the Jacobian of the composition  \tsquare{xred} of two functions  \tsquare{xyellow} is equal to  \ttriangle{xgreen} the product of each function’s Jacobian. Using this rule and  \tdiamond{xgreen} the product rule, one can derive the quotient rule. For 10 points, name this calculus “rule” which states that the derivative of f of g of x is f prime of g of x multiplied by g prime of x. \tcircle{gray} 

\textbf{Answer}: Chain\ rule\\
\tcircle{xred} Clausius–Clapeyron relation
\tsquare{xred} Derivative
\tcircle{gray} Clausius–Clapeyron relation
\end{frame}

\begin{frame}{Packet P7 Question 13}
In eastern Europe, many  \tsquare{xred}  \ttriangle{xred} Jews craft this substance into the shape of a bird or a ladder during Rosh Hashanah. In the Tashlikh ceremony, some Jews symbolically toss pieces of this substance into a river to cast off their sins. In the Torah, Sarah prepares this food for some visiting angels, and it miraculously does not spoil for seven days. Because of the haste of the Exodus from Egypt, Jews prepared an unleavened form of this food that is today eaten during Passover.  \tcircle{xred} For 10 points, name this food, traditional varieties of which include matza and challah. \tdiamond{xgreen}  \tcircle{gray}  \tsquare{xgreen}  \ttriangle{gray} 

\textbf{Answer}: Bread\\
\tsquare{xred} Comecon
\ttriangle{xred} Comecon
\tcircle{xred} Honey
\tcircle{gray} Honey
\ttriangle{gray} Comecon
\end{frame}

\begin{frame}{Packet P7 Question 14}
During the formation of this object, a hero receives a purple and red mantle decorated with depictions of gods, monsters, and chariots. Part of this object falls on and kills a mythological hero as he rests on a beach at Pagasae. A part of this object could supposedly speak because it was constructed from sacred oak wood taken from Dodona. To distract pursuers of this object, Absyrtus is murdered and  \tcircle{xred} cut up into pieces by his sister Medea. A voyage to Colchis was undertaken aboard, for 10 points, what ship used by Jason on his quest for  \tsquare{xred} the Golden Fleece? \tdiamond{xgreen}  \tcircle{gray}  \tsquare{gray}  \ttriangle{gray} 

\textbf{Answer}: Argo\\
\tcircle{xred} Golden Fleece
\tsquare{xred} Golden Fleece
\tcircle{gray} Golden Fleece
\tsquare{gray} Golden Fleece
\ttriangle{gray} Moon
\end{frame}

\begin{frame}{Packet P7 Question 15}
A book partly titled for  \tsquare{xred} this man claims that the simplest machine that can convert scrambled eggs to a whole egg is a hen. This man’s ideas were synthesized with Christian theology by Asa Gray. This is the more recent of the two people whose ideas were combined into the “modern synthesis” of Julian Huxley, whose grandfather Thomas was nicknamed this man’s “bulldog.”  \tsquare{xyellow} The ideas of this man are compared to a “universal acid” in a Daniel Dennett  \tdiamond{xyellow} book named after this man’s “dangerous  \tcircle{xyellow} idea.” For 10 points, name this originator of the theory  \ttriangle{xgreen} of evolution.

\textbf{Answer}: Charles\ Darwin\\
\tsquare{xred} Secularization
\end{frame}

\begin{frame}{Packet P7 Question 16}
A monologue by this writer concludes with a character saying that he would have rather been born as a seagull or a fish than as a man. A woman created by this author wishes that humanity could conceive of “God the Mother” instead of “God the Father” and regrets not consummating her engagement to Gordon Shaw. This author wrote a play about the lovers of Nina Leeds and a play in which  \tsquare{xred} Mary’s morphine  \tdiamond{xgreen}  \tcircle{xgreen} addiction and Jamie’s  \tsquare{xyellow} drinking cause problems for the Tyrone family. For 10 points,  \ttriangle{xred} name this author of Strange Interlude and Long Day’s Journey  \ttriangle{xyellow} into Night.

\textbf{Answer}: Eugene\ O'Neill\\
\tsquare{xred} Strange Interlude
\ttriangle{xred} Long Day's Journey into Night
\end{frame}

\begin{frame}{Packet P7 Question 17}
This poems calls Waterloo ``where the sword united nations drew''. This poem urges a woman to “Smile on,”  \tdiamond{xyellow} not “venture to unmask / Man's heart, and view the Hell that's there” in its digression “To Inez.” The line “There is a pleasure in the pathless woods” opens this poem’s “Apostrophe to the Ocean.” This poem’s title character witnesses a bullfight in Spain and  \tsquare{xyellow} laments on the state of modern Greek culture. For 10 points, name this Lord Byron  \tcircle{xgreen}  \ttriangle{xyellow} poem about a Romantic youth’s journey through Europe.

\textbf{Answer}: Childe\ Harold's\ Pilgrimage\\
\end{frame}

\begin{frame}{Packet P7 Question 18}
In Pride and Prejudice, Mr. Darcy meditates  \tsquare{xred} on the “very great pleasure” that “fine” these things can provide. Ben Jonson’s poem “To Celia” opens with the command “Drink to me only with” these things. William Shakespeare’s 130th Sonnet begins by stating that these body parts of his mistress are “nothing like the sun.” In King Lear, a servant kills the Duke of  \tdiamond{xyellow} Cornwall after witnessing Regan and Goneril removing these body parts from the Earl  \tcircle{xyellow}  \ttriangle{xred} of Gloucester. For 10 points, the loss of what body parts causes Gloucester to wander blindly through a stormy heath? \tsquare{gray}  \ttriangle{gray} 

\textbf{Answer}: Eye\\
\tsquare{xred} Elizabeth Bennet
\ttriangle{xred} Wing
\tsquare{gray} Elizabeth Bennet
\ttriangle{gray} Wing
\end{frame}

\begin{frame}{Packet P7 Question 19}
The speaker of a poem by this author, who claims to be “the world's mindless dweller,” relates the story of a woman named Naima who turns into a dragon and tells of a man who draws a sword from the massive severed head of the wizard Chernomor’s dead brother. This man wrote a poem in which Parasha’s lover wanders the streets of his home city  \tcircle{xgreen} in insanity after she dies in a flood. This author of Ruslan and Ludmila wrote  \tdiamond{xgreen}  \tsquare{xgreen} a poem about Evgenii, who curses a statue of Peter the Great  \ttriangle{xgreen} that pursues him to his death. For 10 points, name this author of “The Bronze Horseman.”

\textbf{Answer}: Alexander\ Pushkin\\
\end{frame}

\begin{frame}{Packet P7 Question 20}
An essay from this literary  \tsquare{xred}  \ttriangle{xred} movement was among the first to argue that Shakespeare’s plays should be not be judged using the Aristotelian Unities, and was published in a collection about “Character and Art.” A member of this movement wrote the plays The Soldiers and The Tutor and names a Georg Buchner novella. A play by Friedrich von Klinger provided the name  \tsquare{xyellow} of this movement, which  \tcircle{xgreen} included the dramatist Jakob Lenz. The Sorrows of Young Werther is from this movement. For 10 points, name this German  \tdiamond{xgreen} literary movement whose name translates as “storm and stress.” \ttriangle{xgreen} 

\textbf{Answer}: Sturm\ und\ Drang\\
\tsquare{xred} An Lushan Rebellion
\ttriangle{xred} Transcendentalism
\end{frame}

\begin{frame}{Packet P7 Question 21}
A playwright from this country wrote a drama  \ttriangle{xyellow} about war crimes  \tsquare{xyellow} trials titled Between  \tcircle{xyellow} God and Man and adapted a folktale in which a man discovers that his wife is a  \tcircle{xred} bird who uses her feathers to produce textiles. The phrase “beginning, break, rapid” outlines the plots of dramas from this country whose stage backgrounds depicted a single pine tree. The play Twilight Crane is from this country, as are the over four hundred types of masks used  \tdiamond{xgreen} in Noh performances. Bunraku and Kabuki are genres of drama from, for 10 points, what country where plays debuted in Osaka?

\textbf{Answer}: Japan\\
\tcircle{xred} Germany
\end{frame}

\begin{frame}{Packet P7 Question 22}
This poet claimed that  \tsquare{xred} he was unworthy to write about wars in a work in which he instead sings “of banquets, of girls fierce in battle / with closely-trimmed nails, attacking young men.” The fourteenth poem in a collection by this author advises “The Ship of State” to “avoid the glistening seas.” The phrase “Now’s the time for drinking deep” opens his poem about Cleopatra. Wilfred Owen titled a poem from this author’s line “Dulce et decorum est pro patria mori.”  \tdiamond{xgreen}  \tcircle{xgreen}  \ttriangle{xgreen} The phrase “carpe  \tsquare{xyellow} diem” was originated by, for 10 points, what Latin poet of three books of Odes?

\textbf{Answer}: Horace\\
\tsquare{xred} Anne Sexton
\end{frame}

\begin{frame}{Packet P7 Question 23}
A raid on three banks in this state by Confederate paramilitary cavalrymen who subsequently escaped to Canada is considered the northernmost land action of the Civil War. John Stark’s  \tcircle{xgreen}  \tsquare{xyellow} forces defeated a unit under Friedrich Baum in a Revolutionary War battle in this state that caused mass desertions among John Burgoyne’s native allies prior to the Saratoga Campaign. The St. Albans  \tsquare{xred} Raid and the Battle of Bennington occurred in, for 10 points, what state where  \tdiamond{xgreen} Ethan Allen led the Green Mountain Boys  \ttriangle{xgreen} militia in a dispute over its eastern border with New Hampshire?

\textbf{Answer}: Vermont\\
\tsquare{xred} Saratoga campaign
\end{frame}

\begin{frame}{Packet P7 Question 24}
The founder of Salon,  \tsquare{xred} David Talbot, wrote a book about this city’s history titled Season of the Witch. The Golden Dragon Massacre led to a crackdown on gang violence in this city, which was the headquarters of the Peoples Temple directly before Jim Jones relocated to Guyana. A “diminished capacity” legal strategy derisively called the Twinkie Defense was used to secure a manslaughter conviction for Dan White in this city  \tcircle{xgreen} after he killed Harvey  \tsquare{xyellow} Milk and George  \tdiamond{xgreen} Moscone. For 10 points, name this California city where The Castro became one of the U.S.’s first  \ttriangle{xgreen} LGBT neighborhoods.

\textbf{Answer}: San\ Francisco\\
\tsquare{xred} Germaine de Staël
\end{frame}

\begin{frame}{Packet P7 Question 25}
A 1363 decree designed to promote the use of this weapon banned most sports on Sundays. Roger Ascham's book Toxophilus is about these weapons, 172 of which were recovered from the wreck of the Mary Rose. A popular myth holds that the gesture of the middle finger arose from a French practice of mutilating prisoners of war so that they could not use these weapons. Henry V's army made devastating use of these weapons to harass  \ttriangle{xred} French knights at the Battle of Agincourt. For 10 points, name these tall  \tsquare{xyellow} weapons used by British archers in the medieval era. \tdiamond{gray}  \tcircle{gray}  \ttriangle{gray} 

\textbf{Answer}: Longbow\\
\ttriangle{xred} V-weapons
\tdiamond{gray} Arrow
\tcircle{gray} Spar torpedo
\ttriangle{gray} V-weapons
\end{frame}

\begin{frame}{Packet P7 Question 26}
Emile Boissonade largely wrote a legal code that specifically promoted penal transport to this island. Jules Brunet organized a force that unsuccessfully defended a star fort on this island. In 1870, former Secretary of Agriculture Horace Capron was hired to modernize  \tcircle{xgreen} this island. Shakushain’s Revolt challenged a fiefdom controlled by the Matsumae Clan on this island, where the Republic  \tdiamond{xgreen} of Ezo briefly  \tsquare{xgreen} resisted the Meiji Restoration. For 10 points, name this primary home of the Ainu people, an island  \ttriangle{xyellow} where fortifications were constructed in Hakodate and Sapporo.

\textbf{Answer}: Hokkaido\\
\end{frame}

\begin{frame}{Packet P7 Question 27}
In 1994, this country’s president denounced his wife Susana and made his daughter its official first lady. In 2000, videos surfaced of a man from this country offering bribes to TV stations to deny interviews with opposition members; that scandal brought down the leader of the SIN intelligence service in this country, Vladimiro  \tsquare{xyellow} Montesinos.  \tdiamond{xgreen}  \tsquare{xred} It was the location of terrorist attacks by Maoist guerillas  \tcircle{xgreen} called the Shining Path during the administration  \ttriangle{xyellow} of Alberto Fujimori. For 10 points, name this country where a revolutionary movement took the name of Inca rebel Tupac Amaru.

\textbf{Answer}: Peru\\
\tsquare{xred} Alberto Fujimori
\end{frame}

\begin{frame}{Packet P7 Question 28}
This man proposed that general relativity could arise from independent physical parameters in his model  \tcircle{xred} of induced gravity. He postulated that the universe was comprised of two “sheets.” This scientist,  \tdiamond{xred} who names three conditions at which baryonic matter and antimatter are produced at different rates, worked with Igor Lamm to develop the first tokamak. This man’s “third idea” was used in the RDS-37 hydrogen bomb, though  \tsquare{xred} he was later exiled to Gorky for speaking out against anti-ballistic missile systems. For 10 points, name this Soviet nuclear scientist and  \tsquare{xyellow} human rights advocate. \tdiamond{gray}  \tcircle{gray}  \ttriangle{xgreen} 

\textbf{Answer}: Andrei\ Sakharov\\
\tcircle{xred} Albert Einstein
\tdiamond{xred} Albert Einstein
\tsquare{xred} Edward Teller
\tdiamond{gray} Albert Einstein
\tcircle{gray} Albert Einstein
\end{frame}

\begin{frame}{Packet P7 Question 29}
These objects are the main subject of Vasily Vereshchagin’s painting  \tcircle{xgreen} The Apotheosis of War. A photograph by Philippe Halsman shows Salvador Dali standing in front of one of these objects formed from the bodies of seven nude women. The subtitle “Red, White, and Blue” is appended to a Georgia O’Keefe painting of one of these objects that originally belonged to a cow. An anamorphic one of these objects is stretched across the floor of Hans Holbein’s The Ambassadors. For 10 points,  \tsquare{xgreen}  \ttriangle{xgreen} name these objects often used as a vanitas  \tdiamond{xgreen} symbol of death.

\textbf{Answer}: Skull\\
\end{frame}

\begin{frame}{Packet P7 Question 30}
This man appears standing and wearing a green coat on the left side a Matthew Pratt painting that shows this man giving an art lesson. Three angels hold the line of a kite on the right side of a painting by this artist, who served as the second president of the  \ttriangle{xyellow} Royal Academy. This  \tdiamond{xred} artist of Benjamin Franklin Drawing Electricity from the Sky  \tdiamond{xyellow} ahistorically showed Simon Fraser behind  \tsquare{xgreen} a man in a green jacket in a painting in which a Native American  \tcircle{xgreen} warrior contemplates a British general’s last moments. For 10 points, name this artist of The Death of General Wolfe.

\textbf{Answer}: Benjamin\ West\\
\tdiamond{xred} Joshua Reynolds
\end{frame}

\begin{frame}{Packet P7 Question 31}
A musical depiction of a landmark in this city uses its composer’s poem “Moving- Marching- Faces of Souls” and builds to a C major chord played by the entire ensemble to depict a pitched battle. An orchestra in this city premiered Sergei Prokofiev’s Fourth Symphony under the direction of Serge Koussevitzky. The Tanglewood is a summer venue  \tsquare{xred} near this city, where Arthur Fiedler was the director of an orchestra known for its Fourth of July concert. The first of Charles Ives’s Three Places in New England is in, for 10 points, what Massachusetts city home to a pops orchestra? \tdiamond{gray}  \tcircle{gray}  \tsquare{gray}  \ttriangle{gray} 

\textbf{Answer}: Boston\\
\tsquare{xred} Boston Symphony Orchestra
\tdiamond{gray} Fall River, Massachusetts
\tcircle{gray} Los Angeles
\tsquare{gray} Boston Symphony Orchestra
\ttriangle{gray} New York City
\end{frame}

\begin{frame}{Packet P7 Question 32}
A sculptor from this country  \tsquare{xred} created a relief for a “Carousel” triumphal arch showing the conquest of Munich and is known for many terracotta sculptures of drunken nymphs and satyrs. A sculptor from this country adapted his cast of the torso of Adele Abruzzesi into his sculpture of two embracing lovers, Eternal Springtime. This birthplace of Clodion is the home country of an artist who was accused of casting a living model  \tcircle{xred} to produce his sculpture The Age of Bronze. For 10 points, name this birthplace of the sculptor of The Thinker, Auguste Rodin. \tdiamond{gray}  \tcircle{gray}  \tsquare{gray}  \ttriangle{gray} 

\textbf{Answer}: France\\
\tsquare{xred} Bertel Thorvaldsen
\tcircle{xred} Auguste Rodin
\tdiamond{gray} Brazil
\tcircle{gray} Auguste Rodin
\tsquare{gray} Bertel Thorvaldsen
\ttriangle{gray} Japan
\end{frame}

\begin{frame}{Packet P7 Question 33}
The leader of this country for much of the 2000s used a campaign slogan of “Peace and Love.” In November 2018, a politician in this country reversed his pledge to combine its environmental and agriculture ministries. The losing candidate in an October 2018 runoff election in this country was the Workers’ Party candidate Fernando Haddad; the election’s winner was stabbed on the campaign trail and has opposed the distribution of LGBT educational materials in schools. For 10 points, what country’s leader-elect is a former army captain named Jair Bolsonaro? \tdiamond{gray}  \tcircle{gray}  \tsquare{gray}  \ttriangle{gray} 

\textbf{Answer}: Brazil\\
\tdiamond{gray} South Korea
\tcircle{gray} South Korea
\tsquare{gray} Luiz Inácio Lula da Silva
\ttriangle{gray} Peru
\end{frame}

\begin{frame}{Packet P7 Question 34}
This actor plays a father  \tsquare{xred} who is upset when he encounters his soon-to-be suspended daughter singing “Hollaback Girl” in a school hallway. A character played by this actor is telling a story about Mardi Gras when he hears that a Russian missile strike has caused a chain reaction of satellite explosions. He portrayed the Hawaii lawyer Matt King, who comes to terms with the death of his comatose wife. He also played Matt Kowalski, who becomes trapped aboard a space station with an astronaut played by  \ttriangle{xred} Sandra Bullock. For 10 points, name this star of The Descendants and Gravity. \tdiamond{gray}  \tcircle{gray}  \tsquare{gray}  \ttriangle{gray} 

\textbf{Answer}: George\ Clooney\\
\tsquare{xred} Samuel L. Jackson
\ttriangle{xred} Matthew McConaughey
\tdiamond{gray} Tom Cruise
\tcircle{gray} John Malkovich
\tsquare{gray} Samuel L. Jackson
\ttriangle{gray} Matthew McConaughey
\end{frame}

\begin{frame}{Packet P7 Question 35}
In this city, a vase showing marching soldiers in full armor, the Warrior Crater, was discovered in Grave Circle A. A stone archway whose top depicts two lions forms a gate in this city, which contains nine surviving tholos tombs including the  \tcircle{xgreen} Treasury of Atreus and is nearby the similar site of Tiryns.  \tsquare{xgreen} A gold funerary mask was unearthed in this city by Heinrich Schliemann. A culture  \tdiamond{xgreen} named for this city used the Linear B script and was the final dominant culture of Bronze Age Greece. For 10 points, name this city where the Mask of Agamemnon was unearthed. \ttriangle{gray} 

\textbf{Answer}: Mycenae\\
\ttriangle{gray} New York City
\end{frame}

\begin{frame}{Packet P7 Question 36}
A painting in this location that renders silver shillings strewn on the floor in gold paint is titled Art and Money, and contains  \tdiamond{xyellow} a characteristic blue-green background. In this location, a painting of a white woman in a pink and grey kimono hangs above a fireplace. The design of this location ignited its creator’s feud with Frederick Leyland. This location, which  \tsquare{xgreen} is currently in the Freer Gallery at the Smithsonian, contains The Princess from the Land of Porcelain. For 10 points,  \ttriangle{xgreen} identify this Asian-inspired room designed by James Whistler, which is named for a colorful bird. \tcircle{gray} 

\textbf{Answer}: The\ Peacock\ Room\\
\tcircle{gray} Washington, D.C.
\end{frame}

\begin{frame}{Packet P7 Question 37}
In 2017, scientists unearthed a complete ichthyosaur skeleton in this country, which is unusual since it is not a far northern country. The Lameta Formation is in this country, whose central region contains a series of “Traps” that formed 66 million years ago around the time of the K-T Extinction. This country and Madagascar share many dinosaur species, since the tectonic plate named for this country was joined with Madagascar before it drifted northward and collided with Asia. For 10 points, name this country where Rajasaurus was discovered in Gujarat. \tdiamond{gray}  \tcircle{gray}  \tsquare{gray}  \ttriangle{gray} 

\textbf{Answer}: India\\
\tdiamond{gray} Panama
\tcircle{gray} Soviet Union
\tsquare{gray} Mongolia
\ttriangle{gray} France
\end{frame}

\begin{frame}{Packet P7 Question 38}
This novel’s narrator lies about being a wrestler to borrow ten dollars from a Mexican driver before stating this book’s final line, “I been away a long time.” A man in this novel sees a rag on a tree branch, reminding him of his first sexual encounter at ten years old, while on a fishing trip that he coordinates with the prostitute Candy Starr. Billy Bibbit commits  \tdiamond{xgreen}  \tcircle{xgreen}  \ttriangle{xgreen} suicide after  \tsquare{xgreen} losing his virginity in this novel that contains a climactic scene in which Chief Bromden smothers the lobotomized Randle McMurphy. For 10 points, name this Ken Kesey novel mostly set in a mental asylum.

\textbf{Answer}: One\ Flew\ Over\ the\ Cuckoo's\ Nest\ (novel)\\
\end{frame}

\begin{frame}{Packet P7 Question 39}
The diary describes this battle with a page for each death in Tanya Savicheva's family. The Green Belt of Glory monument commemorates this battle, during which the attackers were led  \tdiamond{xyellow} by Wilhelm Ritter von  \tcircle{xred} Leeb. Dmitri Shostakovich's Seventh Symphony premiered during and is named after this battle. The  \tsquare{xgreen} defending side at this battle established the Road of Life to transport supplies across the frozen  \tcircle{xyellow} top of Lake Ladoga.  \ttriangle{xyellow} For 10 points, name this siege during which a northern Russian city was attacked by German and Finnish forces during World War Two.

\textbf{Answer}: Siege\ of\ Leningrad\\
\tcircle{xred} Gunfight at the O.K. Corral
\end{frame}

\begin{frame}{Packet P7 Question 40}
Yoram Ben-Porath introduced a production function for this concept to predict its rate of creation. Mankiw, Romer, and Weil argued that introducing this concept to the Solow Model was  \tcircle{xred} necessary for its predictions to corroborate real-world data. Theodore Schultz wrote the paper that formally introduced this concept in 1961. Signaling theory is an alternative to the argument that people are producing this thing by receiving education. A Gary Becker book about people investing in themselves is named after, for 10 points, what non-physical variety of one of the four factors of production? \tdiamond{gray}  \tcircle{gray}  \tsquare{gray}  \ttriangle{gray} 

\textbf{Answer}: Human\ capital\\
\tcircle{xred} Economic growth
\tdiamond{gray} Capital (economics)
\tcircle{gray} Economic growth
\tsquare{gray} Economic growth
\ttriangle{gray} Knowledge
\end{frame}

\begin{frame}{Packet P7 Question 41}
Amsterdam experienced a riot named for this  \ttriangle{xred} crop during World War One. In the 1830s and 40s, Russian peasants on the lower Volga objected to the forced introduction of this crop in a namesake series of riots. Antoine-Augustin Parmentier pushed for the cultivation of this crop in France. This crop provides  \tsquare{xred} an alternate name for the War of the Bavarian Succession.  \tdiamond{xgreen} An epidemic of phytophthora infestans devastated the cultivation of this crop in the mid-19th Century. Robert Peel repealed the Corn Laws to counteract a blight of, for 10 points, what crop that caused an Irish famine? \tcircle{gray}  \tsquare{gray}  \ttriangle{gray} 

\textbf{Answer}: Potato\\
\ttriangle{xred} Soweto uprising
\tsquare{xred} Rice
\tcircle{gray} Cotton
\tsquare{gray} Rice
\ttriangle{gray} Soweto uprising
\end{frame}

